### 2019-03-11 tex/ms.tex
Update ms.tex

\documentclass[modern]{aastex62}

% Load the corTeX style definitions
\input{cortex}

% Bibliography stuff
\bibliographystyle{aasjournal}

% Begin!
\begin{document}

% Title
\title{Detection of A Habitable Planet with \emph{TESS}}

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author[0000-0002-9328-5652]{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}

% Introduction
\section*{The Long and Short of it}
\label{sec:intro}
%
\textsc{corTeX} is a very simple \textsf{GitHub} repository aimed at making
it easy to make your scientific articles open source and reproducible.
\textsc{corTeX} currently does two things. First, it defines the
\textsf{\textbackslash oscaption} command, which adds
links to all figure captions pointing to the exact script that generated it;
see Figure~\ref{fig:pretty_function}.
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:pretty_function}
    }
    \end{centering}
\end{figure}
%

Second, it defines the \textsf{\textbackslash proof} environment, which
adds a link to any equation pointing to a proof, derivation, or
verification of the equation in the form of a \textsf{Jupyter} notebook:
%
\begin{proof}{euler}
    \label{eq:euler}
    e^{i\pi} + 1 = 0.
\end{proof}
%
Check out \citet{Luger2018} for an example of a paper that uses these
features.

% Bibliography
\pagebreak
\bibliography{bib}

\end{document}

### 2019-03-11 .ci/install.sh
Update install.sh

@@ -24,8 +24,8 @@ conda info -a
 # Attempt to resolve issues with SSL certificate expiring for purl.org:
 # https://tectonic.newton.cx/t/how-to-use-tectonic-if-you-can-t-access-purl-org/44
 # https://github.com/tectonic-typesetting/tectonic/issues/131
-#mkdir -p $HOME/.config/Tectonic
-#cat > $HOME/.config/Tectonic/config.toml << EOL
-#[[default_bundles]]
-#url = "https://tectonic.newton.cx/bundles/tlextras-2018.1r0/bundle.tar"
-#EOL
+mkdir -p $HOME/.config/Tectonic
+cat > $HOME/.config/Tectonic/config.toml << EOL
+[[default_bundles]]
+url = "https://tectonic.newton.cx/bundles/tlextras-2018.1r0/bundle.tar"
+EOL

### 2019-03-11 tex/ms.tex
first stab at an abstract

@@
 \input{cortex}
+
+\usepackage{xcolor}
+\usepackage{xspace}
+\newcommand{\TESS}{\emph{TESS}\xspace}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
 
@@
 % Title
-\title{Detection of A Habitable Planet with \emph{TESS}}
+\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}
 
@@
 
+\begin{abstract}
+The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars \todo{(CITE)}. 
+While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
+In this work, we extract this signal and demonstrate that it corresponds to a terrestrial planet with a rotation period of 1 day \todo{(add error estimate!)}. 
+Using the STARRY package, we are able to reconstruct the surface features of this rocky world \citep{Luger2018}. 
+We find evidence for \todo{(clouds, some number of continents, whatever)}. 
+We argue that this planet represents the most promising detection of a habitable world to date, although the potential intelligence of any life on it is yet to be determined.
+\end{abstract}
+
+\keywords{ALIENS}
+
 % Introduction
-\section*{The Long and Short of it}
+\section{Introduction}
 \label{sec:intro}
 %
-\textsc{corTeX} is a very simple \textsf{GitHub} repository aimed at making
-it easy to make your scientific articles open source and reproducible.
-\textsc{corTeX} currently does two things. First, it defines the
-\textsf{\textbackslash oscaption} command, which adds
-links to all figure captions pointing to the exact script that generated it;
-see Figure~\ref{fig:pretty_function}.
-%
-\begin{figure}[h!]
-    \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
-    \oscaption{pretty_function}{%
-        This is a plot of a pretty function. And at the end of this
-        caption is a symbol with a link to the \emph{exact} script
-        that generated it, hosted on \textsf{GitHub}.
-        \label{fig:pretty_function}
-    }
-    \end{centering}
-\end{figure}
-%
 
-Second, it defines the \textsf{\textbackslash proof} environment, which
-adds a link to any equation pointing to a proof, derivation, or
-verification of the equation in the form of a \textsf{Jupyter} notebook:
-%
-\begin{proof}{euler}
-    \label{eq:euler}
-    e^{i\pi} + 1 = 0.
-\end{proof}
-%
-Check out \citet{Luger2018} for an example of a paper that uses these
-features.
+\section{Methods}
+
+\section{Discussion}
+
+\section{Conclusion}
 

### 2019-03-19 data/process_sc.py
consistent interpolation and outlier rejection of LCs

@@ -10,7 +10,7 @@ data_dir = '/mnt/ceph/users/mbedell/tess/'
 def save_all_sc(filenames, out_file):
     N = len(filenames)
     with fits.open(filenames[0]) as hdul:
-        time = np.copy(hdul[1].data['TIME']) # assumes all TPFs have the same cadences
+        time = np.copy(hdul[1].data['TIME']) # assumes all TPFs have the same number of cadences
     M = len(time)
     
     # read all the files:
@@ -20,8 +20,12 @@ def save_all_sc(filenames, out_file):
     cameras = np.empty(N)
     bkgs = np.empty((N,M))
     bkg_errs = np.empty((N,M))
+    raw_bkgs = np.empty((N,M))
+    raw_bkg_errs = np.empty((N,M))
+    raw_times = np.empty((N,M))
+    raw_qualities = np.empty((N,M))
     bad = [] # store indices that may need deleting
-    tenpercent = int(N/10)
+    tenpercent = 1000 # guess
     for i,fn in enumerate(filenames):
         if i//tenpercent == 0:
             print('{0:3.1f}% done'.format(i/N * 100))
@@ -31,8 +35,18 @@ def save_all_sc(filenames, out_file):
                 rows[i] = np.copy(hdul[1].header['2CRV5P'])
                 ccds[i] = np.copy(hdul[0].header['CCD'])
                 cameras[i] = np.copy(hdul[0].header['CAMERA'])
-                bkgs[i,:] = np.copy(hdul[1].data['FLUX_BKG'][:,0,0]) # assumes all pixels get the same bkg
-                bkg_errs[i,:] = np.copy(hdul[1].data['FLUX_BKG_ERR'][:,0,0])
+                # get raw time series:
+                bkg = np.copy(hdul[1].data['FLUX_BKG'][:,0,0]) # assumes all pixels get the same bkg
+                bkg_err = np.copy(hdul[1].data['FLUX_BKG_ERR'][:,0,0])                
+                t = np.copy(hdul[1].data['TIME'])
+                raw_bkgs[i,:] = np.copy(bkg)
+                raw_bkg_errs[i,:] = np.copy(bkg_err)
+                raw_times[i,:] = np.copy(t)
+                raw_qualities[i,:] = np.copy(hdul[1].data['QUALITY'])
+                # interpolate good quality measurements to standard time grid and save:
+                q = hdul[1].data['QUALITY'] == 0
[…]

### 2019-03-21 earthshine/animate.py
woot

@@ -125,7 +125,7 @@ def animate(map, time, phase0=0.0, res=75, interval=75):
         # Rotate the earth to the current phase in the original frame
         map[:, :, :] = y
         map.axis = [0, 1, 0]
-        phase = (360. * time[i]) % 360. + phase0
+        phase = (360. * (time[i] - time[0])) % 360. + phase0
         map.rotate(phase)
 
         # Rotate the earth and the sun into tess' frame  

### 2019-03-21 earthshine/model.py

@@ -113,7 +113,7 @@ def design_matrix(time, ydeg=10, nt=2, period=1.0, phase0=0.0,
         # rotates the earth into phase and then rotates
         # the earth into view for tess
         tx, ty, tz = tess_hat[:, i]
-        phase = (2 * np.pi * time[i]) % (2 * np.pi) + phase0
+        phase = (2 * np.pi * (time[i] - time[0])) % (2 * np.pi) + phase0 * np.pi / 180
         ty2 = ty ** 2
         tx2 = tx ** 2
         cosp = np.cos(phase)

### 2019-03-22 tex/ms.tex
paper outline

@@
 % Title
-\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}
+\title{\TESS Photometric Mapping of Surface Features on a Habitable-Zone Terrestrial Planet: Clouds, Oceans, and Continents}
+%\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}
 
@@
 \begin{abstract}
-The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars \todo{(CITE)}. 
+The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars \citep{Ricker2015}. 
 While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
-In this work, we extract this signal and demonstrate that it corresponds to a terrestrial planet with a rotation period of 1 day \todo{(add error estimate!)}. 
-Using the STARRY package, we are able to reconstruct the surface features of this rocky world \citep{Luger2018}. 
-We find evidence for \todo{(clouds, some number of continents, whatever)}. 
+In this work, we extract this signal and demonstrate that it is consistent with a terrestrial planet with a rotation period of 1 day. 
+Using a spherical harmonic-based reflection model developed as an extension of the STARRY package \citep{Luger2018}, we are able to reconstruct the surface features of this rocky world. 
+We recover a time-variable albedo map of the planet including persistent regions which we interpret as continental features and cloud banks. 
 We argue that this planet represents the most promising detection of a habitable world to date, although the potential intelligence of any life on it is yet to be determined.
@@
 \label{sec:intro}
-%
+
+%Resolving the features of planetary atmospheres and surfaces with precise photometry is a crucial 
+Precise photometry obtained over long periods of time can reveal the atmospheric and surface features of an exoplanet through the method known as phase mapping.
+\todo{(literature background \& citations)}
+
+A new source of precise photometry is the Transiting Exoplanet Survey Satellite (\TESS). 
+Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, citations to planet discoveries etc)}
+
+One intriguing feature of the \TESS photometric data products is a highly time-variable signal represented in the diffuse background across virtually all camera pixels. 
+\todo{(talk abt Earthshine without naming it)} 
+The signal has been widely attributed to a planet which we will call Sol d.
+
+Previous attempts to map this planet from the exoplanet community have suggested the presence of localized surface features, but their resolving power has been severely limited by the duration of observations \citep{Cowan2009}.
+\TESS offers precise 2-minute cadence data spanning a wide range of illumination phases, enabling a level of spatial and temporal resolving power that is unprecedented in the exoplanetary phase mapping literature.
+
+Moreover, recent advances in fast analytic computation of spherical harmonics have made the reconstruction of such detailed maps more feasible than ever. 
+\todo{(STARRY)}
+
+In this work, we build on this methodological foundation to perform reflected-light mapping of planetary surface features on Sol d. 
+We give an overview of the \TESS data used in Section \ref{sec:data}. 
+In Section \ref{sec:methods}, we describe the methods employed to infer a map from these data, including the adaptation of the STARRY algorithm to reflection mapping, the modeling of spacecraft-related systematics, and the likelihood and priors used.
+We present results in Section \ref{sec:results} and make comparison of these findings to state-of-the-art terrestrial planet maps from the literature in Section \ref{sec:discussion}. 
+Finally, we conclude in Section \ref{sec:conclusion} with a look at future prospects for phase-curve mapping of terrestrial exoplanets.
+
+\section{Data}
+\label{sec:data}
+
+\todo{(background extraction from 2-minute cadence targets)}
+
+\todo{(figure showing lightcurves for various targets)}
 
 \section{Methods}
+\label{sec:methods}
+
+\subsection{Systematics Modeling}
+
+\subsection{Reflected-Light Mapping with STARRY}
+\todo{(possibly make the gritty math details be an appendix?)}
+
+\subsection{Likelihood Function \& Inference}
+
+\section{Results}
+\label{sec:results}
+
+\todo{(present results with \& without time variability)}
 
 \section{Discussion}
+\label{sec:discussion}
+
+\todo{(comparison of inferred features to ``model'' (Earth))}
 
 \section{Conclusion}
+\label{sec:conclusion}
 
+\todo{(summarize)}
+
+\todo{(talk abt prospects for doing this analysis with exoplanets)}
+
+\acknowledgements{}
+\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2018}, TensorFlow}
 % Bibliography

### 2019-03-23 tex/ms.tex
more references, better outline

@@
 \affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
+%
+\author{Roland K. Vanderspek}
+\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA}
+%
+\author{Christopher J. Burke}
+\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA}
 
 \begin{abstract}
-The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars \citep{Ricker2015}. 
+\todo{[maybe change first sentences to focus on planet mapping \& give the game away less?]}
+The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
 While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
 In this work, we extract this signal and demonstrate that it is consistent with a terrestrial planet with a rotation period of 1 day. 
-Using a spherical harmonic-based reflection model developed as an extension of the STARRY package \citep{Luger2018}, we are able to reconstruct the surface features of this rocky world. 
+Using a spherical harmonic-based reflection model developed as an extension of the STARRY package, we are able to reconstruct the surface features of this rocky world. 
 We recover a time-variable albedo map of the planet including persistent regions which we interpret as continental features and cloud banks. 
@@
 
-\keywords{ALIENS}
+\keywords{methods: data analysis, techniques: photometric, planets and satellites: oceans, planets and satellites: surfaces, planets and satellites: terrestrial planets}
 
@@
 
-A new source of precise photometry is the Transiting Exoplanet Survey Satellite (\TESS). 
+A new source of precise photometry is the Transiting Exoplanet Survey Satellite \citep[\TESS; ][]{Ricker2015}. 
 Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, citations to planet discoveries etc)}
@@
 
+\todo{(outlier rejection method, trim down to x number of high-SNR lightcurves for computational tractability)}
+
 \todo{(figure showing lightcurves for various targets)}
@@
 
+While the astrophysical signal that we wish to analyze is present in all \todo{x} extracted lightcurves, its strength is modulated by time-variable systematics that are correlated but not identical across all sources.
+\todo{The observed lightcurves can be represented as... (systematics x Earthshine equation)}
+
+We choose to model this systematic component using Pixel Level Decorrelation (PLD).
+\todo{(details, math, and a figure of the bases (possibly two-panel with comparison to telescope housekeeping variables?)}
+
 \subsection{Reflected-Light Mapping with STARRY}
-\todo{(possibly make the gritty math details be an appendix?)}
+
+\todo{(brief recap of STARRY)}
+
+\todo{(adapting STARRY to reflected light/variable illumination phase - possibly make the gritty math details be an appendix?)}
+
+\todo{(time variability of surface features)}
 
 \subsection{Likelihood Function \& Inference}
+
+\todo{(priors, regularization, equation for the likelihood)}
+
+\todo{(details of TensorFlow optimization)}
 
@@
 
+\todo{(utility for \TESS background removal)}
+
 \todo{(talk abt prospects for doing this analysis with exoplanets)}
 
-\acknowledgements{}
-\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2018}, TensorFlow}
+\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} for useful conversations.
+Crucial parts of this work were carried out at the TESS Data Workshop, hosted by Space Telescope Science Institute, and the Building Early Science with TESS Workshop, hosted by the University of Chicago.}
+\facility{TESS}
+\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2019}, TensorFlow}
 % Bibliography

### 2019-03-24 tex/ms.tex
working on the ms

@@
 % Title
-\title{\TESS Photometric Mapping of Surface Features on a Habitable-Zone Terrestrial Planet: Clouds, Oceans, and Continents}
+\title{\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: 
+       Detection of Clouds, Oceans, and Continents}
 %\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}
@@
 \author{Roland K. Vanderspek}
-\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA}
+\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts 
+       Institute of Technology, Cambridge, MA}
 %
 \author{Christopher J. Burke}
-\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA}
+\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts 
+       Institute of Technology, Cambridge, MA}
 
 \begin{abstract}
-\todo{[maybe change first sentences to focus on planet mapping \& give the game away less?]}
-The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
-While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
-In this work, we extract this signal and demonstrate that it is consistent with a terrestrial planet with a rotation period of 1 day. 
-Using a spherical harmonic-based reflection model developed as an extension of the STARRY package, we are able to reconstruct the surface features of this rocky world. 
-We recover a time-variable albedo map of the planet including persistent regions which we interpret as continental features and cloud banks. 
-We argue that this planet represents the most promising detection of a habitable world to date, although the potential intelligence of any life on it is yet to be determined.
+\todo{[maybe change first sentences to focus on planet mapping \& give the game 
+away less?]} The Transiting Exoplanet Survey Satellite (\TESS) mission is a 
+targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
+While \TESS is already enjoying great success with the discovery of many new worlds, 
+the strongest signal in its data is typically ignored, as it lurks in the background 
+of every camera pixel. In this work, we extract this signal and demonstrate that 
+it is consistent with a terrestrial planet with a rotation period of 1 day. 
+Using a spherical harmonic-based reflection model developed as an extension of 
+the \starry package, we are able to reconstruct the surface features of this rocky 
+world. We recover a time-variable albedo map of the planet including persistent 
+regions which we interpret as continental features and cloud banks. 
+We argue that this planet represents the most promising detection of a habitable 
+world to date, although the potential intelligence of any life on it is yet to 
+be determined.
 \end{abstract}
 
-\keywords{methods: data analysis, techniques: photometric, planets and satellites: oceans, planets and satellites: surfaces, planets and satellites: terrestrial planets}
+\keywords{methods: data analysis, techniques: photometric, planets and satellites: 
+          oceans, planets and satellites: surfaces, planets and satellites: 
+          terrestrial planets}
 
@@
 
-%Resolving the features of planetary atmospheres and surfaces with precise photometry is a crucial 
-Precise photometry obtained over long periods of time can reveal the atmospheric and surface features of an exoplanet through the method known as phase mapping.
+%Resolving the features of planetary atmospheres and surfaces with precise 
+%photometry is a crucial 
+Precise photometry obtained over long periods of time can reveal the atmospheric 
+and surface features of an exoplanet through the method known as phase mapping. 
 \todo{(literature background \& citations)}
 
-A new source of precise photometry is the Transiting Exoplanet Survey Satellite \citep[\TESS; ][]{Ricker2015}. 
-Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, citations to planet discoveries etc)}
+A new source of precise photometry is the Transiting Exoplanet Survey Satellite 
+\citep[\TESS; ][]{Ricker2015}. 
+Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, 
+citations to planet discoveries etc)}
 
-One intriguing feature of the \TESS photometric data products is a highly time-variable signal represented in the diffuse background across virtually all camera pixels. 
+One intriguing feature of the \TESS photometric data products is a highly 
+time-variable signal represented in the diffuse background across virtually 
+all camera pixels. 
 \todo{(talk abt Earthshine without naming it)} 
@@
 
-Previous attempts to map this planet from the exoplanet community have suggested the presence of localized surface features, but their resolving power has been severely limited by the duration of observations \citep{Cowan2009}.
-\TESS offers precise 2-minute cadence data spanning a wide range of illumination phases, enabling a level of spatial and temporal resolving power that is unprecedented in the exoplanetary phase mapping literature.
+Previous attempts to map this planet from the exoplanet community have suggested 
+the presence of localized surface features, but their resolving power has been 
+severely limited by the duration of observations \citep{Cowan2009}. 
+\TESS offers precise 2-minute cadence data spanning a wide range of illumination 
+phases, enabling a level of spatial and temporal resolving power that is 
+unprecedented in the exoplanetary phase mapping literature.
 
-Moreover, recent advances in fast analytic computation of spherical harmonics have made the reconstruction of such detailed maps more feasible than ever. 
+Moreover, recent advances in fast analytic computation of spherical harmonics 
+have made the reconstruction of such detailed maps more feasible than ever. 
 \todo{(STARRY)}
 
-In this work, we build on this methodological foundation to perform reflected-light mapping of planetary surface features on Sol d. 
+In this work, we build on this methodological foundation to perform 
+reflected-light mapping of planetary surface features on Sol d. 
 We give an overview of the \TESS data used in Section \ref{sec:data}. 
-In Section \ref{sec:methods}, we describe the methods employed to infer a map from these data, including the adaptation of the STARRY algorithm to reflection mapping, the modeling of spacecraft-related systematics, and the likelihood and priors used.
-We present results in Section \ref{sec:results} and make comparison of these findings to state-of-the-art terrestrial planet maps from the literature in Section \ref{sec:discussion}. 
-Finally, we conclude in Section \ref{sec:conclusion} with a look at future prospects for phase-curve mapping of terrestrial exoplanets.
+In Section \ref{sec:methods}, we describe the methods employed to infer a map 
+from these data, including the adaptation of the \starry algorithm to reflection 
+mapping, the modeling of spacecraft-related systematics, and the likelihood and 
+priors used. 
+We present results in Section \ref{sec:results} and make comparison of these 
+findings to state-of-the-art terrestrial planet maps from the literature in 
+Section \ref{sec:discussion}. 
+Finally, we conclude in Section \ref{sec:conclusion} with a look at future 
+prospects for phase-curve mapping of terrestrial exoplanets.
 
@@
 
-\todo{(outlier rejection method, trim down to x number of high-SNR lightcurves for computational tractability)}
+\todo{(outlier rejection method, trim down to x number of high-SNR lightcurves 
+for computational tractability)}
 
@@
 
-While the astrophysical signal that we wish to analyze is present in all \todo{x} extracted lightcurves, its strength is modulated by time-variable systematics that are correlated but not identical across all sources.
-\todo{The observed lightcurves can be represented as... (systematics x Earthshine equation)}
+While the astrophysical signal that we wish to analyze is present in all \todo{x} 
+extracted lightcurves, its strength is modulated by time-variable systematics 
+that are correlated but not identical across all sources. 
+\todo{The observed lightcurves can be represented as... (systematics x 
+Earthshine equation)}
 
-We choose to model this systematic component using Pixel Level Decorrelation (PLD).
-\todo{(details, math, and a figure of the bases (possibly two-panel with comparison to telescope housekeeping variables?)}
+We choose to model this systematic component using Pixel Level Decorrelation 
+(PLD). \todo{(details, math, and a figure of the bases (possibly two-panel with 
+comparison to telescope housekeeping variables?)}
 
-\subsection{Reflected-Light Mapping with STARRY}
+\subsection{Reflected-Light Mapping with \starry}
 
-\todo{(brief recap of STARRY)}
+\todo{(brief recap of \starry)}
 
-\todo{(adapting STARRY to reflected light/variable illumination phase - possibly make the gritty math details be an appendix?)}
+\todo{(adapting \starry to reflected light/variable illumination phase - 
+possibly make the gritty math details be an appendix?)}
 
@@
 \label{sec:results}
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/phases.pdf}
+    \caption{\label{fig:phases}
+             \tess view of Sol d on every date in Sectors 1
+             and 2 that was included in the regression. Each image is
+             labeled with the corresponding timestamp in TJD.
+             \codelink{EarthView}
+             }
+    \end{centering}
+\end{figure}
 
@@
 
-\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} for useful conversations.
-Crucial parts of this work were carried out at the TESS Data Workshop, hosted by Space Telescope Science Institute, and the Building Early Science with TESS Workshop, hosted by the University of Chicago.}
+\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
+acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
+for useful conversations. Crucial parts of this work were carried out at the 
+TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
+Building Early Science with TESS Workshop, hosted by the University of Chicago.}
 \facility{TESS}
-\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2019}, TensorFlow}
+\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow}
 % Bibliography

### 2019-03-24 earthshine/__init__.py

@@ -1,2 +1,2 @@
-from .model import design_matrix, tess_earth_vector
-from .animate import animate
+from .model import design_matrix, tess_earth_vector, visibility
+from .animate import animate, render

### 2019-03-24 earthshine/animate.py

@@ -15,7 +15,83 @@ REARTH = 1.0 / 6371.0
 TJD0 = 2457000
 cmap = plt.get_cmap("plasma")
 
-__all__ = ["animate"]
+__all__ = ["animate", "render"]
+
+
+def render(map, time, time0, phase0=0.0, res=75):
+    """
+
+    """
+    # Load the SPICE data
+    ephemFiles = glob.glob('../data/TESS_EPH_PRE_LONG_2018*.bsp')
+    tlsFile = '../data/tess2018338154046-41240_naif0012.tls'
+    solarSysFile = '../data/tess2018338154429-41241_de430.bsp'
+    #print(spice.tkvrsn('TOOLKIT'))
+    for ephFil in ephemFiles:
+        spice.furnsh(ephFil)
+    spice.furnsh(tlsFile)
+    spice.furnsh(solarSysFile)
+
+    # JD time
+    et = spice.unitim(time + TJD0, 'JDTDB', 'ET')
+
+    # Calculate positions of TESS, the Earth, and the Sun
+    # Note that our reference frame is that of `starry`,
+    # where `y` points *north*.
+    # This is just the rotation {x, y, z} --> {z, x, y}
+    # relative to the J200 mean equatorial coordinates.
+    tess = np.zeros(3)
+    sun = np.zeros(3)
+    outTuple = spice.spkezr('Mgs Simulation', et, 'J2000', 'NONE', 'Earth')
+    tess[0] = outTuple[0][1] * REARTH
+    tess[1] = outTuple[0][2] * REARTH
+    tess[2] = outTuple[0][0] * REARTH
+    outTuple = spice.spkezr('Sun', et, 'J2000', 'NONE', 'Earth')
+    sun[0] = outTuple[0][1] * REARTH
+    sun[1] = outTuple[0][2] * REARTH
+    sun[2] = outTuple[0][0] * REARTH
+
+    north_pole = np.empty(3)
+    vernal_eq = np.empty(3)
+    tess_hat = tess / np.sqrt(np.sum(tess ** 2))
+    sun_hat = sun / np.sqrt(np.sum(sun ** 2))
+    y = np.array(map[:, :, :])
+
+    # Rotate the earth to the current phase in the original frame
+    map.axis = [0, 1, 0]
+    phase = (360. * (time - time0)) % 360. + phase0
+    R = starry.RAxisAngle([0, 1, 0], phase)
+    map.rotate(phase)
+
+    # Rotate the earth and the sun into tess' frame  
[…]

### 2019-03-24 earthshine/model.py

@@ -10,7 +10,7 @@ assert starry.__version__ == "1.0.0.dev0", \
 REARTH = 1.0 / 6371.0
 TJD0 = 2457000
 
-__all__ = ["design_matrix", "tess_vector"]
+__all__ = ["design_matrix", "tess_vector", "visibility"]
 
 
 def tess_earth_vector(time):
@@ -138,3 +138,118 @@ def design_matrix(time, ydeg=10, nt=2, period=1.0, phase0=0.0,
         X00 = np.array(X[:, 0])
         X = np.delete(X, [n * map.Ny for n in range(map.nt)], axis=1)
         return X, X00
+
+
+def visibility(time, phase0=0.0, res=100):
+    """
+
+    """
+    # Load the SPICE data
+    ephemFiles = glob.glob('../data/TESS_EPH_PRE_LONG_2018*.bsp')
+    tlsFile = '../data/tess2018338154046-41240_naif0012.tls'
+    solarSysFile = '../data/tess2018338154429-41241_de430.bsp'
+    #print(spice.tkvrsn('TOOLKIT'))
+    for ephFil in ephemFiles:
+        spice.furnsh(ephFil)
+    spice.furnsh(tlsFile)
+    spice.furnsh(solarSysFile)
+
+    # JD time range
+    allTJD = time + TJD0
+    nT = len(allTJD)
+    allET = np.zeros((nT,), dtype=np.float)
+    for i, t in enumerate(allTJD):
+        allET[i] = spice.unitim(t, 'JDTDB', 'ET')
+
+    # Calculate positions of TESS, the Earth, and the Sun
+    # Note that our reference frame is that of `starry`,
+    # where `y` points *north*.
+    # This is just the rotation {x, y, z} --> {z, x, y}
+    # relative to the J200 mean equatorial coordinates.
+    tess = np.zeros((3, len(allET)))
+    sun = np.zeros((3, len(allET)))
+    for i, et in enumerate(allET):
+        outTuple = spice.spkezr('Mgs Simulation', et, 'J2000', 'NONE', 'Earth')
+        tess[0, i] = outTuple[0][1] * REARTH
+        tess[1, i] = outTuple[0][2] * REARTH
+        tess[2, i] = outTuple[0][0] * REARTH
+        outTuple = spice.spkezr('Sun', et, 'J2000', 'NONE', 'Earth')
+        sun[0, i] = outTuple[0][1] * REARTH
[…]

### 2019-03-24 notebooks/notebook_setup.py

@@ -9,4 +9,5 @@ rcParams["figure.figsize"] = 12, 4
 rcParams["font.size"] = 16
 rcParams["text.usetex"] = False
 rcParams["font.family"] = ["sans-serif"]
+rcParams["font.sans-serif"] = ["cmss10"]
 rcParams["axes.unicode_minus"] = False

### 2019-03-24 tex/figures/pretty_function.py

@@ -1,22 +1,0 @@
-"""Plot the function sin(1 / XY)."""
-
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Compute sin(1 / xy)
-sz = 1000
-X = np.linspace(-1, 1, sz)
-Y = np.linspace(-1, 1, sz)
-X, Y = np.meshgrid(X, Y)
-Z = np.sin(1 / (X * Y))
-
-# Plot it
-fig, ax = plt.subplots(1)
-im = ax.imshow(Z, cmap=plt.get_cmap("plasma"),
-               origin="lower", extent=(-1, 1, -1, 1))
-plt.colorbar(im, shrink=1, aspect=10)
-ax.set_xlabel("X", fontsize=16)
-ax.set_ylabel("Y", fontsize=16)
-
-# Save it
-fig.savefig("pretty_function.pdf", bbox_inches="tight")

### 2019-03-24 tex/gen_links.py

@@ -3,6 +3,4 @@ import os
 hash = subprocess.check_output(['git', 'rev-parse', 'HEAD']).decode("utf-8")[:-1]
 slug = os.getenv("TRAVIS_REPO_SLUG", "user/repo")
 with open("gitlinks.tex", "w") as f:
-    print(r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.py}{\codeicon}\,\,}" % (slug, hash), file=f)
-    print(r"\newcommand{\animlink}[1]{\href{https://github.com/%s/blob/%s/tex/figures/#1.gif}{\animicon}\,\,}" % (slug, hash), file=f)
-    print(r"\newcommand{\prooflink}[1]{\href{https://github.com/%s/blob/%s/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}" % (slug, hash), file=f)
+    print(r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/notebooks/#1.ipynb}{\codeicon}\,\,}" % (slug, hash), file=f)

### 2019-03-24 tex/ms.tex
added all figs

@@
 
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/phases.pdf}
+    \caption{\label{fig:phases}
+             \tess view of Sol d on every date in Sectors 1
+             and 2 that was included in the regression. Each image is
+             labeled with the corresponding timestamp in TJD. 
+             \codelink{EarthView}
+             }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/data.pdf}
+    \caption{\label{fig:data}
+             Normalized background flux in each of ten postage stamps
+             for each of Sectors 1 and 2. Cadences where Sol d was
+             below or very close to the edge of the sunshade were masked.
+             While the planet is in view for the majority of both orbits
+             in Sector 1, it is only visible in the data at the very end
+             of each orbit in Sector 2.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
+
 \subsection{Systematics Modeling}
@@
 \subsection{Reflected-Light Mapping with \starry}
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/starry_model.pdf}
+    \caption{\label{fig:starry_model}
+             Normalized surface reflectance versus time for the maximum
+             likelihood \starry model in each of the four orbits of \tess
+             in Sectors 1 and 2.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
 
@@
     \begin{centering}
-    \includegraphics[width=\linewidth]{figures/phases.pdf}
-    \caption{\label{fig:phases}
-             \tess view of Sol d on every date in Sectors 1
-             and 2 that was included in the regression. Each image is
-             labeled with the corresponding timestamp in TJD.
-             \codelink{EarthView}
+    \includegraphics[width=\linewidth]{figures/model.pdf}
+    \caption{\label{fig:model}
+             \emph{Top:} Median flux across all postage stamps (black) and
+             the median maximum likelihood model (blue) across Sectors 1 and 2.
+             \emph{Bottom:} Median residuals about the maximum likelihood fit.
+             \codelink{earthshine_S1_S2}
              }
@@
 \todo{(present results with \& without time variability)}
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/map.pdf}
+    \caption{\label{fig:map}
+             \emph{Top:} The maximum likelihood model for the surface albedo
+             of Sol d, weighted by the visibility across Sectors 1 and 2. The
+             dashed white lines indicate latitudes above/below which the
+             visibility drops below 50\%. Black contours indicate coastlines
+             derived from current state-of-the-art models of the surface geography 
+             of Sol d.
+             \emph{Bottom:} Actual corrected surface reflectance in the red band of the
+             \emph{VIIRS} imager, averaged over the same date range and weighted
+             by the same visibility function. This bandpass covers only about one
+             quarter of the \tess bandpass, so deviations between the two images
+             are to be expected.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
+
+The bottom panel of Figure~\ref{fig:map} shows the corrected surface
+reflectance obtained from the
+Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
+Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite. The 
+image shows the corrected surface reflectance in the I1 band of the instrument,
+averaged over the 28 days of data analyzed in this work, and weighted by the
+\tess visibility as in the top panel.
+The I1 band extends from 0.6 to 0.68 $\mu\mathrm{m}$
+\footnote{\url{http://rammb.cira.colostate.edu/projects/npp/VIIRS_bands_and_bandwidths.pdf}},
+and therefore covers only about one-fourth of the bandpass of \tess
+(nominally 0.6 - 1.0 $\mu\mathrm{m}$).
 

### 2019-03-24 tex/gen_links.py

@@ -1,6 +1,6 @@
 import subprocess
 import os
 hash = subprocess.check_output(['git', 'rev-parse', 'HEAD']).decode("utf-8")[:-1]
-slug = os.getenv("TRAVIS_REPO_SLUG", "user/repo")
+slug = os.getenv("TRAVIS_REPO_SLUG", "rodluger/earthshine")
 with open("gitlinks.tex", "w") as f:
     print(r"\newcommand{\codelink}[1]{\href{https://github.com/%s/blob/%s/notebooks/#1.ipynb}{\codeicon}\,\,}" % (slug, hash), file=f)

### 2019-03-24 tex/ms.tex
force date to be April 1

@@
 Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
-Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite. The 
-image shows the corrected surface reflectance in the I1 band of the instrument,
-averaged over the 28 days of data analyzed in this work, and weighted by the
-\tess visibility as in the top panel.
+Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite
+\footnote{Data obtained via 
+\href{https://github.com/rodluger/earthshine/blob/master/tex/figures/viirs.sh}{this wget script}.}. 
+The image shows the corrected surface reflectance in the I1 band of the instrument,
+averaged over the 28 days of data analyzed in this work, smoothed with a Gaussian
+filter, and weighted by the \tess visibility as in the top panel.
 The I1 band extends from 0.6 to 0.68 $\mu\mathrm{m}$

### 2019-03-24 tex/figures/viirs.sh

@@ -1,0 +1,28 @@
+wget -O 2018-07-25.jpeg "https://wvs.earthdata.nasa.gov/api/v1/snapshot?REQUEST=GetSnapshot&TIME=2018-07-25&BBOX=-90.0,-180.0,90.0,180.0&CRS=EPSG:4326&LAYERS=VIIRS_SNPP_CorrectedReflectance_TrueColor&FORMAT=image/jpeg&WIDTH=4099&HEIGHT=2052&ts=1552923852099"
+wget -O 2018-07-26.jpeg "https://wvs.earthdata.nasa.gov/api/v1/snapshot?REQUEST=GetSnapshot&TIME=2018-07-26&BBOX=-90.0,-180.0,90.0,180.0&CRS=EPSG:4326&LAYERS=VIIRS_SNPP_CorrectedReflectance_TrueColor&FORMAT=image/jpeg&WIDTH=4099&HEIGHT=2052&ts=1552923852099"
+wget -O 2018-07-27.jpeg "https://wvs.earthdata.nasa.gov/api/v1/snapshot?REQUEST=GetSnapshot&TIME=2018-07-27&BBOX=-90.0,-180.0,90.0,180.0&CRS=EPSG:4326&LAYERS=VIIRS_SNPP_CorrectedReflectance_TrueColor&FORMAT=image/jpeg&WIDTH=4099&HEIGHT=2052&ts=1552923852099"
+wget -O 2018-07-28.jpeg "https://wvs.earthdata.nasa.gov/api/v1/snapshot?REQUEST=GetSnapshot&TIME=2018-07-28&BBOX=-90.0,-180.0,90.0,180.0&CRS=EPSG:4326&LAYERS=VIIRS_SNPP_CorrectedReflectance_TrueColor&FORMAT=image/jpeg&WIDTH=4099&HEIGHT=2052&ts=1552923852099"
+wget -O 2018-07-29.jpeg "https://wvs.earthdata.nasa.gov/api/v1/snapshot?REQUEST=GetSnapshot&TIME=2018-07-29&BBOX=-90.0,-180.0,90.0,180.0&CRS=EPSG:4326&LAYERS=VIIRS_SNPP_CorrectedReflectance_TrueColor&FORMAT=image/jpeg&WIDTH=4099&HEIGHT=2052&ts=1552923852099"
[…]

### 2019-03-24 tex/ms.tex
another fig

@@
     \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/geometry.pdf}
+    \caption{\label{fig:geometry}
+             Geometry of the \starry model.
+             \codelink{Geometry}
+             }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
+    \begin{centering}
     \includegraphics[width=\linewidth]{figures/starry_model.pdf}
@@
 possibly make the gritty math details be an appendix?)}
+
+The illumination is
+%
+\begin{align}
+    I(b; x, y, z) = \sqrt{1 - b^2}y - bz
+    \label{eq:illum}
+\end{align}
+%
+
+The problem can then be reduced to solving integrals of the form
+%
+\begin{align}
+    \int_{-1}^{1} \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}} x^i y^j z^k \mathrm{d} y \ \mathrm{d} x
+    \label{eq:integral}
+\end{align}
+%
+where $i$ and $j$ are non-negative integers and $k = 0$ or $1$.
 
@@
 Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
-Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite
+Suomi National Polar-orbiting Partnership (\emph{S-NPP}) satellite
 \footnote{Data obtained via 

### 2019-03-24 tex/ms.tex
added starry description

@@
     \caption{\label{fig:geometry}
-             Geometry of the \starry model.
+             Geometry of the \starry model. In this frame, the $y$ axis points up, 
+             the $x$ axis points to the right, and the $z$ axis points out of the page.
+             The planet has unit radius and sits at the origin, while
+             the illumination source is along the $y-z$ plane, with the sub-stellar point is
+             marked by a dot. The semi-major axis of the terminator is unity, and
+             the semi-minor axis of the terminator is denoted $b$. The night side
+             is colored black.
              \codelink{Geometry}
@@
 
-\todo{(adapting \starry to reflected light/variable illumination phase - 
-possibly make the gritty math details be an appendix?)}
+In \cite{Luger2019} we described how to transform between spherical
+harmonic coefficients and coefficients in the polynomial basis $\tilde{p}$, whose
+terms are of the form $x^i y^j z^k$ for (non-negative) integer $i$ and $j$ 
+and $k = 0$ or $1$. Given a representation of a surface map in terms of
+a set of coefficients in $\tilde{p}$, we showed how to compute the visible
+flux by integrating each of the terms in $\tilde{p}$ across the visible
+surface of the projected disk. For unocculted spheres observed in emitted
+light, the area of integration was the full disk, which made the integration
+trivial: the flux contribution from each term in $\tilde{p}$ was a constant
+easily computed via recursion relations involving factorials.
 
-The illumination is
+In the present work, we are interested in \emph{reflected} light, so we must
+account for the illumination by the star, which varies smoothly
+across the dayside of the planet but whose derivative discontinuously changes at the 
+terminator, beyond which the illumination is zero everywhere. This requires
+two modifications to the \starry algorithm: we must (1) weight all integrands
+by the illumination function on the dayside, and (2) modify the integration
+limits to truncate the integrals at the day/night terminator.
+
+Let us consider a right-handed coordinate frame in which the planet has unit 
+radius and is located at the origin, the illumination source is along the $y-z$
+plane, and the sub-stellar point is on the $+y$ axis at $x = 0$
+(see Figure~\ref{fig:geometry}). In this frame, the terminator is a segment of
+an ellipse, with semi-major axis $a=1$ aligned with the $x$ axis and
+semi-minor axis $b$. It is straightforward to show that the sub-stellar point
+is located at $y=\sqrt{1 - b^2}$ and the illumination is given by
 %
 \begin{align}
-    I(b; x, y, z) = \sqrt{1 - b^2}y - bz
+    I(b; x, y) &= 
+    \begin{dcases}
+        \sqrt{1 - b^2}y - bz & 
+            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+            y \geq -b \sqrt{1 - x^2}
+        \\
+        0 & 
+            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+            \mathrm{otherwise}
+    \end{dcases}
+    \quad ,
     \label{eq:illum}
@@
 %
-
-The problem can then be reduced to solving integrals of the form
+where $z = \sqrt{1 - x^2 - y^2}$.
+%
+Since the illumination function is just a polynomial in $x$, $y$, and $z$,
+weighting the terms in $\tilde{p}$ by this function keeps all terms within the
+polynomial basis.
+Provided we always rotate the problem such that the
+sub-stellar point lies along the $+y$ axis as above, the limits of integration
+are $-1 \leq x \leq 1$ and $b\sqrt{1 - x^2} \leq y \leq \sqrt{1 - x^2}$.
+Computing the total reflected flux for any surface map is therefore a matter
+of solving integrals of the form
 %
 \begin{align}
-    \int_{-1}^{1} \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}} x^i y^j z^k \mathrm{d} y \ \mathrm{d} x
+    J_{ijk}(b) &= \int_{-1}^{1} \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}} x^i y^j z^k \mathrm{d} y \ \mathrm{d} x
+    \nonumber\\
+    &=
+    \frac{
+        \Gamma\left(\frac{i + 1}{2}\right) \Gamma\left(\frac{j + 1}{2}\right)
+    }{
+        2 \Gamma\left(\frac{i + j + k + 4}{2}\right)
+    }
+    \begin{dcases}
+        0
+        &
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+        i \, \mathrm{odd}
+        %
+        \\
+        %
+            1 - b^{j + 1}
+        & 
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+        k = 0
+        %
+        \\
+        %
+        \frac{\sqrt{\pi}}{2} - b^{j + 1}\Gamma\left(\frac{j + 4}{2}\right)
+        {_2\tilde{F}_1} \left( -\frac{1}{2}, \frac{j + 1}{2}; \frac{j + 3}{2}; b^2\right)
+        & 
+        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+        k = 1
+    \end{dcases}
+    \quad ,
     \label{eq:integral}
@@
 %
-where $i$ and $j$ are non-negative integers and $k = 0$ or $1$.
-
-\todo{(time variability of surface features)}
+where ${_2\tilde{F}_1}$ is the regularized hypergeometric function. For all values
+of $i$, $j$, and $k$ in $\tilde{p}$, ${_2\tilde{F}_1}$ reduces to simple
+trigonometric functions involving $b$. Moreover, it is straightforward to
+derive recursion relations for $J_{ijk}(b)$, making its evaluation extremely fast.
+The algorithm for computing $J_{ijk}(b)$ is implemented in the development version
+of \starry and will be discussed further in upcoming work.
 

### 2019-03-25 tex/ms.tex
map labels
more text

@@
 
-\todo{(figure showing lightcurves for various targets)}
-
-\section{Methods}
-\label{sec:methods}
-
-\begin{figure}[ht!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/phases.pdf}
-    \caption{\label{fig:phases}
-             \tess view of Sol d on every date in Sectors 1
-             and 2 that was included in the regression. Each image is
-             labeled with the corresponding timestamp in TJD. 
-             \codelink{EarthView}
-             }
-    \end{centering}
-\end{figure}
+Figure showing lightcurves for various targets: Figure~\ref{fig:data}.
 
@@
              \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
+
+\section{Methods}
+\label{sec:methods}
+
+\subsection{Orbital Modeling}
+
+We downloaded 
+\footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
+the Solar System and \tess ephemeris data for
+Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
+to convert the TDB timestamps to 
+ephemeris time (ET). We then used the \textsf{spkezr} utility to compute
+the relative positions of Sol, Sol d, and \tess for every cadence
+in our dataset in the J2000 equatorial reference frame. In this right-handed
+coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
+planet's spin axis, and the $x$ axis points toward the vernal equinox. We
+do not apply any light travel correction, as the expected delay is on the order
+of a few seconds.
+
+At any given cadence, we rotate Sol d about its spin axis to the correct phase,
+assuming a rotational period of $1.00$ day. We determine the initial rotation
+phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
+%
+\begin{align}
+\mathrm{ERA} = 360^\circ(0.7790572732640 + 1.00273781191135448 \, t_U) \, \mathrm{mod} \, 360^\circ
+\end{align}
+%
+where $t_U = t - 2451545.0$. At $t = t_0 = 2458325.5$, the first timestamp in our dataset,
+we find $\mathrm{ERA} = 303.4^\circ$, meaning the vernal equinox will be aligned with
+the prime meridian $360^\circ - 303.4^\circ = 56.6^\circ = 3.77$ hours past $t_0$.
+%
+Finally, we rotate the frame to align
+\tess with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/phases.pdf}
+    \caption{\label{fig:phases}
+             \tess view of Sol d on every date in Sectors 1
+             and 2 that was included in the regression. Each image is
+             labeled with the corresponding timestamp in TJD. 
+             \codelink{EarthView}
              }
@@
 
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/map_labels.pdf}
+    \caption{\label{fig:map_labels}
+             Labeled map of Sol d.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
+
 \todo{(comparison of inferred features to ``model'' (Earth))}
+
+No zonal cloud bands: prior.
 
@@
 \facility{TESS}
-\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow}
+\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow, \spiceypy \citep{Annex2019}}
 % Bibliography

### 2019-03-25 earthshine/animate.py

@@ -6,6 +6,7 @@ from matplotlib.patches import Wedge
 from IPython.display import HTML
 from tqdm import tqdm
 import glob
+import os
 import starry
 assert starry.__version__ == "1.0.0.dev0", \
     "This code requires the `starry` version 1.0.0.dev0."
@@ -14,6 +15,7 @@ assert starry.__version__ == "1.0.0.dev0", \
 REARTH = 1.0 / 6371.0
 TJD0 = 2457000
 cmap = plt.get_cmap("plasma")
+path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 
 __all__ = ["animate", "render"]
 
@@ -23,9 +25,9 @@ def render(map, time, time0, phase0=0.0, res=75):
 
     """
     # Load the SPICE data
-    ephemFiles = glob.glob('../data/TESS_EPH_PRE_LONG_2018*.bsp')
-    tlsFile = '../data/tess2018338154046-41240_naif0012.tls'
-    solarSysFile = '../data/tess2018338154429-41241_de430.bsp'
+    ephemFiles = glob.glob(path + 'TESS_EPH_PRE_LONG_2018*.bsp')
+    tlsFile = path + 'tess2018338154046-41240_naif0012.tls'
+    solarSysFile = path + 'tess2018338154429-41241_de430.bsp'
     #print(spice.tkvrsn('TOOLKIT'))
     for ephFil in ephemFiles:
         spice.furnsh(ephFil)
@@ -100,9 +102,9 @@ def animate(map, time, phase0=0.0, res=75, interval=75):
 
     """
     # Load the SPICE data
-    ephemFiles = glob.glob('../data/TESS_EPH_PRE_LONG_2018*.bsp')
-    tlsFile = '../data/tess2018338154046-41240_naif0012.tls'
-    solarSysFile = '../data/tess2018338154429-41241_de430.bsp'
+    ephemFiles = glob.glob(path + 'TESS_EPH_PRE_LONG_2018*.bsp')
+    tlsFile = path + 'tess2018338154046-41240_naif0012.tls'
+    solarSysFile = path + 'tess2018338154429-41241_de430.bsp'
     #print(spice.tkvrsn('TOOLKIT'))
     for ephFil in ephemFiles:
         spice.furnsh(ephFil)

### 2019-03-25 earthshine/model.py

@@ -2,6 +2,7 @@ import spiceypy as spice
 import glob
 from tqdm import tqdm
 import numpy as np
+import os
 import starry
 assert starry.__version__ == "1.0.0.dev0", \
     "This code requires the `starry` version 1.0.0.dev0."
@@ -9,6 +10,7 @@ assert starry.__version__ == "1.0.0.dev0", \
 # Constants
 REARTH = 1.0 / 6371.0
 TJD0 = 2457000
+path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 
 __all__ = ["design_matrix", "tess_vector", "visibility"]
 
@@ -16,9 +18,9 @@ __all__ = ["design_matrix", "tess_vector", "visibility"]
 def tess_earth_vector(time):
     """Return the cartesian position of TESS relative to the Earth."""
     # Load the SPICE data
-    ephemFiles = glob.glob('../data/TESS_EPH_PRE_LONG_2018*.bsp')
-    tlsFile = '../data/tess2018338154046-41240_naif0012.tls'
-    solarSysFile = '../data/tess2018338154429-41241_de430.bsp'
+    ephemFiles = glob.glob(path + 'TESS_EPH_PRE_LONG_2018*.bsp')
+    tlsFile = path + 'tess2018338154046-41240_naif0012.tls'
+    solarSysFile = path + 'tess2018338154429-41241_de430.bsp'
     for ephFil in ephemFiles:
         spice.furnsh(ephFil)
     spice.furnsh(tlsFile)
@@ -60,9 +62,9 @@ def design_matrix(time, ydeg=10, nt=2, period=1.0, phase0=0.0,
     map = starry.Map(ydeg=ydeg, udeg=0, reflected=True, nt=nt)
 
     # Load the SPICE data
-    ephemFiles = glob.glob('../data/TESS_EPH_PRE_LONG_2018*.bsp')
-    tlsFile = '../data/tess2018338154046-41240_naif0012.tls'
-    solarSysFile = '../data/tess2018338154429-41241_de430.bsp'
+    ephemFiles = glob.glob(path + 'TESS_EPH_PRE_LONG_2018*.bsp')
+    tlsFile = path + 'tess2018338154046-41240_naif0012.tls'
+    solarSysFile = path + 'tess2018338154429-41241_de430.bsp'
     #print(spice.tkvrsn('TOOLKIT'))
     for ephFil in ephemFiles:
[…]

### 2019-03-25 tex/ms.tex
woot

@@
 
+Figure~\ref{fig:phases} shows the view \tess has of Sol d on each of the dates
+in our dataset; these images were produced by applying the sequences of rotations
+described above. The planet is illuminated by Sol assuming it is a point source,
+and the night side is shaded black. The map of Sol d shown in this figure is 
+based on current models of the actual distribution of continents on the planet.
+Note that although the images are computed an integer number of rotation periods
+apart, the planet appears to slowly rotate over the course of the observation.
+This is because of the orbit of \tess, which changes its vantage point relative
+to Sol d over the course of its 13 day orbit.
+
 \begin{figure}[ht!]
@@
              and 2 that was included in the regression. Each image is
-             labeled with the corresponding timestamp in TJD. 
+             labeled with the corresponding timestamp in TJD. The images
+             shown here correspond to current models of the continental coverage
+             of Sol d, not to the map inferred in this study.
              \codelink{EarthView}

### 2019-03-25 tex/ms.tex
more text

@@
 
+\todo{TJD = BJD - 2457000}
+
 \todo{(outlier rejection method, trim down to x number of high-SNR lightcurves 
@@
 Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
-to convert the TDB timestamps to 
+to convert the TJD timestamps to 
 ephemeris time (ET). We then used the \textsf{spkezr} utility to compute
@@
 
-Figure~\ref{fig:phases} shows the view \tess has of Sol d on each of the dates
-in our dataset; these images were produced by applying the sequences of rotations
-described above. The planet is illuminated by Sol assuming it is a point source,
-and the night side is shaded black. The map of Sol d shown in this figure is 
-based on current models of the actual distribution of continents on the planet.
-Note that although the images are computed an integer number of rotation periods
-apart, the planet appears to slowly rotate over the course of the observation.
-This is because of the orbit of \tess, which changes its vantage point relative
-to Sol d over the course of its 13 day orbit.
-
 \begin{figure}[ht!]
@@
 
+Figure~\ref{fig:phases} shows the view \tess has of Sol d on each of the dates
+in our dataset; these images were produced by applying the sequences of rotations
+described above. The planet is illuminated by Sol assuming it is a point source,
+and the night side is shaded black. The map of Sol d shown in this figure is 
+based on current models of the actual distribution of continents on the planet.
+Note that although the images are computed an integer number of rotation periods
+apart, the planet appears to slowly rotate over the course of the observation.
+This is because of the orbit of \tess, which changes its vantage point relative
+to Sol d over the course of its 13 day orbit.
+
 \subsection{Systematics Modeling}
+\label{sec:systematics}
 
-While the astrophysical signal that we wish to analyze is present in all \todo{x} 
+While the astrophysical signal that we wish to analyze is present in all 
 extracted lightcurves, its strength is modulated by time-variable systematics 
-that are correlated but not identical across all sources. 
-\todo{The observed lightcurves can be represented as... (systematics x 
-Earthshine equation)}
+that are correlated but not identical across all postage stamps, since the
+illumination of the CCD by Sol d is strongly inhomogeneous. A physical
+model of the reflections and scattering that gives rise to the
+signal of Sol d on the \tess detector is beyond the scope of this work. Instead,
+we treat this as a de-trending problem, where the signal we wish to fit is
+shared by all postage stamps, but multiplied by a systematic signal that is
+different for each target. This problem is precisely what the technique of
+pixel-level decorelation \citep[PLD;][]{Deming2015, Luger2016, Luger2018a}
+seeks to address. In PLD, one computes the sum over all light curves at each
+point in time, and uses this quantity to normalize each of the individual
+light curves. Since (by assumption) each light curve is the product of the astrophysical
+signal and the systematics signal, this procedure divides out the astrophysical
+signal, producing a basis of vectors that contain \emph{only} functions of the
+systematics. This now serves as a ``clean'' basis one can then use to fit the
+data, with minimal risk of fitting out astrophysical signals.
 
-We choose to model this systematic component using Pixel Level Decorrelation 
-(PLD). \todo{(details, math, and a figure of the bases (possibly two-panel with 
-comparison to telescope housekeeping variables?)}
+We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
+increase the flexibility of the systematics model, we append to $\mathrm{B}$ 5 orthogonal
+polynomials in time for each of the two orbits of \tess in each sector.
+The systematics model $\mathbf{b}$ for the $n^\mathrm{th}$ signal is thus
+%
+\begin{align}
+\mathbf{b}_n = \mathbf{B} \mathbf{w}_n
+\end{align}
+%
+where $\mathbf{w}_n$ are the weights of each regressor.
+Since we solve for different weights for each of the 75 light curves in Sector 1
+and 20 light curves in Sector 2, our systematics model has
+$75 \times (75 + 2 \times 5) + 20 \times (20 + 2 \times 5) = 6,975$ free parameters.
+Since the total number of data points is $912,605$, overfitting is not particularly
+concerning, but we nevertheless impose an L2 prior on the weights with
+standard deviation $\sigma_B = 0.1$.
 
 \subsection{Reflected-Light Mapping with \starry}
+\label{sec:starry}
+
+We model the astrophysical component of the signal---the rotational modulation
+of Sol d in reflected light---using the \starry code package \citep{Luger2019}.
+\starry computes phase curves and occultation light curves for bodies whose
+surfaces are expressed as a sum of spherical harmonics. 
+The algorithm works by first transforming
+from spherical harmonic coefficients to coefficients in the polynomial basis $\tilde{p}$, whose
+terms are of the form $x^i y^j z^k$ for (non-negative) integer $i$ and $j$ 
+and $k = 0$ or $1$. \citet{Luger2019} showed how to compute the visible
+flux by integrating each of the terms in $\tilde{p}$ across the visible
+surface of the projected disk. For unocculted spheres observed in emitted
+light, the area of integration is the full disk, which makes the integration
+trivial: the flux contribution from each term in $\tilde{p}$ is a constant
+easily computed via recursion relations involving factorials. The algorithm is
+thus extremely fast and very precise.
+
+However, in the present work, we are interested in \emph{reflected} light, so we must
+account for the illumination by the star, which varies smoothly
+across the dayside of the planet but whose derivative discontinuously changes at the 
+terminator, beyond which the illumination is zero everywhere. This requires
+two modifications to the \starry algorithm: we must (1) weight all integrands
+by the illumination function on the dayside, and (2) modify the integration
+limits to truncate the integrals at the day/night terminator.
 
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/geometry.pdf}
+    \includegraphics[width=0.4\linewidth]{figures/geometry.pdf}
     \caption{\label{fig:geometry}
-             Geometry of the \starry model. In this frame, the $y$ axis points up, 
+             Geometry of the \starry model in reflected light. In this frame, 
+             the $y$ axis points up, 
              the $x$ axis points to the right, and the $z$ axis points out of the page.
@@
 \end{figure}
-
-\begin{figure}[ht!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/starry_model.pdf}
-    \caption{\label{fig:starry_model}
-             Normalized surface reflectance versus time for the maximum
-             likelihood \starry model in each of the four orbits of \tess
-             in Sectors 1 and 2.
-             \codelink{earthshine_S1_S2}
-             }
-    \end{centering}
-\end{figure}
-
-\todo{(brief recap of \starry)}
-
-In \cite{Luger2019} we described how to transform between spherical
-harmonic coefficients and coefficients in the polynomial basis $\tilde{p}$, whose
-terms are of the form $x^i y^j z^k$ for (non-negative) integer $i$ and $j$ 
-and $k = 0$ or $1$. Given a representation of a surface map in terms of
-a set of coefficients in $\tilde{p}$, we showed how to compute the visible
-flux by integrating each of the terms in $\tilde{p}$ across the visible
-surface of the projected disk. For unocculted spheres observed in emitted
-light, the area of integration was the full disk, which made the integration
-trivial: the flux contribution from each term in $\tilde{p}$ was a constant
-easily computed via recursion relations involving factorials.
-
-In the present work, we are interested in \emph{reflected} light, so we must
-account for the illumination by the star, which varies smoothly
-across the dayside of the planet but whose derivative discontinuously changes at the 
-terminator, beyond which the illumination is zero everywhere. This requires
-two modifications to the \starry algorithm: we must (1) weight all integrands
-by the illumination function on the dayside, and (2) modify the integration
-limits to truncate the integrals at the day/night terminator.
 
@@
 derive recursion relations for $J_{ijk}(b)$, making its evaluation extremely fast.
-The algorithm for computing $J_{ijk}(b)$ is implemented in the development version
-of \starry and will be discussed further in upcoming work.
+We implemented the algorithm for computing $J_{ijk}(b)$ in the development version
+of \starry
+\footnote{\url{https://github.com/rodluger/starry/tree/linear}}
+and will be discussed in detail in upcoming work.
+
+\begin{figure}[ht!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/starry_model.pdf}
+    \caption{\label{fig:starry_model}
+             Normalized surface reflectance versus time for the maximum
+             likelihood \starry model in each of the four orbits of \tess
+             in Sectors 1 and 2.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
+
+As with the systematics model (\S\ref{sec:systematics}), the model
+for the astrophysical signal is \emph{linear}: the total signal $\mathbf{a}$ 
+is a linear operation on the vector of spherical harmonic coefficients 
+that describes the body's surface:
+%
+\begin{align}
+    \mathbf{a} = \mathbf{A} \mathbf{y}
+\end{align}
+%
+where $\mathbf{A}$ is the design matrix \citep[equal to the quantity 
+$\mathbf{s}^\top\mathcal{A}\mathbf{R}'\mathbf{R}$ in][]{Luger2019}
+and $\mathbf{y}$ is the vector of spherical harmonic coefficients. As we will
+see next, the linearity of the problem makes it easily invertible.
 
 \subsection{Likelihood Function \& Inference}
+
+Our full model for the flux in the $n^\mathrm{th}$ postage stamp is thus
+%
+\begin{align}
+\mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
+\end{align}
+%
+where $\circ$ denotes the element-wise product of two vectors.
 

### 2019-03-25 tex/ms.tex
still writing

@@
 and $\mathbf{y}$ is the vector of spherical harmonic coefficients. As we will
-see next, the linearity of the problem makes it easily invertible.
+see below, the linearity of the problem makes it easily invertible.
 
-\subsection{Likelihood Function \& Inference}
+Finally, for reference, in Figure~\ref{fig:starry_model} we plot the
+\starry model for our maximum likelihood fit (\S\ref{sec:results}). The
+sharp rise at the beginning of each orbit in Sector 1 is due to the changing
+vantage point of \tess as Sol d transitions from a thin crescent to full phase.
 
-Our full model for the flux in the $n^\mathrm{th}$ postage stamp is thus
+\subsection{Full Model and Likelihood Function}
+
+Our full model for the flux in the $n^\mathrm{th}$ postage stamp is
 %
@@
 
-\todo{(present results with \& without time variability)}
-
 \begin{figure}[t!]
@@
 \end{figure}
+
+Figure~\ref{fig:model} shows the median model.  \todo{More on this here.}
+
+The top panel of Figure~\ref{fig:map} shows the maximum likelihood map of Sol d.
+\todo{More on this here.}
 
@@
     \caption{\label{fig:map_labels}
-             Labeled map of Sol d.
+             Map of Sol d with the major features indicated with suggested
+             names.
              \codelink{earthshine_S1_S2}
@@
 
-No zonal cloud bands: prior.
+\todo{No zonal cloud bands: prior.}
 

### 2019-03-25 tex/ms.tex
more text

@@
 
+\todo{75 light curves in S1, 20 in S2}
+\todo{912,605 data points in total}
+
 \todo{(outlier rejection method, trim down to x number of high-SNR lightcurves 
 for computational tractability)}
+
+We subtract the estimated background from each signal.
 
@@
 \subsection{Orbital Modeling}
+\label{sec:orbit}
 
@@
 We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
-increase the flexibility of the systematics model, we append to $\mathrm{B}$ 5 orthogonal
+increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
 polynomials in time for each of the two orbits of \tess in each sector.
@@
 $75 \times (75 + 2 \times 5) + 20 \times (20 + 2 \times 5) = 6,975$ free parameters.
-Since the total number of data points is $912,605$, overfitting is not particularly
-concerning, but we nevertheless impose an L2 prior on the weights with
-standard deviation $\sigma_B = 0.1$.
+The total number of data points is $912,605$, so overfitting is not particularly
+concerning; nevertheless, we impose an L2 prior on the weights with
+standard deviation $\sigma_B = 0.1$ (see \S\ref{sec:model}).
 
@@
 $\mathbf{s}^\top\mathcal{A}\mathbf{R}'\mathbf{R}$ in][]{Luger2019}
-and $\mathbf{y}$ is the vector of spherical harmonic coefficients. As we will
-see below, the linearity of the problem makes it easily invertible.
+and $\mathbf{y}$ is the vector of spherical harmonic coefficients. 
+Note that in \cite{Luger2019}, $\mathbf{y}$ describes the emissivity of the surface,
+but here we will use it to represent the \emph{albedo} of the planet.
+As we will see below, the linearity of the problem makes it easily invertible.
 
@@
 \subsection{Full Model and Likelihood Function}
+\label{sec:model}
 
-Our full model for the flux in the $n^\mathrm{th}$ postage stamp is
+Our full model for each light curve is simply the product of the 
+systematics model $\mathbf{b}_n$ (different for each target) and
+the \starry model $\mathbf{a}$ (shared by all targets). Since we happen
+to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
+(\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
+as a multiplicative term. The model for the flux timeseries
+in the $n^\mathrm{th}$ postage stamp is therefore
 %
 \begin{align}
+    \label{eq:model}
     \mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
@@
 
-\todo{(priors, regularization, equation for the likelihood)}
+We solve Equation~(\ref{eq:model}) for the weights $\mathbf{w}_n$ and $\mathbf{y}$
+by maximizing the negative log likelihood function in two separate steps. In the
+first step, we take advantage of the linearity of the problem to perform a fast,
+semi-analytical optimization to obtain a starting guess for the weights. In the
+second step, we apply additional constraints to prevent overfitting and ensure
+an albedo in the range $[0, 1]$ everywhere on the surface.
+
+In the first step, we initialize the \starry model to unity and iteratively
+solve for $\mathbf{w}_n$ and $\mathbf{y}$ by solving the L2-regularized
+least squares problem \citep[see, e.g., \S2.1 in][]{Luger2018a}.
+We assume zero-mean Gaussian priors for the weights:
+%
+\begin{equation}
+    \begin{aligned}
+        \mathbf{w}_n \sim \mathcal{N}(0, \sigma_w^2)
+    \end{aligned}
+    \qquad\qquad\qquad\qquad
+    \begin{aligned}
+        \mathbf{y} \sim \mathcal{N}(0, \sigma_y(l)^2)
+    \end{aligned}\, ,
+\end{equation}
+%
+with $\sigma_w = 0.1$ and 
+%
+\begin{align}
+    \sigma_y(l) &=
+    \begin{dcases}
+        1.75\times 10^{-5} \, l^\frac{3}{2} & 
+            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+            l < 2
+        \\
+        1.40\times 10^{-4} \, l^{-\frac{3}{2}} & 
+            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
+            l \geq 2
+    \end{dcases}
+    \, ,
+\end{align}
+%
+where $l$ is the spherical harmonic degree. The latter prior was chosen
+by trial-and-error and was adjusted to keep the albedo positive
+everywhere on the surface. Note, importantly, that we do
+not fit for the coefficient of the constant $Y_{0,0}$ spherical harmonic,
+but instead fix it to unity. Since the solutions obtained in this step are merely
+used as a starting point for the second step (see below), the choice of prior 
+at this stage has minimal impact on our results.
+
+In general, we find that the iterative scheme converges within about 50 
+iterations. However, since it is strongly regularized, the model significantly
+underfits the data. In the next step, we remove our L2 prior on the spherical
+harmonic coefficients and instead regularize the actual surface albedo, which
+we compute on a uniform spherical grid with 50,000 points. We enforce a 
+uniform prior in the range $[0, 1]$, with an exponential drop on either 
+side. This constraint breaks the linearity of the problem, so we must
+now use a non-linear optimizer.
 
@@
              \emph{Bottom:} Actual corrected surface reflectance in the red band of the
-             \emph{VIIRS} imager, averaged over the same date range and weighted
+             \emph{VIIRS} imager, averaged over the same date range, band limited
+             to $l_\mathrm{max} = 15$, and weighted
              by the same visibility function. This bandpass covers only about one

### 2019-03-25 tex/ms.tex
tensorflow description

@@
 polynomials in time for each of the two orbits of \tess in each sector.
-The systematics model $\mathbf{b}$ for the $n^\mathrm{th}$ signal is thus
+The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
 %
 \begin{align}
-\mathbf{b}_n = \mathbf{B} \mathbf{w}_n
+\mathbf{p}_n = \mathbf{B} \mathbf{w}_n
 \end{align}
@@
 As with the systematics model (\S\ref{sec:systematics}), the model
-for the astrophysical signal is \emph{linear}: the total signal $\mathbf{a}$ 
+for the astrophysical signal is \emph{linear}: the signal $\mathbf{s}$ 
 is a linear operation on the vector of spherical harmonic coefficients 
@@
 \begin{align}
-    \mathbf{a} = \mathbf{A} \mathbf{y}
+    \mathbf{s} = \mathbf{A} \mathbf{y}
 \end{align}
 %
-where $\mathbf{A}$ is the design matrix \citep[equal to the quantity 
-$\mathbf{s}^\top\mathcal{A}\mathbf{R}'\mathbf{R}$ in][]{Luger2019}
-and $\mathbf{y}$ is the vector of spherical harmonic coefficients. 
+where $\mathbf{A}$ is the design matrix and $\mathbf{y}$ is the vector of spherical harmonic coefficients. 
 Note that in \cite{Luger2019}, $\mathbf{y}$ describes the emissivity of the surface,
 but here we will use it to represent the \emph{albedo} of the planet.
-As we will see below, the linearity of the problem makes it easily invertible.
+We choose a maximum spherical harmonics degree $l_{max} = 15$ for our fits,
+noting that increasing $l_{max}$ above this value does not significantly
+improve the quality of our fits. At the equator, $l = 15$ corresponds to
+a resolution on the order of $180^\circ/15 = 12^\circ$.
 
@@
 Our full model for each light curve is simply the product of the 
-systematics model $\mathbf{b}_n$ (different for each target) and
-the \starry model $\mathbf{a}$ (shared by all targets). Since we happen
+systematics model $\mathbf{p}_n$ (different for each target) and
+the \starry model $\mathbf{s}$ (shared by all targets). Since we happen
 to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
@@
 iterations. However, since it is strongly regularized, the model significantly
-underfits the data. In the next step, we remove our L2 prior on the spherical
+underfits the data. In the second step, we remove our L2 prior on the spherical
 harmonic coefficients and instead regularize the actual surface albedo, which
@@
 uniform prior in the range $[0, 1]$, with an exponential drop on either 
-side. This constraint breaks the linearity of the problem, so we must
-now use a non-linear optimizer.
+side. We additionally impose a constraint on the power spectrum of the
+inferred map, \todo{bla bla}.
+
+Our full negative log likelihood function in this step is therefore
+%
+\begin{align}
+    -\log\mathcal{L} \, = \, 
+        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \Sigma^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
+        &\frac{1}{2}\mathbf{w}^\top \Lambda_w^{-1} \mathbf{w} \, + \nonumber \\
+        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \Lambda_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
+        &\frac{1}{2}(\rho - l^{-\gamma})^\top \Lambda_\rho^{-1} (\rho - l^{-\gamma}) \, + \nonumber \\
+        &\frac{1}{2} \frac{\gamma^2}{\sigma_\gamma^2}
+        \quad,
+\end{align}
+%
+where \todo{explain all this stuff.}
+
+All of these constraint break the linearity of the problem, so we must
+now use a non-linear optimizer. We use the 
+\textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
+to maximize the negative log likelihood.
 
@@
 \facility{TESS}
-\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow, \spiceypy \citep{Annex2019}}
+\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
+TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}
 % Bibliography

### 2019-03-26 tex/ms.tex
animation
gory details of the optim

@@
 \begin{equation}
+    \label{eq:wprior}
     \begin{aligned}
@@
 we compute on a uniform spherical grid with 50,000 points. We enforce a 
-uniform prior in the range $[0, 1]$, with an exponential drop on either 
+uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
 side. We additionally impose a constraint on the power spectrum of the
-inferred map, \todo{bla bla}.
-
+inferred map, requiring that it be drawn from a distribution whose mean
+is a decaying power law in the spherical harmonic degree $l$ in order
+to suppress ringing and spurious high order features.
 Our full negative log likelihood function in this step is therefore
@@
 \begin{align}
+    \label{eq:nll}
     -\log\mathcal{L} \, = \, 
-        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \Sigma^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
-        &\frac{1}{2}\mathbf{w}^\top \Lambda_w^{-1} \mathbf{w} \, + \nonumber \\
-        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \Lambda_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
-        &\frac{1}{2}(\rho - l^{-\gamma})^\top \Lambda_\rho^{-1} (\rho - l^{-\gamma}) \, + \nonumber \\
-        &\frac{1}{2} \frac{\gamma^2}{\sigma_\gamma^2}
+        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \boldsymbol{\Sigma}^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
+        &\frac{1}{2}\mathbf{w}^\top \boldsymbol{\Lambda}_w^{-1} \mathbf{w} \, + \nonumber \\
+        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \boldsymbol{\Lambda}_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
+        &\frac{1}{2}(\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma})^\top \boldsymbol{\Lambda}_\rho^{-1} (\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma}) \, + \nonumber \\
+        &\frac{1}{2} \frac{(\gamma - \gamma_0)^2}{\sigma_\gamma^2}
         \quad,
@@
 %
-where \todo{explain all this stuff.}
+where $\mathbf{f}$ is the measured flux across all targets,
+$\mathbf{m}$ is the full model (Equation~\ref{eq:model}),
+$\boldsymbol{\Sigma}$ is the (diagonal) data covariance, 
+$\mathbf{w}$ are the systematics model weights for all targets,
+$\boldsymbol{\Lambda}_w$ is the prior covariance of the weights
+(Equation~\ref{eq:wprior}), $\mathbf{a_-}$ and $\mathbf{a_+}$ are
+vectors containing the values of the albedo that are below zero and above one, 
+respectively, $\boldsymbol{\Lambda}_a$ is the covariance of the Gaussian
+used to smooth the edges of the top-hat prior on $\mathbf{a}$,
+$\boldsymbol{\rho}$ is the power spectrum of the inferred spherical harmonic map
+(equal to the sum of the squares of the coefficients at each degree $\boldsymbol{l}$),
+$\gamma$ is the power law index of the power spectrum prior, $\boldsymbol{\Lambda}_\rho$ is the
+covariance of that prior, $\gamma_0 = 1.5$ is the mean of the prior on $\gamma$
+and $\sigma_\gamma^2 = 10^{-2}$ is the corresponding variance.
+%
+For simplicity, all our prior covariances are diagonal and
+homoscedastic with variances equal to $10^{-2}$ for $\mathbf{w}$, and
+$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\mathbf{\rho}$.
 
-All of these constraint break the linearity of the problem, so we must
-now use a non-linear optimizer. We use the 
+Unfortunately, all of the constraints outlined above break the linearity 
+of the problem, and we must turn to a non-linear optimizer. We use the 
 \textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
-to maximize the negative log likelihood.
+to maximize Equation~(\ref{eq:nll}).
 
@@
              are to be expected.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
+    \caption{\label{fig:map_temporal}
+             Compare to Figure~\ref{fig:model}. An animated version
+             of this figure is available 
+             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{here}.
              \codelink{earthshine_S1_S2}

### 2019-03-26 tex/ms.tex
getting there

@@
 In general, we find that the iterative scheme converges within about 50 
-iterations. However, since it is strongly regularized, the model significantly
+iterations, taking about three minutes on a laptop computer. However, since it 
+is strongly regularized, the model significantly
 underfits the data. In the second step, we remove our L2 prior on the spherical
@@
 \textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
-to maximize Equation~(\ref{eq:nll}).
-
-\todo{(details of TensorFlow optimization)}
+to maximize Equation~(\ref{eq:nll}). Starting with the values of the
+weights obtained in the first step, we run the \textsf{AdamOptimizer}
+for 1000 iterations, well past convergence. Since \tf automatically
+computes and propagates gradient information, this step is similarly fast
+and also finishes in under three minutes on a standard computer.
 
@@
 
-\begin{figure}[t!]
+The top panel of Figure~\ref{fig:model} shows the median of the maximum likelihood model
+across all 95 targets (blue) overplotted on the median flux across
+the same targets (black). The median residuals are shown in the bottom panel; these have
+standard deviation of about one percent. While there is significant correlated
+structure in the residuals, their power spectrum displays a broad peak extending 
+between about 0.1 and 10 days, with a significant dip at exactly 1 day. This
+suggests our model is fitting the rotational variability of Sol d quite well, but
+additional temporal variations---most likely due to cloud movement---cause aperiodic
+changes to the reflectivity of the surface. We revisit this point in \S\ref{sec:discussion}.
+
+\todo{More on this here.}
+
+\begin{figure}[p!]
     \begin{centering}
@@
 
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
-    \caption{\label{fig:map_temporal}
-             Compare to Figure~\ref{fig:model}. An animated version
-             of this figure is available 
-             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{here}.
-             \codelink{earthshine_S1_S2}
-             }
-    \end{centering}
-\end{figure}
-
-Figure~\ref{fig:model} shows the median model.  \todo{More on this here.}
-
 The top panel of Figure~\ref{fig:map} shows the maximum likelihood map of Sol d.
@@
 \label{sec:discussion}
+
+Residuals in Figure~\ref{fig:model} display significant correlated
+structure. Talk about their power spectrum.
+
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
+    \caption{\label{fig:map_temporal}
+             Compare to Figure~\ref{fig:model}. An animated version
+             of this figure is available 
+             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{here}.
+             \codelink{earthshine_S1_S2}
+             }
+    \end{centering}
+\end{figure}
 

### 2019-03-26 tex/ms.tex
incremental progress on writing

@@
 
-\todo{(background extraction from 2-minute cadence targets)}
+The \TESS pipeline produces processed lightcurves for all short-cadence targets. 
+Part of this processing is the determination of the localized background flux within each postage stamp, which is provided as an ancillary time series. 
+\todo{TJD = BJD - 2457000}
+We use these background flux measurements as our primary data source in this work.
 
-\todo{TJD = BJD - 2457000}
+For each of the two sectors considered (Sector 1 and Sector 2), we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across all four \TESS cameras and extracted the background flux time series from each.
+Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see Section \ref{sec:systematics}).
+We down-selected our pool of 1000 targets to 75 maximally useful background lightcurves from Sector 1 and 20 from Sector 2. 
+This down-selection was done with several criteria in mind: each lightcurve should contain a significant signal from Sol d; they should be representative of the general background flux modulation seen across the \TESS cameras, rather than containing any truly localized signals from astrophysical background sources; and the sample as a whole should contain the full range of typical behaviors of background across the entire \TESS field of view.
+To accomplish this, we... \todo{(decide whether it's outlier rejection only or full-on categorization)}
 
-\todo{75 light curves in S1, 20 in S2}
-\todo{912,605 data points in total}
+\todo{(masking out epochs without Sol d shine, subtraction of baseline background flux)}
 
-\todo{(outlier rejection method, trim down to x number of high-SNR lightcurves 
-for computational tractability)}
-
-We subtract the estimated background from each signal.
+The final data set to be used consists of 75 Sector 1 background lightcurves and 20 Sector 2 background lightcurves corresponding to the epochs at which Sol d signal was clearly registered by \TESS. 
+This is 912,605 data points in total.
 
@@
 different for each target. This problem is precisely what the technique of
-pixel-level decorelation \citep[PLD;][]{Deming2015, Luger2016, Luger2018a}
+pixel-level decorrelation \citep[PLD;][]{Deming2015, Luger2016, Luger2018a}
 seeks to address. In PLD, one computes the sum over all light curves at each

### 2019-03-26 tex/ms.tex
updates

--- 2019-03-26 tex/ms.tex
@@
 At any given cadence, we rotate Sol d about its spin axis to the correct phase,
-assuming a rotational period of $1.00$ day. We determine the initial rotation
+assuming a rotational period of $0.9972696$ day. We determine the initial rotation
 phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
@@
 \tess with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
+We verified our rotations by comparing our results on several days to the
+ephemerides provided by the JPL HORIZONS Web interface
+\footnote{See \url{https://ssd.jpl.nasa.gov/horizons.cgi} and 
+\href{https://github.com/rodluger/earthshine/blob/master/notebooks/SanitCheck.ipynb}{this
+Jupyter notebook.}}.
 
@@
 noting that increasing $l_{max}$ above this value does not significantly
-improve the quality of our fits. At the equator, $l = 15$ corresponds to
-a resolution on the order of $180^\circ/15 = 12^\circ$.
+improve the quality of our fits. Note that $l = 15$ corresponds to
+a maximum surface resolution on the order of $180^\circ/15 = 12^\circ$.
 
@@
 
-Unfortunately, all of the constraints outlined above break the linearity 
+Unfortunately, the constraints outlined above break the linearity 
 of the problem, and we must turn to a non-linear optimizer. We use the 
@@
 
+We expect the brightest features to be ice, clouds, and forest canopy. Deserts
+to a lesser extent. Bare soil / rock and oceans are the darkest \citep{Jedlovec2009}.
+
 Residuals in Figure~\ref{fig:model} display significant correlated
-structure. Talk about their power spectrum.
+structure. Talk about their power spectrum. Talk about how S2 is worse fit.
 

### 2019-03-26 earthshine/__init__.py

@@ -1,2 +1,2 @@
-from .model import design_matrix, tess_earth_vector, visibility
+from .model import design_matrix, tess_earth_vector, visibility, smooth
 from .animate import animate, render

### 2019-03-26 earthshine/animate.py

@@ -20,7 +20,7 @@ path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 __all__ = ["animate", "render"]
 
 
-def render(map, time, time0, phase0=0.0, res=75):
+def render(map, time, time0, phase0=0.0, res=75, period=0.9972696):
     """
 
     """
@@ -61,7 +61,7 @@ def render(map, time, time0, phase0=0.0, res=75):
 
     # Rotate the earth to the current phase in the original frame
     map.axis = [0, 1, 0]
-    phase = (360. * (time - time0)) % 360. + phase0
+    phase = (360. * (time - time0) / period) % 360. + phase0
     R = starry.RAxisAngle([0, 1, 0], phase)
     map.rotate(phase)
 
@@ -97,7 +97,7 @@ def render(map, time, time0, phase0=0.0, res=75):
 
 
 # Visualize the orbit
-def animate(map, time, phase0=0.0, res=75, interval=75):
+def animate(map, time, phase0=0.0, res=75, interval=75, period=0.9972696):
     """
 
     """
@@ -204,7 +204,7 @@ def animate(map, time, phase0=0.0, res=75, interval=75):
         # Rotate the earth to the current phase in the original frame
         map[:, :, :] = y
         map.axis = [0, 1, 0]
-        phase = (360. * (time[i] - time[0])) % 360. + phase0
+        phase = (360. * (time[i] - time[0]) / period) % 360. + phase0
         R = starry.RAxisAngle([0, 1, 0], phase)
         map.rotate(phase)
 

### 2019-03-26 earthshine/model.py

@@ -3,6 +3,7 @@ import glob
 from tqdm import tqdm
 import numpy as np
 import os
+import healpy as hp
 import starry
 assert starry.__version__ == "1.0.0.dev0", \
     "This code requires the `starry` version 1.0.0.dev0."
@@ -12,7 +13,54 @@ REARTH = 1.0 / 6371.0
 TJD0 = 2457000
 path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 
-__all__ = ["design_matrix", "tess_vector", "visibility"]
+__all__ = ["design_matrix", "tess_vector", "visibility", "smooth"]
+
+
+def alm_to_ylm(alm, lmax):
+    # Convert the alms to real coefficients
+    ylm = np.zeros(lmax ** 2 + 2 * lmax + 1, dtype='float')
+    i = 0
+    for l in range(0, lmax + 1):
+        for m in range(-l, l + 1):
+            j = hp.sphtfunc.Alm.getidx(lmax, l, np.abs(m))
+            if m < 0:
+                ylm[i] = np.sqrt(2) * (-1) ** m * alm[j].imag
+            elif m == 0:
+                ylm[i] = alm[j].real
+            else:
+                ylm[i] = np.sqrt(2) * (-1) ** m * alm[j].real
+            i += 1
+    return ylm
+
+
+def ylm_to_alm(ylm, lmax):
+    # Convert the ylms to complex coefficients
+    alm = np.zeros(lmax ** 2 + 2 * lmax + 1, dtype='complex128') * np.nan
+    i = 0
+    for l in range(0, lmax + 1):
+        for m in range(-l, l + 1):
+            j = hp.sphtfunc.Alm.getidx(lmax, l, np.abs(m))
+            if np.isnan(alm[j]):
+                alm[j] = 0.0
+            if m < 0:
+                alm[j] += 1j * (ylm[i] / (np.sqrt(2) * (-1) ** m))
+            elif m == 0:
+                alm[j] += ylm[i]
+            else:
+                alm[j] += ylm[i] / (np.sqrt(2) * (-1) ** m)
+            i += 1
+    alm = alm[:np.argmax(np.isnan(alm))]
+    return alm
+
+
+def smooth(map, sigma):
+    """Smooth a map in place with a Gaussian kernel."""
+    lmax = map.ydeg
+    alm = ylm_to_alm(map.y, lmax)
+    hp.sphtfunc.smoothalm(alm, sigma=sigma, inplace=True)
[…]

### 2019-03-26 setup.py

@@ -18,7 +18,8 @@ setup(name='earthshine',
           'numpy>=1.8',
           'scipy',
           'matplotlib',
-          'starry==1.0.0.dev0'
+          'starry==1.0.0.dev0',
+          'healpy'
       ],
       dependency_links=[
         'https://github.com/rodluger/starry/tarball/linear#egg=starry-1.0.0.dev0'

### 2019-03-27 tex/ms.tex
better

@@
 to convert the TJD timestamps to 
-ephemeris time (ET). We then used the \textsf{spkezr} utility to compute
+ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
 the relative positions of Sol, Sol d, and \tess for every cadence
@@
 of \starry
-\footnote{\url{https://github.com/rodluger/starry/tree/linear}}
-and will be discussed in detail in upcoming work.
+\footnote{\url{https://github.com/rodluger/starry/tree/linear}};
+the details will be discussed in more detail in upcoming work.
 
@@
 is a linear operation on the vector of spherical harmonic coefficients 
+$\mathbf{y}$
 that describes the body's surface:
@@
 but here we will use it to represent the \emph{albedo} of the planet.
-We choose a maximum spherical harmonics degree $l_{max} = 15$ for our fits,
+We choose a maximum spherical harmonic degree $l_{max} = 25$ for our fits,
 noting that increasing $l_{max}$ above this value does not significantly
-improve the quality of our fits. Note that $l = 15$ corresponds to
-a maximum surface resolution on the order of $180^\circ/15 = 12^\circ$.
+improve the quality of our fits. Note that $l = 25$ corresponds to
+a maximum surface resolution on the order of $180^\circ/25 \approx 7^\circ$.
 
@@
 Our full model for each light curve is simply the product of the 
-systematics model $\mathbf{p}_n$ (different for each target) and
-the \starry model $\mathbf{s}$ (shared by all targets). Since we happen
+systematics model $\mathbf{p}_n = \mathbf{B}\mathbf{w}_n$ (different for each target) and
+the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we happen
 to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
@@
 In general, we find that the iterative scheme converges within about 50 
-iterations, taking about three minutes on a laptop computer. However, since it 
+iterations, taking about fifteen minutes on a laptop computer. However, since it 
 is strongly regularized, the model significantly
@@
 homoscedastic with variances equal to $10^{-2}$ for $\mathbf{w}$, and
-$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\mathbf{\rho}$.
+$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.
 
@@
 for 1000 iterations, well past convergence. Since \tf automatically
-computes and propagates gradient information, this step is similarly fast
-and also finishes in under three minutes on a standard computer.
+computes and propagates gradient information, this step is fast
+and also finishes in under five minutes on a standard computer.
 
@@
              of Sol d.
-             \emph{Bottom:} Actual corrected surface reflectance in the red band of the
-             \emph{VIIRS} imager, averaged over the same date range, band limited
-             to $l_\mathrm{max} = 15$, and weighted
-             by the same visibility function. This bandpass covers only about one
-             quarter of the \tess bandpass, so deviations between the two images
-             are to be expected.
+             \emph{Bottom:} Approximate cloud coverage map based on corrected
+             surface reflectance obtained by the
+             \emph{VIIRS} imager, averaged over the same date range and weighted
+             by the same visibility function.
              \codelink{earthshine_S1_S2}
@@
 
-The bottom panel of Figure~\ref{fig:map} shows the corrected surface
-reflectance obtained from the
+The bottom panel of Figure~\ref{fig:map} shows an approximate average
+cloud cover map of Sol d based on imagery taken by the
 Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
@@
 \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/viirs.sh}{this wget script}.}. 
-The image shows the corrected surface reflectance in the I1 band of the instrument,
+The image was produced by \todo{explain...}
 averaged over the 28 days of data analyzed in this work, smoothed with a Gaussian
 filter, and weighted by the \tess visibility as in the top panel.
-The I1 band extends from 0.6 to 0.68 $\mu\mathrm{m}$
-\footnote{\url{http://rammb.cira.colostate.edu/projects/npp/VIIRS_bands_and_bandwidths.pdf}},
-and therefore covers only about one-fourth of the bandpass of \tess
-(nominally 0.6 - 1.0 $\mu\mathrm{m}$).
 
@@
 to a lesser extent. Bare soil / rock and oceans are the darkest \citep{Jedlovec2009}.
+
+\subsection{Temporal Evolution}
 
@@
 \end{figure}
+
+\subsection{Sources of Bias}
+
+In our analysis, we neglected the effects of limb darkening. Because of
+atmospheric attenuation, features near the limb of the planet should in
+reality contribute less to the flux than our model predicts. This could
+bias our results particularly in cases where the planet is seen at half
+phase (for instance, during days 1326 and 1341 in Figure~\ref{fig:phases}).
+In the absence of limb darkening, the brightest regions on the planet are those
+close to the sub-stellar point, which is on the limb. Limb darkening should
+shift the regions of peak brightness closer to the center of the planet, adding
+an east-west bias in the location of the features we identify.
+
+We also ignored the finite angular size of Sol at Sol d (about $0.5^\circ$),
+treating it instead as a point source. Regions immediately nightward of the 
+terminator should therefore contribute a small amount of flux, which we neglect.
+The effect, however, is below the resolution of our inferred map, so we expect
+it does not introduce significant bias.
+
+Finally, we implicitly assumed an isotropic prior on the spherical harmonic
+coefficients by imposing a power spectrum in only the degree $l$. This has the
+effect of lessening the extent to which features can be confined to certain
+latitudes. In particular, our prior implicitly disfavors banded cloud structure,
+which one may \emph{a priori} expect on a rapidly rotating planet such as 
+Sol d. The bottom panel of Figure~\ref{fig:map} shows such banded structure
+at the equator and at mid-latitudes due to the combined effects of 
+north-south circulation and deflection by the Coriolis force.
 

### 2019-03-27 earthshine/animate.py

@@ -20,7 +20,7 @@ path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 __all__ = ["animate", "render"]
 
 
-def render(map, time, time0, phase0=0.0, res=75, period=0.9972696):
+def render(map, time, phase0=-56.5, time0=1325.5, res=75, period=0.9972696):
     """
 
     """
@@ -97,7 +97,7 @@ def render(map, time, time0, phase0=0.0, res=75, period=0.9972696):
 
 
 # Visualize the orbit
-def animate(map, time, phase0=0.0, res=75, interval=75, period=0.9972696):
+def animate(map, time, phase0=-56.5, time0=1325.5, res=75, interval=75, period=0.9972696):
     """
 
     """
@@ -204,7 +204,7 @@ def animate(map, time, phase0=0.0, res=75, interval=75, period=0.9972696):
         # Rotate the earth to the current phase in the original frame
         map[:, :, :] = y
         map.axis = [0, 1, 0]
-        phase = (360. * (time[i] - time[0]) / period) % 360. + phase0
+        phase = (360. * (time[i] - time0) / period) % 360. + phase0
         R = starry.RAxisAngle([0, 1, 0], phase)
         map.rotate(phase)
 

### 2019-03-27 earthshine/model.py

@@ -57,7 +57,7 @@ def smooth(map, sigma):
     """Smooth a map in place with a Gaussian kernel."""
     lmax = map.ydeg
     alm = ylm_to_alm(map.y, lmax)
-    hp.sphtfunc.smoothalm(alm, sigma=sigma, inplace=True)
+    hp.sphtfunc.smoothalm(alm, sigma=sigma, inplace=True, verbose=False)
     ylm = alm_to_ylm(alm, lmax)
     map[:, :] = ylm
     return
@@ -95,8 +95,8 @@ def tess_earth_vector(time):
     return tess
 
 
-def design_matrix(time, ydeg=10, nt=2, period=0.9972696, phase0=0.0, 
-                  fit_linear_term=False):
+def design_matrix(time, ydeg=10, nt=2, period=0.9972696, phase0=-56.5, 
+                  time0=1325.5, fit_linear_term=False):
     """
     Compute and return the design matrix.
 
@@ -104,7 +104,8 @@ def design_matrix(time, ydeg=10, nt=2, period=0.9972696, phase0=0.0,
         time: The time array in TJD.
         ydeg: The maximum spherical harmonic degree.
         nt: The number of map temporal components.
-        phase0: The phase of the map at `t = 0` in degrees.
+        phase0: The phase of the map at `t = time0` in degrees.
+        time0: The time at which the phase is defined in days.
     """
     # Instantiate a `starry` map
     map = starry.Map(ydeg=ydeg, udeg=0, reflected=True, nt=nt)
@@ -163,7 +164,7 @@ def design_matrix(time, ydeg=10, nt=2, period=0.9972696, phase0=0.0,
         # rotates the earth into phase and then rotates
         # the earth into view for tess
         tx, ty, tz = tess_hat[:, i]
-        phase = (2 * np.pi * (time[i] - time[0]) / period) % (2 * np.pi) + phase0 * np.pi / 180
+        phase = (2 * np.pi * (time[i] - time0) / period) % (2 * np.pi) + phase0 * np.pi / 180
         ty2 = ty ** 2
         tx2 = tx ** 2
         cosp = np.cos(phase)
@@ -190,7 +191,7 @@ def design_matrix(time, ydeg=10, nt=2, period=0.9972696, phase0=0.0,
         return X, X00
 
 
-def visibility(time, phase0=0.0, res=100, period=0.9972696):
+def visibility(time, phase0=-56.5, time0=1325.5, res=100, period=0.9972696):
     """
 
[…]

### 2019-03-27 tex/ms.tex
minor data changes

@@
 Part of this processing is the determination of the localized background flux within each postage stamp, which is provided as an ancillary time series. 
-\todo{TJD = BJD - 2457000}
-We use these background flux measurements as our primary data source in this work.
+As with all \TESS time series data products, the time is given in \TESS Julian Days (TJD), defined as BJD - 2457000, and the data are delivered in 27-day parcels corresponding to the varying pointing sectors of \TESS.
+We use these background flux measurements from Sectors 1 and 2 as our primary data source in this work.
 
-For each of the two sectors considered (Sector 1 and Sector 2), we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across all four \TESS cameras and extracted the background flux time series from each.
+For each of the two sectors considered, we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across the full \TESS field of view and extracted the background flux time series from each.
 Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see Section \ref{sec:systematics}).
@@
 This is 912,605 data points in total. 
-
-Figure showing lightcurves for various targets: Figure~\ref{fig:data}.
+A representative sample of these signals is shown in Figure~\ref{fig:data}.
 

### 2019-03-27 tex/ms.tex
more updates

--- 2019-03-27 tex/ms.tex
@@
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
     \begin{centering}
@@
 At any given cadence, we rotate Sol d about its spin axis to the correct phase,
-assuming a rotational period of $0.9972696$ day. We determine the initial rotation
+assuming a rotation period of $0.9972696$ day, the sidereal rotation period
+of the planet. We determine the initial rotation
 phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
@@
 We verified our rotations by comparing our results on several days to the
-ephemerides provided by the JPL HORIZONS Web interface
+ephemerides provided by the JPL HORIZONS Web interface%
 \footnote{See \url{https://ssd.jpl.nasa.gov/horizons.cgi} and 
@@
 
-\subsection{Reflected-Light Mapping with \starry}
+\subsection{Reflected Light Mapping with \starry}
 \label{sec:starry}
@@
 but here we will use it to represent the \emph{albedo} of the planet.
-We choose a maximum spherical harmonic degree $l_{max} = 25$ for our fits,
-noting that increasing $l_{max}$ above this value does not significantly
-improve the quality of our fits. Note that $l = 25$ corresponds to
-a maximum surface resolution on the order of $180^\circ/25 \approx 7^\circ$.
+We choose a maximum spherical harmonic degree $l_{max} = 10$ for our fits,
+noting that increasing $l_{max}$ above this value 
+leads to a quick rise in the amount of ``ringing'' without substantially
+increasing the quality of our fits. Note that $l = 10$ corresponds to
+a maximum surface resolution on the order of $180^\circ/10 \approx 18^\circ$.
 
@@
     \begin{centering}
+    \includegraphics[width=\linewidth]{figures/map_L2.pdf}
+    \caption{\label{fig:map_L2}
+             Maximum likelihood map of Sol d obtained during the first
+             stage of our optimization procedure, in which an iterative
+             analytic approach was used to solve the bilinear model, 
+             subject to very conservative regularization. Despite the low
+             resolution of this map, the bright features appear to track
+             land masses which for specificity we will refer to as (from left to right)
+             ``South America,'' ``Africa,'' and ``Asia.''
+             The two dark features are associated with the planet's
+             two purported oceans, which we call the ``Pacific'' and the ``Atlantic.''
+             }
+    \end{centering}
+\end{figure}
+
+Figure~\ref{fig:map_L2} shows the maximum likelihood map inferred
+during the first stage of our optimization procedure. Since the map
+coefficients were heavily regularized, the dynamic range of the albedo
+variations was less than 10\%; we scaled it to span the range [0, 1]
+for better visualization. Furthermore, although the resolution is on 
+the order of $12^\circ$, features typically span ${\sim}45^\circ$; this is
+also an artefact of our regularization. However, broad features are already
+visible in the map: three bright regions and two dark regions (one of which
+wraps around the antimeridian). Overplotted on the inferred map are
+coastal outlines corresponding to our current best understanding of 
+the geography of Sol d. One can see that the three bright regions roughly
+track, from left to right, continents we shall refer to as ``South America,''
+``Africa,'' and ``Asia,'' in keeping with the literature. The dark regions
+are associated with the two major purported oceans on the planet, the
+``Pacific'' (centered at longitude $\pm180^\circ$) and ``Atlantic''
+(centered at longitude $\-45^\circ$).
+
+\begin{figure}[t!]
+    \begin{centering}
     \includegraphics[width=\linewidth]{figures/model.pdf}
@@
 
+As expected, we obtain a much better fit
 The top panel of Figure~\ref{fig:model} shows the median of the maximum likelihood model
@@
 the same targets (black). The median residuals are shown in the bottom panel; these have
-standard deviation of about one percent. While there is significant correlated
+standard deviation of less than one percent. While there is significant correlated
 structure in the residuals, their power spectrum displays a broad peak extending 
-between about 0.1 and 10 days, with a significant dip at exactly 1 day. This
+between about 0.1 and 10 days, with a significant dip at 1.00 day. This
 suggests our model is fitting the rotational variability of Sol d quite well, but
@@
 
-The top panel of Figure~\ref{fig:map} shows the maximum likelihood map of Sol d.
+The top panel of Figure~\ref{fig:map} shows the maximum likelihood albedo map of Sol d,
+weighted by a visibility function, which we computed as the average of the product of the 
+cosine of the illumination angle and the cosine of the angle between the 
+observer vector and the vector normal to the surface of Sol d. This normalization
+has the effect of downweighting regions that are either seldom illuminated (such
+as regions near the southern pole of Sol d, as the observations were taken during
+southern winter) or seldom in view (such as regions near the north pole of the planet,
+which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \tess).
+Because there is little data in these regions, their albedo is prior-dominated
+and tends to fluctuate substantially with small changes to the choices we make
+when fitting the data. Conversely, we find that the large scale features close to
+the equator of Sol d are mostly insensitive to our choices of prior. In the Figure,
+we use dashed lines to delineate the regions whose average visibility is larger
+than 0.5.
+
 \todo{More on this here.}
@@
 Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
-Suomi National Polar-orbiting Partnership (\emph{S-NPP}) satellite
+Suomi National Polar-orbiting Partnership (\emph{S-NPP}) satellite%
 \footnote{Data obtained via 
 \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/viirs.sh}{this wget script}.}. 
-The image was produced by \todo{explain...}
-averaged over the 28 days of data analyzed in this work, smoothed with a Gaussian
-filter, and weighted by the \tess visibility as in the top panel.
+The image was produced by analyzing the corrected true color reflectance in the
+I1 (red), M4 (blue), and M3 (green) bands and masking
+all pixels that were either dark or had significant variance among the three
+bands (i.e., inconsistent with a grey spectrum). We then averaged the images
+averaged over the 28 days of data analyzed in this work, smoothed it, 
+and weighted by the \tess visibility as in the top panel.
 
@@
     \caption{\label{fig:map_temporal}
-             Compare to Figure~\ref{fig:model}. An animated version
-             of this figure is available 
-             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{here}.
+             Something.
              \codelink{earthshine_S1_S2}

### 2019-03-27 tex/ms.tex
more text

@@
 For simplicity, all our prior covariances are diagonal and
-homoscedastic with variances equal to $10^{-2}$ for $\mathbf{w}$, and
+homoscedastic with variances equal to $2.5\times 10^{-3}$ for $\mathbf{w}$, and
 $10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.
@@
 
-As expected, we obtain a much better fit
-The top panel of Figure~\ref{fig:model} shows the median of the maximum likelihood model
-across all 95 targets (blue) overplotted on the median flux across
-the same targets (black). The median residuals are shown in the bottom panel; these have
+As expected, the second, non-linear step in our optimization procedure
+yields a much better fit to the data.
+The top panel of Figure~\ref{fig:model} shows the median of the 
+maximum likelihood model in this second step
+across all 95 targets (blue) overplotted on the median flux (black). 
+The median residuals are shown in the bottom panel; these have
 standard deviation of less than one percent. While there is significant correlated
@@
     \caption{\label{fig:map_temporal}
-             Something.
+             The inferred mean map when allowing for slight temporal
+             variations in the spherical harmonic coefficients. Compare
+             to Figure~\ref{fig:map}. An animated version of this figure
+             is available on 
+             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{GitHub}.
              \codelink{earthshine_S1_S2}
@@
 
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=\linewidth]{figures/map_labels.pdf}
-    \caption{\label{fig:map_labels}
-             Map of Sol d with the major features indicated with suggested
-             names.
-             \codelink{earthshine_S1_S2}
-             }
-    \end{centering}
-\end{figure}
+% \begin{figure}[t!]
+%     \begin{centering}
+%     \includegraphics[width=\linewidth]{figures/map_labels.pdf}
+%     \caption{\label{fig:map_labels}
+%             Map of Sol d with the major features indicated with suggested
+%             names.
+%             \codelink{earthshine_S1_S2}
+%             }
+%     \end{centering}
+% \end{figure}
 

### 2019-03-27 tex/ms.tex
more texting

@@
 
-\todo{More on this here.}
-
 \begin{figure}[p!]
@@
 
-The top panel of Figure~\ref{fig:map} shows the maximum likelihood albedo map of Sol d,
-weighted by a visibility function, which we computed as the average of the product of the 
+In the top panel of Figure~\ref{fig:map} we show the final,
+maximum likelihood albedo map inferred for Sol d weighted by a visibility function.
+The visibiluty function is computed as the average of the product of the 
 cosine of the illumination angle and the cosine of the angle between the 
@@
 which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \tess).
-Because there is little data in these regions, their albedo is prior-dominated
+Because there is little data from these regions, their albedo is prior-dominated
 and tends to fluctuate substantially with small changes to the choices we make
@@
 than 0.5.
-
-\todo{More on this here.}
 
@@
 
+While the two panels display fundamentally different quantities---an albedo
+and a cloudiness factor---we expect that the signal of Sol d in the \tess
+bandpass is dominated by cloud reflectivity, as water clouds have an albedo
+higher than soil, vegetation, or ocean in the optical/near infrared. We therefore
+expect large, coherent cloud structures to show up as the brightest regions 
+in our inferred map, and in fact we find that this is generally the case. The
+dominant feature in our inferred map is a bright region spanning longitudes
+of $+50^\circ$ to $+100^\circ$ just northward of the equator. This is also the
+dominant feature in the VIIRS map, corresponding to the persistent weather system
+associated with summertime monsoons in the south of Asia.
+
+Secondary features common to both maps are a permanent cloudy region over
+central Africa with a westward spur over the Atlantic Ocean, a veneer of clouds
+over the north Pacific, and a pile up of clouds on the western coast of
+northern South America. The dark regions in the inferred map rather loosely
+track the Pacific, Atlantic, and Indian Oceans, although the correspondence
+is not exact.
+
 \section{Discussion}
@@
 
-\begin{figure}[t!]
+\begin{figure}[p!]
     \begin{centering}

### 2019-03-27 tex/ms.tex
bla bla bla

@@
 bandpass is dominated by cloud reflectivity, as water clouds have an albedo
-higher than soil, vegetation, or ocean in the optical/near infrared. We therefore
+higher than soil, vegetation, or ocean in the optical/near infrared
+\citep[e.g.,][]{Jedlovec2009}. We therefore
 expect large, coherent cloud structures to show up as the brightest regions 
@@
 
-We expect the brightest features to be ice, clouds, and forest canopy. Deserts
-to a lesser extent. Bare soil / rock and oceans are the darkest \citep{Jedlovec2009}.
+The problem of inferring a two-dimensional map from a one-dimensional
+timeseries is famously ill-posed given its large null space and many complex
+degeneracies \citep[e.g.,][]{CowanFuentesHaggard2013}. In fact, for a 
+uniformly illuminated body, its rotational light curve encodes at most
+$2l_\mathrm{max}$ modes (one sine term and one cosine term per frequency), 
+where $l_\mathrm{max}$ is the highest spherical
+harmonic degree of features on the surface of the body. The number of modes
+\emph{on the surface of the body}, however, increases quadratically 
+as $(l_\mathrm{max} + 1)^2$. This means that for a body whose surface is
+perfectly described by a spherical harmonic map of degree $l_\mathrm{max} = 10$,
+which is described by 121 coefficients, only 20 linear combinations
+of those coefficients are actually projected onto the light curve. The
+problem is fundamentally non-invertible, since most of the information
+one wishes to extract lies in the null space.
+
+Fortunately, there are two aspects of the problem at hand that facilitate
+this (seemingly impossible) inversion. First, the surface of Sol d is
+not uniformly illuminated; instead, different parts of the surface are weighted
+by different amounts as the planet rotates and as the angle of incident starlight
+moves over the course of the year. This weighting is sufficient to break many
+of the degeneracies, which are rooted in the anti-symmetry of many of the spherical
+harmonic modes. Moreover, the discontinuous day/night terminator further
+breaks these degeneracies, as only modes that are anti-symmetric about
+the visible lune of the planet strictly remain in the null space. Second, 
+the changing vantage point of \tess relative to Sol d (and our exact knowledge of it)
+break degeneracies that are viewpoint-dependent. In particular, the motion of
+\tess changes the position and shape of the terminator on the projected disk
+of Sol d, enhancing the effect discussed above.
+
+In fact, because of these points, there should formally be \emph{no} null space 
+in this particular problem. In practice, however, it is evident from
+Figure~\ref{fig:map} that degenaricies still abound. \todo{bla bla bla.}
 

### 2019-03-27 tex/ms.tex
bla bla...

@@
 In general, we find that the iterative scheme converges within about 50 
-iterations, taking about fifteen minutes on a laptop computer. However, since it 
+iterations, taking about three minutes on a laptop computer. However, since it 
 is strongly regularized, the model significantly
@@
 computes and propagates gradient information, this step is fast
-and also finishes in under five minutes on a standard computer.
+and also finishes in under three minutes on a laptop.
 
@@
 for better visualization. Furthermore, although the resolution is on 
-the order of $12^\circ$, features typically span ${\sim}45^\circ$; this is
+the order of $18^\circ$, features typically span ${\sim}45^\circ$; this is
 also an artefact of our regularization. However, broad features are already
@@
 
+\subsection{An Ill-Posed Problem}
+\label{sec:illposed}
+
 The problem of inferring a two-dimensional map from a one-dimensional
@@
 in this particular problem. In practice, however, it is evident from
-Figure~\ref{fig:map} that degenaricies still abound. \todo{bla bla bla.}
+Figure~\ref{fig:map} that degenaricies still abound. This is likely because
+of the finite signal-to-noise of our measurements and various biases in
+our adopted model. While the measurement errors on our data points are
+quite small---since the signal of Sol d is both quite strong and independently
+measured at 95 different positions on the detector---our lack of understanding
+of the complex optics that give rise to the signal in the first place, and our
+attempt to na{\"i}vely model it with pixel-level decorrelation, likely
+introduces significant correlated noise into the problem. We discuss
+sources of bias in more detail in \S\ref{sec:bias} below
+
+\subsection{Confirmation Bias}
+\label{sec:confirmation}
+\todo{bla bla bla}
 
 \subsection{Temporal Evolution}
+\label{sec:temporal}
 
@@
 \subsection{Sources of Bias}
+\label{sec:bias}
+
+\todo{PLD, moon background, etc.}
 
@@
 
-\todo{(comparison of inferred features to ``model'' (Earth))}
+\subsection{Application to Other Planets}
+\label{sec:otherplanets}
 
-\todo{No zonal cloud bands: prior.}
+\todo{For realz, how would we do this.}
 

### 2019-03-27 tex/ms.tex
confirmation bias

@@
 in this particular problem. In practice, however, it is evident from
-Figure~\ref{fig:map} that degenaricies still abound. This is likely because
+Figure~\ref{fig:map} that degenaricies still abound. While we infer a few of the
+dominant features of the cloud map of Sol d, several of them are skewed, 
+shifted, or entirely out of place. This is the case, for instance, with
+the cloud bank west of South America, which extends too far westward, and
+the northern Atlantic Ocean, which appears to extends into the east coast of
+North America. We identify three broad reasons for this.
+
+First, many of the issues arise because
 of the finite signal-to-noise of our measurements and various biases in
@@
 attempt to na{\"i}vely model it with pixel-level decorrelation, likely
-introduces significant correlated noise into the problem. We discuss
-sources of bias in more detail in \S\ref{sec:bias} below
+introduces significant correlated noise into the problem. We discuss this
+and other sources of bias in more detail in \S\ref{sec:bias} below.
+
+Second, while we attempted to adopt agnostic priors on the map coefficients---i.e.,
+we fit for a spectral slope rather than impose one---our inferred map is still 
+heavily prior-dependent. Our choice of regularization strength for the systematics
+was based on trial-and-error and what ``looked good'', as was the choice for the 
+hyperprior on the spectral
+slope and the maximum spherical harmonic degree of the map. Although the main
+features of the map (the monsoon over south Asia, the clouds over Africa and
+South America, and dark regions associated with the three major oceans) persist
+regardless of the choice of prior, their exact shapes and contrast varied
+significantly under different assumptions.
+
+Third, and most importantly, we have not performed actual inference: that is, 
+we simply found the maximum likelihood solution (subject to our constraints),
+with no estimate of the uncertainty anywhere on our map. A much better
+approach than simply maximizing the likelihood function is to marginalize
+over the nuisance parameters---such as the systematic model weights and the spectral
+slope. This is more costly, but certainly not intractable, and we will
+pursue this in upcoming work.
 
@@
 \label{sec:confirmation}
-\todo{bla bla bla}
+
+It is difficult to avoid being disingenuous in one's solution
+when the answer (or the expected answer)
+to a problem is known ahead of time. Since we had access to 
+``ground truth'' from the beginning, many of the de-trending/processing/fitting
+choices we made were (however inadvertently) driven by the desire to
+come as close as possible to the correct answer. While many of these choices
+correspond to numbers we have explicitly quoted here, such as the prior
+variances on our model terms, several of them are implicit decisions on
+\emph{how} we performed the analysis. For instance, in an early version of 
+the project we used as regressors actual \tess housekeeping variables---such as the angle 
+and elevation of the Earth and the Moon relative to each of the four camera 
+boresights---instead of the PLD basis. However, the systematics model constructed from these quantities
+proved to be too inflexible, judging in part from the poor fidelity of the recovered
+maps. The results in this work
+must therefore be taken with a grain of salt. That said, we have attempted to
+offset the possibility of confirmation bias by making our model
+(Equation~\ref{eq:model}) as simple as possible in the end (a multiplicative baseline
+and a linear reflectance model) and thus limiting
+the number of knobs we could turn. We also opted to fit for the spectral
+slope of the map rather than use the power spectrum inferred from 
+real imaging data. Moreover, the broad features in the strongly
+regularized map (Figure~\ref{map_L2})---and in particular the monsoon clouds
+over southeast Asia---are insensitive to most of our model choices.
 

### 2019-03-27 tex/ms.tex
more discussions

@@
 real imaging data. Moreover, the broad features in the strongly
-regularized map (Figure~\ref{map_L2})---and in particular the monsoon clouds
+regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
 over southeast Asia---are insensitive to most of our model choices.
+
+\subsection{Sources of Bias}
+\label{sec:bias}
+
+One of the largest sources of bias is the fact that we assumed our
+systematics model is strictly multiplicative. Although we subtracted
+an estimate of the baseline non-Sol d background flux from each target
+(measured from the mid-sector portions of the light curve where the
+planet was below the edge of the sunshade), we implicitly assumed
+that this constant baseline was the \emph{only} source of additive
+noise. We know this to be strictly untrue, as Sol d is known to
+have a companion (Sol d I), a moon about one-third the diameter of 
+Sol d, whose reflected light should cause periodic modulations
+in the background flux of \tess pixels. Because of its small size and
+very low ($\sim 0.1$) albedo, we chose to ignore its effect, but it
+is likely to contaminate our signal at certain points in the orbit
+where \tess is closer to Sol d I than to Sol d. While this will
+likely bias the \starry model at those times, the effect is particularly
+concerning because of its impact on the PLD basis. While PLD can be an
+extremely powerful de-trending technique, it is notorious for
+grossly overfitting signals in the presence of uncorrected background
+modulations \citep{Luger2016}. This happens because PLD strictly
+assumes the noise is multiplicative, which is not the case for 
+signals with varying (additive) background levels. In principle, one
+could model the reflectance variability of Sol d I in the same way as
+we did here, but since the optics are not well understood, this 
+may be difficult in practice.
+
+In our analysis, we also neglected the effects of limb darkening. Because of
+atmospheric attenuation, features near the limb of the planet should in
+reality contribute less to the flux than our model predicts. This could
+bias our results particularly in cases where the planet is seen at half
+phase (for instance, during days 1326 and 1341 in Figure~\ref{fig:phases}).
+In the absence of limb darkening, the brightest regions on the planet are those
+close to the sub-stellar point, which is on the limb. Limb darkening should
+shift the regions of peak brightness closer to the center of the planet, adding
+an east-west bias in the location of the features we identify.
+
+We also ignored the finite angular size of Sol at Sol d (about $0.5^\circ$),
+treating it instead as a point source. Regions immediately nightward of the 
+terminator should therefore contribute a small amount of flux, which we neglect.
+The effect, however, is below the resolution of our inferred map, so we expect
+it does not introduce significant bias.
+
+Moreover, we implicitly assumed an isotropic prior on the spherical harmonic
+coefficients by imposing a power spectrum in only the degree $l$. This has the
+effect of lessening the extent to which features can be confined to certain
+latitudes. In particular, our prior implicitly disfavors banded cloud structure,
+which one may \emph{a priori} expect on a rapidly rotating planet such as 
+Sol d. The bottom panel of Figure~\ref{fig:map} shows such banded structure
+at the equator and at mid-latitudes due to the combined effects of 
+north-south circulation and deflection by the Coriolis force.
+
+Finally, and perhaps more importantly, our model assumed a \emph{static}
+map for the surface of Sol d. We also know this to be incorrect, since
+clouds form and move on timescales of hours to days. We discuss this in
+detail next.
+
+% \begin{figure}[t!]
+%     \begin{centering}
+%     \includegraphics[width=\linewidth]{figures/map_labels.pdf}
+%     \caption{\label{fig:map_labels}
+%             Map of Sol d with the major features indicated with suggested
+%             names.
+%             \codelink{earthshine_S1_S2}
+%             }
+%     \end{centering}
+% \end{figure}
 
@@
 \end{figure}
-
-\subsection{Sources of Bias}
-\label{sec:bias}
-
-\todo{PLD, moon background, etc.}
-
-In our analysis, we neglected the effects of limb darkening. Because of
-atmospheric attenuation, features near the limb of the planet should in
-reality contribute less to the flux than our model predicts. This could
-bias our results particularly in cases where the planet is seen at half
-phase (for instance, during days 1326 and 1341 in Figure~\ref{fig:phases}).
-In the absence of limb darkening, the brightest regions on the planet are those
-close to the sub-stellar point, which is on the limb. Limb darkening should
-shift the regions of peak brightness closer to the center of the planet, adding
-an east-west bias in the location of the features we identify.
-
-We also ignored the finite angular size of Sol at Sol d (about $0.5^\circ$),
-treating it instead as a point source. Regions immediately nightward of the 
-terminator should therefore contribute a small amount of flux, which we neglect.
-The effect, however, is below the resolution of our inferred map, so we expect
-it does not introduce significant bias.
-
-Finally, we implicitly assumed an isotropic prior on the spherical harmonic
-coefficients by imposing a power spectrum in only the degree $l$. This has the
-effect of lessening the extent to which features can be confined to certain
-latitudes. In particular, our prior implicitly disfavors banded cloud structure,
-which one may \emph{a priori} expect on a rapidly rotating planet such as 
-Sol d. The bottom panel of Figure~\ref{fig:map} shows such banded structure
-at the equator and at mid-latitudes due to the combined effects of 
-north-south circulation and deflection by the Coriolis force.
-
-% \begin{figure}[t!]
-%     \begin{centering}
-%     \includegraphics[width=\linewidth]{figures/map_labels.pdf}
-%     \caption{\label{fig:map_labels}
-%             Map of Sol d with the major features indicated with suggested
-%             names.
-%             \codelink{earthshine_S1_S2}
-%             }
-%     \end{centering}
-% \end{figure}
 

### 2019-03-27 tex/ms.tex
blurb

@@
 
-Residuals in Figure~\ref{fig:model} display significant correlated
-structure. Talk about their power spectrum. Talk about how S2 is worse fit.
+\todo{Residuals in Figure~\ref{fig:model} display significant correlated
+structure. Talk about their power spectrum. Temporal fit helps. Discuss
+Figure~\ref{fig:map_temporal} and argue we have evidence for clouds.}
 
@@
 
-\todo{For realz, how would we do this.}
+\todo{Discuss how we would we do this for an actual exoplanet, and
+all the homework we need to do before that happens.}
 

### 2019-03-27 tex/ms.tex
lil more intro

--- 2019-03-27 tex/ms.tex
@@
 
-%Resolving the features of planetary atmospheres and surfaces with precise 
-%photometry is a crucial 
-Precise photometry obtained over long periods of time can reveal the atmospheric 
-and surface features of an exoplanet through the method known as phase mapping. 
+Of the many challenges and opportunities facing the field of exoplanets in the future, the prospect of mapping the surface of an Earth-like planet is one of the most exciting -- and one of the most difficult.
+Present-day missions including the Transiting Exoplanet Survey Satellite \citep[\TESS; ][]{Ricker2015} aim to discover small terrestrial planets around bright, nearby stars. 
+Once these targets are found, efforts to characterize them in detail and determine their habitability will begin in earnest. 
+The discovery of surface features including continents and oceans will be a critical hint for the habitability of an alien world.
+
+Such mapping can be done by constructing a phase map of the planet using precise photometry obtained over long periods of time. 
 \todo{(literature background \& citations)}
@@
 in this particular problem. In practice, however, it is evident from
-Figure~\ref{fig:map} that degenaricies still abound. While we infer a few of the
-dominant features of the cloud map of Sol d, several of them are skewed, 
-shifted, or entirely out of place. This is the case, for instance, with
-the cloud bank west of South America, which extends too far westward, and
-the northern Atlantic Ocean, which appears to extends into the east coast of
-North America. We identify three broad reasons for this.
-
-First, many of the issues arise because
+Figure~\ref{fig:map} that degenaricies still abound. This is likely because
 of the finite signal-to-noise of our measurements and various biases in
@@
 attempt to na{\"i}vely model it with pixel-level decorrelation, likely
-introduces significant correlated noise into the problem. We discuss this
-and other sources of bias in more detail in \S\ref{sec:bias} below.
-
-Second, while we attempted to adopt agnostic priors on the map coefficients---i.e.,
-we fit for a spectral slope rather than impose one---our inferred map is still 
-heavily prior-dependent. Our choice of regularization strength for the systematics
-was based on trial-and-error and what ``looked good'', as was the choice for the 
-hyperprior on the spectral
-slope and the maximum spherical harmonic degree of the map. Although the main
-features of the map (the monsoon over south Asia, the clouds over Africa and
-South America, and dark regions associated with the three major oceans) persist
-regardless of the choice of prior, their exact shapes and contrast varied
-significantly under different assumptions.
-
-Third, and most importantly, we have not performed actual inference: that is, 
-we simply found the maximum likelihood solution (subject to our constraints),
-with no estimate of the uncertainty anywhere on our map. A much better
-approach than simply maximizing the likelihood function is to marginalize
-over the nuisance parameters---such as the systematic model weights and the spectral
-slope. This is more costly, but certainly not intractable, and we will
-pursue this in upcoming work.
+introduces significant correlated noise into the problem. We discuss
+sources of bias in more detail in \S\ref{sec:bias} below
 
@@
 \label{sec:confirmation}
-
-It is difficult to avoid being disingenuous in one's solution
-when the answer (or the expected answer)
-to a problem is known ahead of time. Since we had access to 
-``ground truth'' from the beginning, many of the de-trending/processing/fitting
-choices we made were (however inadvertently) driven by the desire to
-come as close as possible to the correct answer. While many of these choices
-correspond to numbers we have explicitly quoted here, such as the prior
-variances on our model terms, several of them are implicit decisions on
-\emph{how} we performed the analysis. For instance, in an early version of 
-the project we used as regressors actual \tess housekeeping variables---such as the angle 
-and elevation of the Earth and the Moon relative to each of the four camera 
-boresights---instead of the PLD basis. However, the systematics model constructed from these quantities
-proved to be too inflexible, judging in part from the poor fidelity of the recovered
-maps. The results in this work
-must therefore be taken with a grain of salt. That said, we have attempted to
-offset the possibility of confirmation bias by making our model
-(Equation~\ref{eq:model}) as simple as possible in the end (a multiplicative baseline
-and a linear reflectance model) and thus limiting
-the number of knobs we could turn. We also opted to fit for the spectral
-slope of the map rather than use the power spectrum inferred from 
-real imaging data. Moreover, the broad features in the strongly
-regularized map (Figure~\ref{map_L2})---and in particular the monsoon clouds
-over southeast Asia---are insensitive to most of our model choices.
+\todo{bla bla bla}
 

### 2019-03-27 tex/ms.tex
done for the day

@@
 \todo{(literature background \& citations)}
+
+\todo{We need to cite} \citep{Berdyugina2017,Cowan2009,Cowan2018,Haggard2018,Kawahara2010,Fujii2012,Lustig-Yaeger2018} and others.
+
+\todo{We need to cite}\citep{Knutson2007,Majeau2012,deWit2012} on the first maps of an exoplanet.
 
@@
 
-% \begin{figure}[t!]
-%     \begin{centering}
-%     \includegraphics[width=\linewidth]{figures/map_labels.pdf}
-%     \caption{\label{fig:map_labels}
-%             Map of Sol d with the major features indicated with suggested
-%             names.
-%             \codelink{earthshine_S1_S2}
-%             }
-%     \end{centering}
-% \end{figure}
-
 \subsection{Temporal Evolution}
@@
 
-\todo{Residuals in Figure~\ref{fig:model} display significant correlated
-structure. Talk about their power spectrum. Temporal fit helps. Discuss
-Figure~\ref{fig:map_temporal} and argue we have evidence for clouds.}
+As we mentioned in \S\ref{sec:results}, the residuals about our maximum
+likelihood fit show correlated structure with power at a large range
+of periods ranging from 0.1 up to 10 days. This is likely due to 
+the fact that rotational variability is not the sole source of the
+signal of Sol d: additionally, there is likely temporal variation in the 
+albedo of certain parts of the map, most probably due to cloud movement.
+In order to test this, we used \starry to construct a time-variable
+spherical harmonic map, defined by a vector of spherical harmonic coefficients
+that varies slowly over time:
+%
+\begin{align}
+    \mathbf{y}(t) = \sum_{n=0}^N \mathbf{y}_n c_n(t)
+\end{align}
+%
+where the $\mathbf{y}_n$ are the $N$ spherical harmonic coefficient
+vectors that describe the temporal variability and the $c_n$ are the components
+of the basis in time. Since this is a linear operation on the spherical
+harmonic coefficients, the \starry model is still linear, and may be
+solved in the same way as before.
+
+We choose the $c_n$ vectors to be an orthogonal polynomial basis in time of 
+degree 6 spanning all of Sector 1. Under this basis, one can 
+approximately interpret
+$\mathbf{y}_0$ as the static component of the map, $\mathbf{y}_1$ as the
+component that varies quasi-linearly in time, $\mathbf{y}_2$ as the component
+that varies quasi-quadratically, and so forth. In all, we fit for six
+of these map components.
+
+We neglect the data taken in Sector 2, focusing instead on the portion of the data for which
+we have good temporal coverage. In order to mitigate overfitting due to
+the larger number of variables we are solving for,
+we add a term to our likelihood function that forces the coefficients
+of the $n > 0$ maps to remain small. We further evaluate the albedo of the map
+on a grid at six equally spaced points in time, enforcing our albedo and
+power spectrum priors separately at each of these points.
 
@@
 
-\subsection{Application to Other Planets}
+The mean of the temporal solution is shown in Figure~\ref{fig:map_temporal},
+and a link to an animated version is provided in the caption. No significant
+differences are evident, although the residuals improved by ${\sim}30\%$
+and contain significantly less power on timescales longer than 1 day.
+We conclude that while this is evidence for cloud variability on these
+timescales, a more detailed investigation is warranted to say anything
+meaningful about the dynamics of clouds on Sol d.
+
+\subsection{Implication for Future Observations}
 \label{sec:otherplanets}
 
-\todo{Discuss how we would we do this for an actual exoplanet, and
-all the homework we need to do before that happens.}
+Observed in the \tess band, Sol d is a planet dominated by
+clouds. \todo{Discuss how this problem is *hard* and how we need
+large time baseline to disentangle clouds from continents, and even
+then there are cloud features that are stationary, so hard to
+tell apart. What we really need is multi-band photometry,
+as suggested in \cite{Cowan2009}.}
 
@@
 \todo{(summarize)}
-
-\todo{(utility for \TESS background removal)}
-
 \todo{(talk abt prospects for doing this analysis with exoplanets)}

### 2019-03-27 tex/ms.tex
fixed some typos

@@
 \footnote{See \url{https://ssd.jpl.nasa.gov/horizons.cgi} and 
-\href{https://github.com/rodluger/earthshine/blob/master/notebooks/SanitCheck.ipynb}{this
+\href{https://github.com/rodluger/earthshine/blob/master/notebooks/SanityCheck.ipynb}{this
 Jupyter notebook.}}.
@@
 concerning; nevertheless, we impose an L2 prior on the weights with
-standard deviation $\sigma_B = 0.1$ (see \S\ref{sec:model}).
+standard deviation $\sigma_w = 0.05$ (see \S\ref{sec:model}).
 
@@
 %
-with $\sigma_w = 0.1$ and 
+with $\sigma_w = 0.05$ and 
 %
@@
 For simplicity, all our prior covariances are diagonal and
-homoscedastic with variances equal to $2.5\times 10^{-3}$ for $\mathbf{w}$, and
-$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\boldsymbol{\rho}$.
+homoscedastic with variances equal to $2.5\times 10^{-3}$ for $\mathbf{w}$,
+$10^{-8}$ for $\mathbf{a}$, and $10^{-1}$ for $\boldsymbol{\rho}$.
 
@@
 problem is fundamentally non-invertible, since most of the information
-one wishes to extract lies in the null space.
+one wishes to extract never makes it into the light curve in the first place.
 
@@
 the changing vantage point of \tess relative to Sol d (and our exact knowledge of it)
-break degeneracies that are viewpoint-dependent. In particular, the motion of
+breaks degeneracies that are viewpoint-dependent. In particular, the motion of
 \tess changes the position and shape of the terminator on the projected disk
@@
 
-In fact, because of these points, there should formally be \emph{no} null space 
+In fact, because of these points, there should actually be \emph{no} null space 
 in this particular problem. In practice, however, it is evident from
@@
 the cloud bank west of South America, which extends too far westward, and
-the northern Atlantic Ocean, which appears to extends into the east coast of
-North America. We identify three broad reasons for this.
+the northern Atlantic Ocean, which appears to extend into the east coast of
+North America. We identify four broad reasons for this.
 
@@
 measured at 95 different positions on the detector---our lack of understanding
-of the complex optics that give rise to the signal in the first place, and our
-attempt to na{\"i}vely model it with pixel-level decorrelation, likely
-introduces significant correlated noise into the problem. We discuss this
+of the complex optics (and our
+attempt to na{\"i}vely model it with pixel-level decorrelation) likely
+introduces significant correlated noise when we de-trend. We discuss this
 and other sources of bias in more detail in \S\ref{sec:bias} below.
@@
 
-Third, and most importantly, we have not performed actual inference: that is, 
+Third, inspection of Figure~\ref{fig:phases} shows that most of the time, Sol
+d is close to full phase as seen by \tess.
+With the terminator close to the limb
+of the planet, its ability to break degeneracies is considerably lessened.
+We are therefore somewhat limited in our ability to infer in particular the
+latitudinal position of features. Observations of Sol d in upcoming
+sectors may contain longer segments in which Sol d is seen in crescent,
+which should help mitigate these degeneracies.
+
+Fourth, and most importantly, we have not performed actual inference: that is, 
 we simply found the maximum likelihood solution (subject to our constraints),
@@
 
-\subsection{Sources of Bias}
+\subsection{Other Kinds of Bias}
 \label{sec:bias}
@@
 clouds form and move on timescales of hours to days. We discuss this in
-detail next.
+detail in the following section.
 
@@
 the fact that rotational variability is not the sole source of the
-signal of Sol d: additionally, there is likely temporal variation in the 
+signal of Sol d: additionally, there is temporal variation in the 
 albedo of certain parts of the map, most probably due to cloud movement.
@@
 degree 6 spanning all of Sector 1. Under this basis, one can 
-approximately interpret
+interpret
 $\mathbf{y}_0$ as the static component of the map, $\mathbf{y}_1$ as the
-component that varies quasi-linearly in time, $\mathbf{y}_2$ as the component
-that varies quasi-quadratically, and so forth. In all, we fit for six
+component that varies (quasi-)linearly in time, $\mathbf{y}_2$ as the component
+that varies (quasi-)quadratically, and so forth. In all, we fit for six
 of these map components.

### 2019-03-27 tex/ms.tex
a little more text

@@
 
-Observed in the \tess band, Sol d is a planet dominated by
-clouds. \todo{Discuss how this problem is *hard* and how we need
+As we discussed above, light curve inversion is a hard problem,
+and we have shown that this is true even when the solution is
+known ahead of time. Presented with the top panel of Figure~\ref{fig:map}
+(without the continent outlines),
+an inhabitant of Sol d would be hard-pressed to identify that
+as a map of their home planet. This is in part due to the biases
+in our optimization, which we discussed above, but also due to the 
+simple fact that the reflectance of Sol d is dominated---by far---by clouds.
+
+\todo{Discuss how this problem is *hard* and how we need
 large time baseline to disentangle clouds from continents, and even

### 2019-03-27 tex/ms.tex
more wordzzzz

@@
 in our optimization, which we discussed above, but also due to the 
-simple fact that the reflectance of Sol d is dominated---by far---by clouds.
+simple fact that the reflectance of Sol d is dominated---by far---by 
+time-variable clouds. While stationary cloud features on Sol d are
+typically associated with continents (the most pronounced cloud features
+being over South America, Africa, and south Asia), persistent cloud
+cover can occur over open ocean, as seen in the north Pacific
+in Figure~\ref{fig:map}. Given a baseline of just a few weeks, it is
+not possible to tell the difference between highly reflective land
+features (such as ice or vegetation) and stationary clouds.
+
+We should not expect other exoplanets in the habitable zone to be
+any different.
 

### 2019-03-28 tex/ms.tex
Boom

@@
 
+\todo{We need to cite \cite{Sagan1993}!}
+
 A new source of precise photometry is the Transiting Exoplanet Survey Satellite 
@@
 reflected-light mapping of planetary surface features on Sol d. 
-We give an overview of the \TESS data used in Section \ref{sec:data}. 
-In Section \ref{sec:methods}, we describe the methods employed to infer a map 
+We give an overview of the \TESS data used in \S\ref{sec:data}. 
+In \S\ref{sec:methods}, we describe the methods employed to infer a map 
 from these data, including the adaptation of the \starry algorithm to reflection 
@@
 priors used. 
-We present results in Section \ref{sec:results} and make comparison of these 
+We present results in \S\ref{sec:results} and make comparison of these 
 findings to state-of-the-art terrestrial planet maps from the literature in 
-Section \ref{sec:discussion}. 
-Finally, we conclude in Section \ref{sec:conclusion} with a look at future 
+\S\ref{sec:discussion}. 
+Finally, we conclude in \S\ref{sec:conclusions} with a look at future 
 prospects for phase-curve mapping of terrestrial exoplanets.
@@
 For each of the two sectors considered, we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across the full \TESS field of view and extracted the background flux time series from each.
-Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see Section \ref{sec:systematics}).
+Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see \S\ref{sec:systematics}).
 We down-selected our pool of 1000 targets to 75 maximally useful background lightcurves from Sector 1 and 20 from Sector 2. 
@@
 As we discussed above, light curve inversion is a hard problem,
-and we have shown that this is true even when the solution is
+and we have shown that this is true even at high signal-to-noise and 
+when the solution is
 known ahead of time. Presented with the top panel of Figure~\ref{fig:map}
 (without the continent outlines),
-an inhabitant of Sol d would be hard-pressed to identify that
+an inhabitant of Sol d may be hard-pressed to identify that
 as a map of their home planet. This is in part due to the biases
@@
 We should not expect other exoplanets in the habitable zone to be
-any different.
+any different. Future missions such as LUVOIR or HabEx may enable
+us to collect data on the phase curves of such planets, but that
+data will be of signficantly lower quality and poorer time resolution,
+so the work presented here can be seen as an upper limit on what we may
+be able to infer about exoplanets in the habitable zone with
+next-generation facilities.
 
-\todo{Discuss how this problem is *hard* and how we need
-large time baseline to disentangle clouds from continents, and even
-then there are cloud features that are stationary, so hard to
-tell apart. What we really need is multi-band photometry,
-as suggested in \cite{Cowan2009}.}
+That said, the time baseline considered in this work was fairly
+limited---three weeks in Sector 1 and one week in Sector 2,
+spanning two months in total. Observations taken throughout an entire
+year on Sol d---during which time cloud patterns should change with the
+seasons and the angle between the day/night terminator and the 
+axis of rotation should precess---may help to disambiguate between
+clouds, oceans, and continents. We intend to perform this analysis
+in upcoming work once data from future \tess sectors becomes available.
 
-\section{Conclusion}
-\label{sec:conclusion}
+Alternatively, time-resolved observations in multiple bands could
+also help with this problem. This was discussed in \cite{Cowan2009},
+who showed that multi-band photometry of the Earth enables one to
+disentangle the contributions from oceans, continents, and cloud cover.
+A robust detection of surface features on an exoplanet in the habitable
+zone will likely necessitate both approaches alongside a circumspect
+analysis of the uncertainties and degeneracies at play.
+
+\section{Conclusions}
+\label{sec:conclusions}
 

### 2019-03-28 tex/ms.tex
tweaks

@@
 The \TESS pipeline produces processed lightcurves for all short-cadence targets. 
-Part of this processing is the determination of the localized background flux within each postage stamp, which is provided as an ancillary time series. 
-As with all \TESS time series data products, the time is given in \TESS Julian Days (TJD), defined as BJD - 2457000, and the data are delivered in 27-day parcels corresponding to the varying pointing sectors of \TESS.
-We use these background flux measurements from Sectors 1 and 2 as our primary data source in this work.
+Part of this processing is the determination of the localized background flux 
+within each postage stamp, which is provided as an ancillary time series. 
+As with all \TESS time series data products, the time is given in \TESS Julian 
+Days (TJD), defined as $\mathrm{BJD} - 2457000$, and the data are delivered in 27-day 
+parcels corresponding to the varying pointing sectors of \TESS. 
+We use these background flux measurements from Sectors 1 and 2 as our primary 
+data source in this work.
 
-For each of the two sectors considered, we downloaded a randomized subsample of 1000 short-cadence lightcurve files corresponding to postage stamps located across the full \TESS field of view and extracted the background flux time series from each.
-Not all postage stamps are equally informative, since the desired signal from Sol d is inhomogenously spread across the \TESS detectors and manifests differently in different regions (see \S\ref{sec:systematics}).
-We down-selected our pool of 1000 targets to 75 maximally useful background lightcurves from Sector 1 and 20 from Sector 2. 
-This down-selection was done with several criteria in mind: each lightcurve should contain a significant signal from Sol d; they should be representative of the general background flux modulation seen across the \TESS cameras, rather than containing any truly localized signals from astrophysical background sources; and the sample as a whole should contain the full range of typical behaviors of background across the entire \TESS field of view.
-To accomplish this, we... \todo{(decide whether it's outlier rejection only or full-on categorization)}
+For each of the two sectors considered, we downloaded a random subsample of 
+1,000 short-cadence lightcurve files corresponding to postage stamps located 
+across the full \TESS field of view and extracted the background flux time 
+series from each. 
+Not all postage stamps are equally informative, since the desired signal from 
+Sol d is inhomogenously spread across the \TESS detectors and manifests 
+differently in different regions (see \S\ref{sec:systematics}). 
+We down-selected our pool of 1000 targets to 75 maximally useful background 
+lightcurves from Sector 1 and 20 from Sector 2. 
+This down-selection was done with several criteria in mind: each lightcurve 
+should contain a significant signal from Sol d; they should be representative 
+of the general background flux modulation seen across the \TESS cameras, rather 
+than containing any truly localized signals from astrophysical background 
+sources; and the sample as a whole should contain the full range of typical 
+behaviors of background across the entire \TESS field of view. 
+To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
+full-on categorization)}
 
-\todo{(masking out epochs without Sol d shine, subtraction of baseline background flux)}
+\todo{(masking out epochs without Sol d shine, subtraction of baseline 
+background flux)}
 
-The final data set to be used consists of 75 Sector 1 background lightcurves and 20 Sector 2 background lightcurves corresponding to the epochs at which Sol d signal was clearly registered by \TESS. 
+The final data set to be used consists of 75 Sector 1 background lightcurves 
+and 20 Sector 2 background lightcurves corresponding to the epochs at which 
+Sol d signal was clearly registered by \TESS. 
 This is 912,605 data points in total. 
@@
 \footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
-the Solar System and \tess ephemeris data for
+the Solar System and \TESS ephemeris data for
 Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
@@
 ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
-the relative positions of Sol, Sol d, and \tess for every cadence
+the relative positions of Sol, Sol d, and \TESS for every cadence
 in our dataset in the J2000 equatorial reference frame. In this right-handed
@@
 Finally, we rotate the frame to align
-\tess with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
+\TESS with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
 We verified our rotations by comparing our results on several days to the
@@
     \caption{\label{fig:phases}
-             \tess view of Sol d on every date in Sectors 1
+             \TESS view of Sol d on every date in Sectors 1
              and 2 that was included in the regression. Each image is
@@
 
-Figure~\ref{fig:phases} shows the view \tess has of Sol d on each of the dates
+Figure~\ref{fig:phases} shows the view \TESS has of Sol d on each of the dates
 in our dataset; these images were produced by applying the sequences of rotations
@@
 apart, the planet appears to slowly rotate over the course of the observation.
-This is because of the orbit of \tess, which changes its vantage point relative
+This is because of the orbit of \TESS, which changes its vantage point relative
 to Sol d over the course of its 13 day orbit.
@@
 model of the reflections and scattering that gives rise to the
-signal of Sol d on the \tess detector is beyond the scope of this work. Instead,
+signal of Sol d on the \TESS detector is beyond the scope of this work. Instead,
 we treat this as a de-trending problem, where the signal we wish to fit is
@@
 increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
-polynomials in time for each of the two orbits of \tess in each sector.
+polynomials in time for each of the two orbits of \TESS in each sector.
 The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
@@
              Normalized surface reflectance versus time for the maximum
-             likelihood \starry model in each of the four orbits of \tess
+             likelihood \starry model in each of the four orbits of \TESS
              in Sectors 1 and 2.
@@
 sharp rise at the beginning of each orbit in Sector 1 is due to the changing
-vantage point of \tess as Sol d transitions from a thin crescent to full phase.
+vantage point of \TESS as Sol d transitions from a thin crescent to full phase.
 
@@
 the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we happen
-to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
+to know the exact distance $\mathbf{r}$ between \TESS and Sol d at all times
 (\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
@@
 southern winter) or seldom in view (such as regions near the north pole of the planet,
-which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \tess).
+which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \TESS).
 Because there is little data from these regions, their albedo is prior-dominated
@@
 averaged over the 28 days of data analyzed in this work, smoothed it, 
-and weighted by the \tess visibility as in the top panel.
+and weighted by the \TESS visibility as in the top panel.
 
 While the two panels display fundamentally different quantities---an albedo
-and a cloudiness factor---we expect that the signal of Sol d in the \tess
+and a cloudiness factor---we expect that the signal of Sol d in the \TESS
 bandpass is dominated by cloud reflectivity, as water clouds have an albedo
@@
 the visible lune of the planet strictly remain in the null space. Second, 
-the changing vantage point of \tess relative to Sol d (and our exact knowledge of it)
+the changing vantage point of \TESS relative to Sol d (and our exact knowledge of it)
 breaks degeneracies that are viewpoint-dependent. In particular, the motion of
-\tess changes the position and shape of the terminator on the projected disk
+\TESS changes the position and shape of the terminator on the projected disk
 of Sol d, enhancing the effect discussed above.
@@
 Third, inspection of Figure~\ref{fig:phases} shows that most of the time, Sol
-d is close to full phase as seen by \tess.
+d is close to full phase as seen by \TESS.
 With the terminator close to the limb
@@
 \emph{how} we performed the analysis. For instance, in an early version of 
-the project we used as regressors actual \tess housekeeping variables---such as the angle 
+the project we used as regressors actual \TESS housekeeping variables---such as the angle 
 and elevation of the Earth and the Moon relative to each of the four camera 
@@
 Sol d, whose reflected light should cause periodic modulations
-in the background flux of \tess pixels. Because of its small size and
+in the background flux of \TESS pixels. Because of its small size and
 very low ($\sim 0.1$) albedo, we chose to ignore its effect, but it
 is likely to contaminate our signal at certain points in the orbit
-where \tess is closer to Sol d I than to Sol d. While this will
+where \TESS is closer to Sol d I than to Sol d. While this will
 likely bias the \starry model at those times, the effect is particularly
@@
 clouds, oceans, and continents. We intend to perform this analysis
-in upcoming work once data from future \tess sectors becomes available.
+in upcoming work once data from future \TESS sectors becomes available.
 

### 2019-03-28 tex/ms.tex
stuff

@@
 differently in different regions (see \S\ref{sec:systematics}). 
-We down-selected our pool of 1000 targets to 75 maximally useful background 
+We down-selected our pool of 1,000 targets to 75 maximally useful background 
 lightcurves from Sector 1 and 20 from Sector 2. 
@@
 heavily prior-dependent. Our choice of regularization strength for the systematics
-was based on trial-and-error and what ``looked good'', as was the choice for the 
+was based on trial-and-error and what ``looked good,'' as was the choice for the 
 hyperprior on the spectral
@@
 
-\todo{(summarize)}
-\todo{(talk abt prospects for doing this analysis with exoplanets)}
+We have used \TESS photometry to
+produce a global map of Sol d, a terrestrial planet in the habitable
+zone of a G2 main-sequence star. We adapted the \starry code to 
+generate (and invert) light curves in reflected light, coupling it
+to a variation of pixel level decorrelation to model the systematics
+in the \TESS detector. We detect three large scale bright regions near
+the equator of the planet, associated with persistent cloud structures
+at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
+likely track continents. Pronounced dark features are identified
+at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
+significant latitudinal extent, likely tracking oceans. Because of the
+vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
+high latitudes on the planet, although this may change with upcoming
+sectors.
+
+\todo{A bit more here.}
 
 \acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
-acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
+acknowledge Dan Foreman-Mackey, David W. Hogg, Ben Pope, \todo{and ...} 
 for useful conversations. Crucial parts of this work were carried out at the 
@@
 TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}
+
 % Bibliography
-\pagebreak
 \bibliography{bib}

### 2019-03-28 tex/ms.tex
better abstract

@@
 \usepackage{xcolor}
-\usepackage{xspace}
-\newcommand{\TESS}{\emph{TESS}\xspace}
 \newcommand{\todo}[1]{\textcolor{red}{#1}}
@@
 \begin{abstract}
-\todo{[maybe change first sentences to focus on planet mapping \& give the game 
-away less?]} The Transiting Exoplanet Survey Satellite (\TESS) mission is a 
-targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
-While \TESS is already enjoying great success with the discovery of many new worlds, 
-the strongest signal in its data is typically ignored, as it lurks in the background 
-of every camera pixel. In this work, we extract this signal and demonstrate that 
-it is consistent with a terrestrial planet with a rotation period of 1 day. 
+Multiple exoplanets have now been photometrically mapped using phase-modulated reflection or emission from their surfaces and atmospheres, but the small amplitudes of such signals have limited previous maps almost exclusively to hot gas giant planets.
+In this work, we uncover a signal using recently released data from the Transiting Exoplanet Survey Satellite (\TESS) which we show corresponds to time-variable reflection from a terrestrial 
+planet with a rotation period of $0.9972696$ days. 
 Using a spherical harmonic-based reflection model developed as an extension of 
@@
 world. We recover a time-variable albedo map of the planet including persistent 
-regions which we interpret as continental features and cloud banks. 
+regions which we interpret as oceans and cloud banks indicative of continental features. 
 We argue that this planet represents the most promising detection of a habitable 
@@
 
-Of the many challenges and opportunities facing the field of exoplanets in the future, the prospect of mapping the surface of an Earth-like planet is one of the most exciting -- and one of the most difficult.
+Of the many challenges and opportunities facing the field of exoplanets in the future, the prospect of mapping the surface of a potentially habitable planet is one of the most exciting -- and one of the most difficult.
 Present-day missions including the Transiting Exoplanet Survey Satellite \citep[\TESS; ][]{Ricker2015} aim to discover small terrestrial planets around bright, nearby stars. 
-Once these targets are found, efforts to characterize them in detail and determine their habitability will begin in earnest. 
-The discovery of surface features including continents and oceans will be a critical hint for the habitability of an alien world.
+Once these targets are found, much more detailed observational characterization must follow to evaluate their suitability for harboring life. 
+The discovery of surface features including continents and oceans would be a critical hint towards the habitability of an alien world.
 
-Such mapping can be done by constructing a phase map of the planet using precise photometry obtained over long periods of time. 
-\todo{(literature background \& citations)}
+The most straightforward method of observing features on a terrestrial exoplanet would be to directly image the planet at sufficient resolution. 
+However,
+
+Surface mapping can also be done by observing rotational phase-dependent variations of the planetary signal in precise photometric time series. 
+\todo{(summarize how it works)} 
+This is a complex data analysis problem: strong degeneracies are involved when transforming a 1-dimensional time series into a 2-dimensional surface map. 
+Interpretation is also challenging in the face of many potential explanations for a poorly resolved observed feature.
 
@@
 
-A new source of precise photometry is the Transiting Exoplanet Survey Satellite 
-\citep[\TESS; ][]{Ricker2015}. 
-Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, 
-citations to planet discoveries etc)}
+%A new source of precise photometry is the Transiting Exoplanet Survey Satellite 
+%\citep[\TESS; ][]{Ricker2015}. 
+%Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, 
+%citations to planet discoveries etc)}
 
-One intriguing feature of the \TESS photometric data products is a highly 
-time-variable signal represented in the diffuse background across virtually 
-all camera pixels. 
-\todo{(talk abt Earthshine without naming it)} 
-The signal has been widely attributed to a planet which we will call Sol d.
+%One intriguing feature of the \TESS photometric data products is a highly 
+%time-variable signal represented in the diffuse background across virtually 
+%all camera pixels. 
+%\todo{(talk abt Earthshine without naming it)} 
+%The signal has been widely attributed to a planet which we will call Sol d.
 
@@
 phases, enabling a level of spatial and temporal resolving power that is 
-unprecedented in the exoplanetary phase mapping literature.
+unprecedented in the history of exoplanet phase mapping.
 
-Moreover, recent advances in fast analytic computation of spherical harmonics 
-have made the reconstruction of such detailed maps more feasible than ever. 
-\todo{(STARRY)}
+Moreover, recent advances in the computational tractability of this data analysis problem 
+have made the reconstruction of detailed maps more feasible than ever. 
+\todo{(describe how STARRY works - fast analytic computation of spherical harmonics)}
 
@@
 priors used. 
-We present results in \S\ref{sec:results} and make comparison of these 
-findings to state-of-the-art terrestrial planet maps from the literature in 
+We present results in \S\ref{sec:results} and make a comparison of these 
+findings to state-of-the-art terrestrial planet maps in 
 \S\ref{sec:discussion}. 
-Finally, we conclude in \S\ref{sec:conclusions} with a look at future 
-prospects for phase-curve mapping of terrestrial exoplanets.
+Finally, we conclude in \S\ref{sec:conclusions}.
 
@@
 within each postage stamp, which is provided as an ancillary time series. 
-As with all \TESS time series data products, the time is given in \TESS Julian 
-Days (TJD), defined as $\mathrm{BJD} - 2457000$, and the data are delivered in 27-day 
+As with all \TESS time series data products, the time is given in units of \TESS Julian 
+Date (TJD), defined as $\mathrm{BJD} - 2457000$ \todo{(is this barycentric corrected?)}, and the data are delivered in 27-day 
 parcels corresponding to the varying pointing sectors of \TESS. 
@@
 to a variation of pixel level decorrelation to model the systematics
-in the \TESS detector. We detect three large scale bright regions near
+in the \TESS detector.
+
+We detect three large scale bright regions near
 the equator of the planet, associated with persistent cloud structures
@@
 
+In conclusion, we have demonstrated that \TESS is an effective addition to NASA's fleet of weather satellites.
+
 \acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
-acknowledge Dan Foreman-Mackey, David W. Hogg, Ben Pope, \todo{and ...} 
+acknowledge Jonathan Fraine, Dan Foreman-Mackey, David W. Hogg, Ben Montet, and Ben Pope 
 for useful conversations. Crucial parts of this work were carried out at the 

### 2019-03-28 tex/ms.tex
arxiver tag and a bit more intro

@@
 \begin{document}
+
+%@arxiver{map.pdf}
 
@@
 The most straightforward method of observing features on a terrestrial exoplanet would be to directly image the planet at sufficient resolution. 
-However,
+However, such an observation would require an effective telescope aperture orders of magnitude larger than currently available as well as extremely advanced coronagraphic optics, making it a far-future goal.
 
 Surface mapping can also be done by observing rotational phase-dependent variations of the planetary signal in precise photometric time series. 
-\todo{(summarize how it works)} 
 This is a complex data analysis problem: strong degeneracies are involved when transforming a 1-dimensional time series into a 2-dimensional surface map. 
@@
 
-\todo{We need to cite} \citep{Berdyugina2017,Cowan2009,Cowan2018,Haggard2018,Kawahara2010,Fujii2012,Lustig-Yaeger2018} and others.
+\todo{(Summary of previous mapping work:)}\citep{Knutson2007,Majeau2012,deWit2012}
 
-\todo{We need to cite}\citep{Knutson2007,Majeau2012,deWit2012} on the first maps of an exoplanet.
+\todo{(Discussion of expanding this work to terrestrial planets and/or reflected light:)} \citep{Berdyugina2017,Cowan2009,Cowan2018,Haggard2018,Kawahara2010,Fujii2012,Lustig-Yaeger2018} and others.
 
@@
 
-%A new source of precise photometry is the Transiting Exoplanet Survey Satellite 
-%\citep[\TESS; ][]{Ricker2015}. 
-%Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, 
-%citations to planet discoveries etc)}
+The \TESS mission promises to deliver thousands of new exoplanets around bright, nearby stars, many of which may be terrestrial worlds potentially suitable for life. 
+In fact, one such world, a planet which we will call Sol d, has already been extensively observed by \TESS.
 
-%One intriguing feature of the \TESS photometric data products is a highly 
-%time-variable signal represented in the diffuse background across virtually 
-%all camera pixels. 
-%\todo{(talk abt Earthshine without naming it)} 
-%The signal has been widely attributed to a planet which we will call Sol d.
-
-Previous attempts to map this planet from the exoplanet community have suggested 
+Previous attempts to map Sol d from the exoplanet community have suggested 
 the presence of localized surface features, but their resolving power has been 
@@
 \todo{(describe how STARRY works - fast analytic computation of spherical harmonics)}
+\todo{(also maybe say something about Cowan approach)}
 

### 2019-03-28 tex/ms.tex
tweak
minor changes
data

@@
 \begin{abstract}
-Multiple exoplanets have now been photometrically mapped using phase-modulated reflection or emission from their surfaces and atmospheres, but the small amplitudes of such signals have limited previous maps almost exclusively to hot gas giant planets.
-In this work, we uncover a signal using recently released data from the Transiting Exoplanet Survey Satellite (\TESS) which we show corresponds to time-variable reflection from a terrestrial 
+Multiple exoplanets have now been photometrically mapped using phase-modulated 
+reflection or emission from their surfaces and atmospheres, but the small amplitudes 
+of such signals have limited previous maps almost exclusively to hot gas giant planets. 
+In this work, we uncover a signal using recently released data from the Transiting 
+Exoplanet Survey Satellite (\TESS) which we show corresponds to time-variable reflection 
+from a terrestrial 
 planet with a rotation period of $0.9972696$ days. 
@@
 across the full \TESS field of view and extracted the background flux time 
-series from each. 
+series (\textsf{SAP\_BKG}) and corresponding uncertainties
+(\textsf{SAP\_BKG\_ERR}) from each. 
 Not all postage stamps are equally informative, since the desired signal from 
-Sol d is inhomogenously spread across the \TESS detectors and manifests 
+Sol d is inhomogenously spread across the \TESS detectors and manifests itself
 differently in different regions (see \S\ref{sec:systematics}). 
@@
 behaviors of background across the entire \TESS field of view. 
-To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
-full-on categorization)}
-
-\todo{(masking out epochs without Sol d shine, subtraction of baseline 
-background flux)}
-
-The final data set to be used consists of 75 Sector 1 background lightcurves 
-and 20 Sector 2 background lightcurves corresponding to the epochs at which 
-Sol d signal was clearly registered by \TESS. 
-This is 912,605 data points in total. 
+To accomplish this, we interpolated all light curves in Sector 1 onto the same time
+grid, masked all cadences with nonzero \textsf{QUALITY} flags and
+cadences during which Sol d was below the edge of the sunshade, and
+normalized them to the same min-max range. We then computed the median
+flux at each cadence along with an estimate of the variance from the
+median absolute deviation (MAD) across all light curves.
+For each light curve, we then computed a score $\chi^2$ equal to the sum of the squares of the
+deviation from the median at each of the $N$ cadences, normalized by the variance.
+We removed all light curves with $\chi^2 < N$ from the pool, placing
+them in a separate group. We repeated these steps several times,
+classifying light curves into four groups for Sector 1 and two groups for Sector 2. 
+We found that this
+procedure effectively grouped together light curves with similar features,
+increasing in variation within each group from the first group (most homogeneous) 
+to the last group (most heterogeneous). In practice, we found light curves
+in all but the last group to be dominated by 
+the signal of Sol d, while light
+curves in the last group were dominated by signals other than the
+periodic modulation of the planet. To obtain our final set of light curves, 
+we sorted the light curves in each group by the amplitude
+of the signal and kept the first 25 in each of the first three groups in Sector 1
+and the first 20 in the first group in Sector 2 for a total
+of 75 and 20 light curves, respectively. Our final dataset consisted of
+912,605 data points in total. 
 A representative sample of these signals is shown in Figure~\ref{fig:data}.

### 2019-03-28 tex/ms.tex
stuff

@@
 \S\ref{sec:discussion}. 
-Finally, we conclude in \S\ref{sec:conclusions}.
+Finally, we conclude with a summary of our major findings in \S\ref{sec:conclusions}.
 
@@
 As with all \TESS time series data products, the time is given in units of \TESS Julian 
-Date (TJD), defined as $\mathrm{BJD} - 2457000$ \todo{(is this barycentric corrected?)}, and the data are delivered in 27-day 
+Date (TJD), defined as $\mathrm{BJD} - 2457000$, and the data are delivered in 27-day 
 parcels corresponding to the varying pointing sectors of \TESS. 
@@
 grid, masked all cadences with nonzero \textsf{QUALITY} flags and
-cadences during which Sol d was below the edge of the sunshade, and
-normalized them to the same min-max range. We then computed the median
-flux at each cadence along with an estimate of the variance from the
+cadences during which Sol d was below the edge of the sunshade.
+During the selection step only, we also normalized them to the same min-max range.
+We then computed the median
+flux at each cadence along with an estimate of the variance based on the
 median absolute deviation (MAD) across all light curves.
-For each light curve, we then computed a score $\chi^2$ equal to the sum of the squares of the
+For each light curve, we calculated a score $\chi^2$ equal to the sum of the squares of the
 deviation from the median at each of the $N$ cadences, normalized by the variance.
@@
 and the first 20 in the first group in Sector 2 for a total
-of 75 and 20 light curves, respectively. Our final dataset consisted of
-912,605 data points in total. 
+of 75 and 20 light curves, respectively. We then computed an estimate of the
+non-Sol d background flux from the cadences during which the planet was below
+the edge of the sunshade and removed this baseline from the flux.
+Finally, we median-normalized all light curves (as opposed to the min-max
+normalization used for the classification).
+Our final dataset consisted of 912,605 data points in total. 
 A representative sample of these signals is shown in Figure~\ref{fig:data}.
@@
 terminator should therefore contribute a small amount of flux, which we neglect.
-The effect, however, is below the resolution of our inferred map, so we expect
-it does not introduce significant bias.
+Similarly, we used the timestamps reported in the \tess light curve
+FITS files, which are corrected to the barycenter of the Sol system. Since
+our signal originates from a source that is closer to \tess than the
+barycenter of the system, the timestamps may be wrong by up to 8 minutes,
+the light travel time from \tess to Sol. During 8 minutes, Sol d rotates
+by about $2^\circ$, so there should be a blurring of our inferred map at
+this scale. However, these two effects
+are well below the resolution of our map, so we expect
+them not to introduce significant bias.
 

### 2019-03-28 tex/ms.tex
tweaked abstract

@@
 \begin{abstract}
-Multiple exoplanets have now been photometrically mapped using phase-modulated 
-reflection or emission from their surfaces and atmospheres, but the small amplitudes 
-of such signals have limited previous maps almost exclusively to hot gas giant planets. 
+To date, a handful of exoplanets have been photometrically mapped using phase-modulated 
+reflection or emission from their surfaces, but the small amplitudes 
+of such signals have limited previous maps almost exclusively to coarse dipolar
+features on hot giant planets. 
 In this work, we uncover a signal using recently released data from the Transiting 
-Exoplanet Survey Satellite (\TESS) which we show corresponds to time-variable reflection 
+Exoplanet Survey Satellite (\TESS), which we show corresponds to time-variable reflection 
 from a terrestrial 

### 2019-03-28 tex/ms.tex
intro

@@
 
-Of the many challenges and opportunities facing the field of exoplanets in the future, the prospect of mapping the surface of a potentially habitable planet is one of the most exciting -- and one of the most difficult.
-Present-day missions including the Transiting Exoplanet Survey Satellite \citep[\TESS; ][]{Ricker2015} aim to discover small terrestrial planets around bright, nearby stars. 
-Once these targets are found, much more detailed observational characterization must follow to evaluate their suitability for harboring life. 
-The discovery of surface features including continents and oceans would be a critical hint towards the habitability of an alien world.
-
-The most straightforward method of observing features on a terrestrial exoplanet would be to directly image the planet at sufficient resolution. 
-However, such an observation would require an effective telescope aperture orders of magnitude larger than currently available as well as extremely advanced coronagraphic optics, making it a far-future goal.
-
-Surface mapping can also be done by observing rotational phase-dependent variations of the planetary signal in precise photometric time series. 
-This is a complex data analysis problem: strong degeneracies are involved when transforming a 1-dimensional time series into a 2-dimensional surface map. 
-Interpretation is also challenging in the face of many potential explanations for a poorly resolved observed feature.
-
-\todo{(Summary of previous mapping work:)}\citep{Knutson2007,Majeau2012,deWit2012}
+Of the many challenges and opportunities facing the field of exoplanets in the future, 
+the prospect of mapping the surface of a potentially habitable planet is one of 
+the most exciting -- and one of the most difficult. 
+Present-day missions including the Transiting Exoplanet Survey Satellite 
+\citep[\TESS; ][]{Ricker2015} aim to discover small terrestrial planets around 
+bright, nearby stars. 
+Once these targets are found, more detailed observational characterization 
+must follow to evaluate their suitability for harboring life. 
+The discovery of surface features such as continents and oceans would be a 
+critical step toward understanding the habitability of an alien world.
+
+The most straightforward method of observing features on a terrestrial exoplanet 
+would be to directly image the planet at sufficient resolution. 
+However, such an observation would require an effective telescope aperture many orders 
+of magnitude larger and equipped with far more advanced coronagraphic optics
+than what we have available today.
+
+Fortunately, surface mapping can also be done indirectly by observing rotational 
+phase-dependent variations of the planetary signal in precise photometric time series. 
+This is a complex data analysis problem: strong degeneracies are involved when 
+transforming a 1-dimensional time series into a 2-dimensional surface map
+\citep{CowanFuentesHaggard2013}. 
+Interpretation is also challenging in the face of many potential explanations 
+for a poorly resolved surface feature. Nevertheless, this technique has
+already proven successful in the mapping of large dipolar features on the surfaces
+of hot giant planets, most notably the hot Jupiter HD189733b
+\citep{Knutson2007,Majeau2012,deWit2012}. More recently, this technique has also
+been applied to the potentially terrestrial planet 55 Cancri e, suggesting
+a large longitudinal offset in its peak surface emission due to either
+lava flows on the surface or strong atmospheric recirculation
+\citep{Demory2016,Demory2016b,Hammond2017}.
 
@@
 
-The \TESS mission promises to deliver thousands of new exoplanets around bright, nearby stars, many of which may be terrestrial worlds potentially suitable for life. 
-In fact, one such world, a planet which we will call Sol d, has already been extensively observed by \TESS.
+The \TESS mission promises to deliver thousands of new exoplanets around bright, 
+nearby stars, many of which may be terrestrial worlds potentially suitable for life. 
+In fact, one such world, a planet which we will call Sol d, has already been 
+extensively observed by \TESS.
 
@@
 (\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
-as a multiplicative term. The model for the flux timeseries
+as a multiplicative term. The model for the flux time series
 in the $n^\mathrm{th}$ postage stamp is therefore
@@
 The problem of inferring a two-dimensional map from a one-dimensional
-timeseries is famously ill-posed given its large null space and many complex
+time series is famously ill-posed given its large null space and many complex
 degeneracies \citep[e.g.,][]{CowanFuentesHaggard2013}. In fact, for a 

### 2019-03-28 tex/ms.tex
edits

--- 2019-03-28 tex/ms.tex
@@
 As with all \TESS time series data products, the time is given in units of \TESS Julian 
-Date (TJD), defined as $\mathrm{BJD} - 2457000$, and the data are delivered in 27-day 
+Date (TJD), defined as $\mathrm{BJD} - 2457000$ \todo{(is this barycentric corrected?)}, and the data are delivered in 27-day 
 parcels corresponding to the varying pointing sectors of \TESS. 
@@
 across the full \TESS field of view and extracted the background flux time 
-series (\textsf{SAP\_BKG}) and corresponding uncertainties
-(\textsf{SAP\_BKG\_ERR}) from each. 
+series from each. 
 Not all postage stamps are equally informative, since the desired signal from 
-Sol d is inhomogenously spread across the \TESS detectors and manifests itself
+Sol d is inhomogenously spread across the \TESS detectors and manifests 
 differently in different regions (see \S\ref{sec:systematics}). 
@@
 behaviors of background across the entire \TESS field of view. 
-To accomplish this, we interpolated all light curves in Sector 1 onto the same time
-grid, masked all cadences with nonzero \textsf{QUALITY} flags and
-cadences during which Sol d was below the edge of the sunshade.
-During the selection step only, we also normalized them to the same min-max range.
-We then computed the median
-flux at each cadence along with an estimate of the variance based on the
-median absolute deviation (MAD) across all light curves.
-For each light curve, we calculated a score $\chi^2$ equal to the sum of the squares of the
-deviation from the median at each of the $N$ cadences, normalized by the variance.
-We removed all light curves with $\chi^2 < N$ from the pool, placing
-them in a separate group. We repeated these steps several times,
-classifying light curves into four groups for Sector 1 and two groups for Sector 2. 
-We found that this
-procedure effectively grouped together light curves with similar features,
-increasing in variation within each group from the first group (most homogeneous) 
-to the last group (most heterogeneous). In practice, we found light curves
-in all but the last group to be dominated by 
-the signal of Sol d, while light
-curves in the last group were dominated by signals other than the
-periodic modulation of the planet. To obtain our final set of light curves, 
-we sorted the light curves in each group by the amplitude
-of the signal and kept the first 25 in each of the first three groups in Sector 1
-and the first 20 in the first group in Sector 2 for a total
-of 75 and 20 light curves, respectively. We then computed an estimate of the
-non-Sol d background flux from the cadences during which the planet was below
-the edge of the sunshade and removed this baseline from the flux.
-Finally, we median-normalized all light curves (as opposed to the min-max
-normalization used for the classification).
-Our final dataset consisted of 912,605 data points in total. 
+To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
+full-on categorization)}
+
+\todo{(masking out epochs without Sol d shine, subtraction of baseline 
+background flux)}
+
+The final data set to be used consists of 75 Sector 1 background lightcurves 
+and 20 Sector 2 background lightcurves corresponding to the epochs at which 
+Sol d signal was clearly registered by \TESS. 
+This is 912,605 data points in total. 
 A representative sample of these signals is shown in Figure~\ref{fig:data}.
@@
 At any given cadence, we rotate Sol d about its spin axis to the correct phase,
-assuming a rotation period of $0.9972696$ day, the sidereal rotation period
-of the planet. We determine the initial rotation
+assuming a planetary rotation period of $0.9972696$ days. We determine the initial rotation
 phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
@@
     \caption{\label{fig:phases}
-             \TESS view of Sol d on every date in Sectors 1
-             and 2 that was included in the regression. Each image is
-             labeled with the corresponding timestamp in TJD. The images
-             shown here correspond to current models of the continental coverage
-             of Sol d, not to the map inferred in this study.
+             Synthetic images showing \TESS's view of Sol d on every date in 
+             Sectors 1 and 2 that was included in the regression. Each image 
+             is labeled with the corresponding timestamp in TJD. 
+             The dayside features shown here correspond to a hypothetical 
+             model of Sol d, not to the map inferred in this study.
              \codelink{EarthView}
@@
 apart, the planet appears to slowly rotate over the course of the observation.
-This is because of the orbit of \TESS, which changes its vantage point relative
+This is due to the orbit of \TESS, which changes its vantage point relative
 to Sol d over the course of its 13 day orbit.
@@
 pixel-level decorrelation \citep[PLD;][]{Deming2015, Luger2016, Luger2018a}
-seeks to address. In PLD, one computes the sum over all light curves at each
+seeks to address. In PLD, one computes the sum over all $N$ light curves at each
 point in time, and uses this quantity to normalize each of the individual
@@
 signal and the systematics signal, this procedure divides out the astrophysical
-signal, producing a basis of vectors that contain \emph{only} functions of the
+signal, producing a basis of $N$ vectors that contain \emph{only} functions of the
 systematics. This now serves as a ``clean'' basis one can then use to fit the 
-data, with minimal risk of fitting out astrophysical signals.
+systematics component of the data, with minimal risk of fitting out astrophysical signals.
 
-We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
+We use PLD to determine a basis sets for each \TESS sector. 
+We then construct a design matrix $\mathbf{B}$ out of this PLD basis. To
 increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
 polynomials in time for each of the two orbits of \TESS in each sector. 
+\todo{(this is confusing - what order of polynomial? 
+is the design matrix shared for LCs from either sector?)}
 The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
@@
 \starry computes phase curves and occultation light curves for bodies whose
-surfaces are expressed as a sum of spherical harmonics. 
+surfaces can be expressed as a sum of spherical harmonics. 
 The algorithm works by first transforming
@@
 However, in the present work, we are interested in \emph{reflected} light, so we must
-account for the illumination by the star, which varies smoothly
-across the dayside of the planet but whose derivative discontinuously changes at the 
+account for the illumination by the star. This illumination varies smoothly
+across the dayside of the planet, but its derivative discontinuously changes at the 
 terminator, beyond which the illumination is zero everywhere. This requires
@@
 As with the systematics model (\S\ref{sec:systematics}), the model
-for the astrophysical signal is \emph{linear}: the signal $\mathbf{s}$ 
+for the astrophysical signal is \emph{linear}. The signal $\mathbf{s}$ 
 is a linear operation on the vector of spherical harmonic coefficients 
@@
 but here we will use it to represent the \emph{albedo} of the planet.
-We choose a maximum spherical harmonic degree $l_{max} = 10$ for our fits,
-noting that increasing $l_{max}$ above this value 
-leads to a quick rise in the amount of ``ringing'' without substantially
-increasing the quality of our fits. Note that $l = 10$ corresponds to
+
+We chose a maximum spherical harmonic degree $l_{max} = 10$ for our fits.
+Increasing $l_{max}$ above this value 
+leads to a sharp rise in the amount of ``ringing'' without substantially
+increasing the quality of the fit. Note that $l = 10$ corresponds to
 a maximum surface resolution on the order of $180^\circ/10 \approx 18^\circ$.
@@
 (\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
-as a multiplicative term. The model for the flux timeseries
+as a multiplicative term to scale from the intrinsic luminance \todo{(is this the right word??)} of Sol d to 
+the flux observed by \TESS. The model for the flux timeseries
 in the $n^\mathrm{th}$ postage stamp is therefore
@@
 for 1000 iterations, well past convergence. Since \tf automatically
-computes and propagates gradient information, this step is fast
-and also finishes in under three minutes on a laptop.
+computes and propagates gradient information, this step is fast, 
+finishing in under three minutes on a laptop.
 
@@
              two purported oceans, which we call the ``Pacific'' and the ``Atlantic.'' 
+	     Black contours correspond to supposed coastlines
+             derived from current state-of-the-art models of the surface geography 
+             of Sol d.             
              }
@@
 variations was less than 10\%; we scaled it to span the range [0, 1]
-for better visualization. Furthermore, although the resolution is on 
+for better visualization. Furthermore, although the maximum resolution of
+the spherical harmonic model is on 
 the order of $18^\circ$, features typically span ${\sim}45^\circ$; this is
@@
              dashed white lines indicate latitudes above/below which the
-             visibility drops below 50\%. Black contours indicate coastlines
-             derived from current state-of-the-art models of the surface geography 
-             of Sol d.
+             visibility drops below 50\%. As in Figure~\ref{fig:map_L2}, coastlines 
+             based on current models from the literature are overplotted as black contours.
              \emph{Bottom:} Approximate cloud coverage map based on corrected
@@
 maximum likelihood albedo map inferred for Sol d weighted by a visibility function.
-The visibiluty function is computed as the average of the product of the 
+The visibility function is computed as the average of the product of the 
 cosine of the illumination angle and the cosine of the angle between the 
@@
 as regions near the southern pole of Sol d, as the observations were taken during
-southern winter) or seldom in view (such as regions near the north pole of the planet,
-which during Sectors 1 and 2 were mostly on the opposite side of Sol d than \TESS).
+southern winter) or seldom in view (such as regions near the northern pole of the planet,
+which during Sectors 1 and 2 were mostly on the opposite side of Sol d from \TESS).
 Because there is little data from these regions, their albedo is prior-dominated
 and tends to fluctuate substantially with small changes to the choices we make
-when fitting the data. Conversely, we find that the large scale features close to
+when fitting the data. On the other hand, we find that the large scale features close to
 the equator of Sol d are mostly insensitive to our choices of prior. In the Figure,
@@
 bands (i.e., inconsistent with a grey spectrum). We then averaged the images
-averaged over the 28 days of data analyzed in this work, smoothed it, 
+averaged over the 28 days of data analyzed in this work, smoothed it \todo{(how?)}, 
 and weighted by the \TESS visibility as in the top panel.
@@
 by different amounts as the planet rotates and as the angle of incident starlight
-moves over the course of the year. This weighting is sufficient to break many
+moves over the course of the planet's year. This weighting is sufficient to break many
 of the degeneracies, which are rooted in the anti-symmetry of many of the spherical
@@
 in this particular problem. In practice, however, it is evident from
-Figure~\ref{fig:map} that degenaricies still abound. While we infer a few of the
+Figure~\ref{fig:map} that degenericies still abound. While we infer a few of the
 dominant features of the cloud map of Sol d, several of them are skewed, 
@@
 South America, and dark regions associated with the three major oceans) persist
-regardless of the choice of prior, their exact shapes and contrast varied
+regardless of the choice of prior, their exact shapes and contrast vary
 significantly under different assumptions.
@@
 slope. This is more costly, but certainly not intractable, and we will
-pursue this in upcoming work.
+pursue this in future work.
 
@@
 and a linear reflectance model) and thus limiting
-the number of knobs we could turn. We also opted to fit for the spectral
-slope of the map rather than use the power spectrum inferred from 
-real imaging data. Moreover, the broad features in the strongly
+the number of knobs we could turn. We also opted to forego any use of 
+real imaging data in our model; for instance, we fit for the spectral
+slope of the map as a free parameter rather than using the true power spectrum 
+of Sol d. Moreover, the broad features in the strongly
 regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
@@
 terminator should therefore contribute a small amount of flux, which we neglect.
-Similarly, we used the timestamps reported in the \tess light curve
-FITS files, which are corrected to the barycenter of the Sol system. Since
-our signal originates from a source that is closer to \tess than the
-barycenter of the system, the timestamps may be wrong by up to 8 minutes,
-the light travel time from \tess to Sol. During 8 minutes, Sol d rotates
-by about $2^\circ$, so there should be a blurring of our inferred map at
-this scale. However, these two effects
-are well below the resolution of our map, so we expect
-them not to introduce significant bias.
+The effect, however, is below the resolution of our inferred map, so we expect
+that it does not introduce significant bias.
 
@@
 us to collect data on the phase curves of such planets, but that
-data will be of signficantly lower quality and poorer time resolution,
+data will be of significantly lower quality and poorer time resolution,
 so the work presented here can be seen as an upper limit on what we may
@@
 
-Alternatively, time-resolved observations in multiple bands could
+Additionally, time-resolved observations in multiple bands could
 also help with this problem. This was discussed in \cite{Cowan2009},

### 2019-03-28 tex/ms.tex

@@
 behaviors of background across the entire \TESS field of view. 
-To accomplish this, we... \todo{(decide whether it's outlier rejection only or 
-full-on categorization)}
-
-\todo{(masking out epochs without Sol d shine, subtraction of baseline 
-background flux)}
-
-The final data set to be used consists of 75 Sector 1 background lightcurves 
-and 20 Sector 2 background lightcurves corresponding to the epochs at which 
-Sol d signal was clearly registered by \TESS. 
-This is 912,605 data points in total. 
+To accomplish this, we interpolated all light curves in Sector 1 onto the same time
+grid, masked all cadences with nonzero \textsf{QUALITY} flags and
+cadences during which Sol d was below the edge of the sunshade.
+During the selection step only, we also normalized them to the same min-max range.
+We then computed the median
+flux at each cadence along with an estimate of the variance based on the
+median absolute deviation (MAD) across all light curves.
+For each light curve, we calculated a score $\chi^2$ equal to the sum of the squares of the
+deviation from the median at each of the $N$ cadences, normalized by the variance.
+We removed all light curves with $\chi^2 < N$ from the pool, placing
+them in a separate group. We repeated these steps several times,
+classifying light curves into four groups for Sector 1 and two groups for Sector 2. 
+We found that this
+procedure effectively grouped together light curves with similar features,
+increasing in variation within each group from the first group (most homogeneous) 
+to the last group (most heterogeneous). In practice, we found light curves
+in all but the last group to be dominated by 
+the signal of Sol d, while light
+curves in the last group were dominated by signals other than the
+periodic modulation of the planet. To obtain our final set of light curves, 
+we sorted the light curves in each group by the amplitude
+of the signal and kept the first 25 in each of the first three groups in Sector 1
+and the first 20 in the first group in Sector 2 for a total
+of 75 and 20 light curves, respectively. We then computed an estimate of the
+non-Sol d background flux from the cadences during which the planet was below
+the edge of the sunshade and removed this baseline from the flux.
+Finally, we median-normalized all light curves (as opposed to the min-max
+normalization used for the classification).
+Our final dataset consisted of 912,605 data points in total. 
 A representative sample of these signals is shown in Figure~\ref{fig:data}.
@@
 (\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
-as a multiplicative term to scale from the intrinsic luminance \todo{(is this the right word??)} of Sol d to 
+as a multiplicative term to scale from the intrinsic luminance 
+\todo{(is this the right word??)} of Sol d to 
 the flux observed by \TESS. The model for the flux timeseries
@@
 terminator should therefore contribute a small amount of flux, which we neglect.
-The effect, however, is below the resolution of our inferred map, so we expect
-that it does not introduce significant bias.
+Similarly, we used the timestamps reported in the \tess light curve
+FITS files, which are corrected to the barycenter of the Sol system. Since
+our signal originates from a source that is closer to \tess than the
+barycenter of the system, the timestamps may be wrong by up to 8 minutes,
+the light travel time from \tess to Sol. During 8 minutes, Sol d rotates
+by about $2^\circ$, so there should be a blurring of our inferred map at
+this scale. However, these two effects
+are well below the resolution of our map, so we expect
+them not to introduce significant bias.
 

### 2019-03-28 tex/ms.tex
more

--- 2019-03-28 tex/ms.tex
@@
 
-\todo{(Discussion of expanding this work to terrestrial planets and/or reflected light:)} \citep{Berdyugina2017,Cowan2009,Cowan2018,Haggard2018,Kawahara2010,Fujii2012,Lustig-Yaeger2018} and others.
-
-\todo{We need to cite \cite{Sagan1993}!}
-
-The \TESS mission promises to deliver thousands of new exoplanets around bright, 
-nearby stars, many of which may be terrestrial worlds potentially suitable for life. 
-In fact, one such world, a planet which we will call Sol d, has already been 
-extensively observed by \TESS.
+However, obtaining a map of a temperate terrestrial exoplanet is still
+beyond the capabilities of current facilities, as both the thermal and 
+reflected light signals from these planets
+are orders of magnitude below current measurement capabilities. Nevertheless,
+much work has been done on the theoretical front on mapping terrestrial
+planets in the habitable zone
+\citep[e.g.,][]{Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
+for a review, see \cite{Cowan2018}.
+
+In this work, we show how we can harness photometric data collected by the \TESS mission
+to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
+orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
+star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
+the habitable zone for follow-up with other missions, it came as a great surprise
+to us that data from the spacecraft could be used not only to detect Sol d but to
+characterize it in detal. This is due primarily to the strong nature of the reflected
+light signal originating from the planet, which 
+due to complex internal optics illuminates the entirety of the \TESS detector 
+during most of Sector 1 and part of Sector 2.
+
+\todo{more}
 
@@
 \todo{(also maybe say something about Cowan approach)}
+
+\todo{We need to cite \cite{Sagan1993}!}
 
@@
 
-We downloaded 
+We downloaded%
 \footnote{\url{https://archive.stsci.edu/missions/tess/models/}}

### 2019-03-28 tex/ms.tex
more

@@
 (\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
-as a multiplicative term to scale from the intrinsic luminance 
-\todo{(is this the right word??)} of Sol d to 
-the flux observed by \TESS. The model for the flux timeseries
+as a multiplicative term to scale the luminosity 
+of Sol d to the flux observed by \TESS. The model for the flux timeseries
 in the $n^\mathrm{th}$ postage stamp is therefore
@@
 bands (i.e., inconsistent with a grey spectrum). We then averaged the images
-averaged over the 28 days of data analyzed in this work, smoothed it \todo{(how?)}, 
-and weighted by the \TESS visibility as in the top panel.
+averaged over the 28 days of data analyzed in this work, smoothed it 
+with a Gaussian filter, and weighted by the \TESS visibility as in the top panel.
 

### 2019-03-28 tex/ms.tex
Jiang citation
stuffs

@@
 to us that data from the spacecraft could be used not only to detect Sol d but to
-characterize it in detal. This is due primarily to the strong nature of the reflected
+characterize it in detail. This is due primarily to the strong nature of the reflected
 light signal originating from the planet, which 
-due to complex internal optics illuminates the entirety of the \TESS detector 
+because of complex internal optics illuminates the entirety of the \TESS detector 
 during most of Sector 1 and part of Sector 2.
-
-\todo{more}
 
@@
 the presence of localized surface features, but their resolving power has been 
-severely limited by the duration of observations \citep{Cowan2009}. 
+severely limited by the cadence and/or duration of observations \citep{Cowan2009,Jiang2018}. 
 \TESS offers precise 2-minute cadence data spanning a wide range of illumination 
@@
 have made the reconstruction of detailed maps more feasible than ever. 
-\todo{(describe how STARRY works - fast analytic computation of spherical harmonics)}
-\todo{(also maybe say something about Cowan approach)}
+\cite{Luger2019} developed a \todo{more more more}
+\cite{Haggard2018}
 

### 2019-03-28 tex/ms.tex
words and labels

@@
 the habitable zone for follow-up with other missions, it came as a great surprise
-to us that data from the spacecraft could be used not only to detect Sol d but to
+to many that data from the spacecraft could be used not only to detect Sol d but to
 characterize it in detail. This is due primarily to the strong nature of the reflected
@@
 
-\todo{A bit more here.}
+We fit Sol d with both static and time-variable albedo maps. 
+\todo{We find...} 
+Future observations with \TESS will yield further information on 
+the time variability of surface features on Sol d.
+
+\todo{(habitability of Sol d, speculation on landing sites)}
+
+The work presented here also serves as a relevant case study for future 
+efforts to characterize terrestrial exoplanets. \todo{(more)}
 

### 2019-03-28 tex/ms.tex
artists conception
tweakz

@@
 
-We use PLD to determine a basis sets for each \TESS sector. 
-We then construct a design matrix $\mathbf{B}$ out of this PLD basis. To
-increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
-polynomials in time for each of the two orbits of \TESS in each sector. 
-\todo{(this is confusing - what order of polynomial? 
-is the design matrix shared for LCs from either sector?)}
+We use PLD to determine a systematics basis set for each \TESS sector, and
+from this basis we construct a separate design matrix $\mathbf{B}$ for each sector. To
+increase the flexibility of the systematics model, we append to $\mathbf{B}$ a basis of
+fifth order orthogonal polynomials in time.
 The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
@@
 
+\begin{figure}[t!]
+    \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/artist.png}
+    \caption{\label{fig:artist}
+             Artist's conception of Sol d.
+             \emph{Credit: Ian Peng-Sue, age 7.}
+             }
+    \end{centering}
+\end{figure}
+
 \section{Conclusions}

### 2019-03-28 tex/ms.tex
made some funnies

--- 2019-03-28 tex/ms.tex
@@
 at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
-significant latitudinal extent, likely tracking oceans. Because of the
+significant latitudinal extent, likely corresponding to oceans. Because of the
 vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
@@
 We fit Sol d with both static and time-variable albedo maps. 
-\todo{We find...} 
-Future observations with \TESS will yield further information on 
-the time variability of surface features on Sol d.
-
-\todo{(habitability of Sol d, speculation on landing sites)}
+We find tentative evidence for variability in Sol d's cloud coverage over 
+the course of Sector 1 observations. 
+Upcoming observations with \TESS will yield further information on 
+the time variability of surface features on Sol d on a variety of timescales.
+
+The likely prevalence of continents, oceans, and complex weather patterns 
+on Sol d make it an extremely promising site for the evolution of life. 
+We strongly advocate for future missions to further investigate this possibility. 
+In particular, Sol d may be a good choice of target for a lander mission. 
+One prime landing site is located at the planetary (latitude, longitude) coordinates 
+($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R.
+Casey) led us to conclude that this would not be a suitable location.}
 
@@
 
-\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
-acknowledge Jonathan Fraine, Dan Foreman-Mackey, David W. Hogg, Ben Montet, and Ben Pope 
-for useful conversations. Crucial parts of this work were carried out at the 
+\acknowledgements{Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
+David W. Hogg, and Ben Pope for useful conversations. 
+Crucial parts of this work were carried out at the 
 TESS Data Workshop, hosted by Space Telescope Science Institute, and the 

### 2019-03-28 tex/ms.tex
Intro is doooone

--- 2019-03-28 tex/ms.tex
@@
 than what we have available today.
-
+%
 Fortunately, surface mapping can also be done indirectly by observing rotational 
@@
 In this work, we show how we can harness photometric data collected by the \TESS mission
-to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
+to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$~m
 orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
-star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
+star \citep{Sagan1993}. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
 the habitable zone for follow-up with other missions, it came as a great surprise
-to many that data from the spacecraft could be used not only to detect Sol d but to
+that data from the spacecraft could be used not only to detect Sol d but to
 characterize it in detail. This is due primarily to the strong nature of the reflected
@@
 the presence of localized surface features, but their resolving power has been 
-severely limited by the cadence and/or duration of observations \citep{Cowan2009,Jiang2018}. 
+limited by the cadence and/or duration of observations \citep{Cowan2009,Jiang2018}. 
 \TESS offers precise 2-minute cadence data spanning a wide range of illumination 
@@
 unprecedented in the history of exoplanet phase mapping. 
-
-Moreover, recent advances in the computational tractability of this data analysis problem 
+%
+Moreover, recent advances on the modeling side 
 have made the reconstruction of detailed maps more feasible than ever. 
-\cite{Luger2019} developed a \todo{more more more}
-\cite{Haggard2018}
-
-\todo{We need to cite \cite{Sagan1993}!}
-
-In this work, we build on this methodological foundation to perform 
-reflected-light mapping of planetary surface features on Sol d. 
-We give an overview of the \TESS data used in \S\ref{sec:data}. 
-In \S\ref{sec:methods}, we describe the methods employed to infer a map 
+\cite{Luger2019} developed an analytic algorithm for generating---and
+inverting---light curves of stars and planets whose surface emission is
+described in terms of spherical harmonics, dubbed \starry. The analyticity of this
+method makes the computation of the model both fast and precise.
+In turn, \cite{Haggard2018} derived similar analytic expressions for the
+analogous case in reflected light, packaged into the 
+\textsf{EARL} code. In this work, we derive similar expressions within
+the \starry framework to perform fast, analytical inversion of the light curve
+of Sol d and thus construct a map of the planet in reflected light.
+
+The paper is organized as follows: we give an overview of the \TESS data used in \S\ref{sec:data},
+and in \S\ref{sec:methods} we describe the methods employed to infer a map 
 from these data, including the adaptation of the \starry algorithm to reflection 
@@
 We present results in \S\ref{sec:results} and make a comparison of these 
-findings to state-of-the-art terrestrial planet maps in 
+findings to other state-of-the-art maps of Sol d in 
 \S\ref{sec:discussion}. 
@@
 
+\todo{Make sure to reference Figure~\ref{fig:artist} here.}
+
 We have used \TESS photometry to

### 2019-03-28 tex/ms.tex
typos

@@
 
-The \TESS pipeline produces processed lightcurves for all short-cadence targets. 
+The \TESS pipeline produces processed light curves for all short-cadence targets. 
 Part of this processing is the determination of the localized background flux 
@@
 For each of the two sectors considered, we downloaded a random subsample of 
-1,000 short-cadence lightcurve files corresponding to postage stamps located 
+1,000 short-cadence light curve files corresponding to postage stamps located 
 across the full \TESS field of view and extracted the background flux time 
@@
 Not all postage stamps are equally informative, since the desired signal from 
-Sol d is inhomogenously spread across the \TESS detectors and manifests itself
+Sol d is inhomogeneously spread across the \TESS detectors and manifests itself
 differently in different regions (see \S\ref{sec:systematics}). 
 We down-selected our pool of 1,000 targets to 75 maximally useful background 
-lightcurves from Sector 1 and 20 from Sector 2. 
-This down-selection was done with several criteria in mind: each lightcurve 
+light curves from Sector 1 and 20 from Sector 2. 
+This down-selection was done with several criteria in mind: each light curve 
 should contain a significant signal from Sol d; they should be representative 
@@
 While the astrophysical signal that we wish to analyze is present in all 
-extracted lightcurves, its strength is modulated by time-variable systematics 
+extracted light curves, its strength is modulated by time-variable systematics 
 that are correlated but not identical across all postage stamps, since the
@@
 as a multiplicative term to scale the luminosity 
-of Sol d to the flux observed by \TESS. The model for the flux timeseries
+of Sol d to the flux observed by \TESS. The model for the flux time series
 in the $n^\mathrm{th}$ postage stamp is therefore
@@
 in this particular problem. In practice, however, it is evident from
-Figure~\ref{fig:map} that degenericies still abound. While we infer a few of the
+Figure~\ref{fig:map} that degeneracies still abound. While we infer a few of the
 dominant features of the cloud map of Sol d, several of them are skewed, 

### 2019-03-28 tex/ms.tex
integrated artist figure

--- 2019-03-28 tex/ms.tex
@@
 
+\section{Conclusions}
+\label{sec:conclusions}
+
+We have used \TESS photometry to
+produce a global map of Sol d, a terrestrial planet in the habitable
+zone of a G2 main-sequence star. We adapted the \starry code to 
+generate (and invert) light curves in reflected light, coupling it
+to a variation of pixel level decorrelation to model the systematics
+in the \TESS detector.
+
+We detect three large scale bright regions near
+the equator of the planet, associated with persistent cloud structures
+at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
+likely track continents. Pronounced dark features are identified
+at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
+significant latitudinal extent, likely corresponding to oceans. Because of the
+vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
+high latitudes on the planet, although this may change with upcoming
+sectors.
+
+We fit Sol d with both static and time-variable albedo maps. 
+We find tentative evidence for variability in Sol d's cloud coverage over 
+the course of Sector 1 observations. 
+Upcoming observations with \TESS will yield further information on 
+the time variability of surface features on Sol d on a variety of timescales.
+
 \begin{figure}[t!]
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
-
-\todo{Make sure to reference Figure~\ref{fig:artist} here.}
-
-We have used \TESS photometry to
-produce a global map of Sol d, a terrestrial planet in the habitable
-zone of a G2 main-sequence star. We adapted the \starry code to 
-generate (and invert) light curves in reflected light, coupling it
-to a variation of pixel level decorrelation to model the systematics
-in the \TESS detector.
-
-We detect three large scale bright regions near
-the equator of the planet, associated with persistent cloud structures
-at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
-likely track continents. Pronounced dark features are identified
-at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
-significant latitudinal extent, likely corresponding to oceans. Because of the
-vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
-high latitudes on the planet, although this may change with upcoming
-sectors.
-
-We fit Sol d with both static and time-variable albedo maps. 
-We find tentative evidence for variability in Sol d's cloud coverage over 
-the course of Sector 1 observations. 
-Upcoming observations with \TESS will yield further information on 
-the time variability of surface features on Sol d on a variety of timescales.
+To summarize, we have robustly detected surface features from \TESS 
+light curves of Sol d. While the resolution of the map we obtain is limited, 
+it is clear that surface features including low-albedo oceanic regions and 
+high-albedo cloud banks or land masses are present on this terrestrial 
+world. An artist's impression of the planet is shown in Figure~\ref{fig:artist}. 
+While somewhat fanciful and rather far-fetched, this artistic interpretation 
+is nevertheless broadly consistent with the data.
 
@@
 
+\newpage
 % Bibliography

### 2019-03-28 tex/ms.tex
changed roland's initial
misc

@@
 %
-\author{Roland K. Vanderspek}
+\author{Roland Vanderspek}
 \affil{Kavli Institute for Astrophysics and Space Research, Massachusetts 
@@
 At any given cadence, we rotate Sol d about its spin axis to the correct phase,
-assuming a planetary rotation period of $0.9972696$ days. We determine the initial rotation
+assuming a planetary rotation period of $0.9972696$ days and an obliquity
+of $23.437^\circ$. We determine the initial rotation
 phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
@@
              derived from current state-of-the-art models of the surface geography 
-             of Sol d.             
+             of Sol d. \codelink{earthshine_S1_S2}      
              }
@@
 data will be of significantly lower quality and poorer time resolution,
-so the work presented here can be seen as an upper limit on what we may
+and we will not know the planet's rotation period or obliquity ahead of time.
+The work presented here can therefore be seen as an upper limit on what we may
 be able to infer about exoplanets in the habitable zone with
@@
 axis of rotation should precess---may help to disambiguate between
-clouds, oceans, and continents. We intend to perform this analysis
+clouds, oceans, and continents. Although the signal of Sol d 
+mostly disappears from the \tess detector after Sector 2, it is
+expected to return in Sectors 14 and 15 when the planet will again
+be above the edge of the sunshade.
+We intend to perform this analysis
 in upcoming work once data from future \TESS sectors becomes available.
@@
 One prime landing site is located at the planetary (latitude, longitude) coordinates 
-($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R.
+(\href{https://www.google.com/maps/place/Roswell,+NM/@36.2909732,-94.0798131,3.96z/data=!4m5!3m4!1s0x86e2651365aced55:0xe41b0be474cfd77e!8m2!3d33.3942655!4d-104.5230242}{$33.3943^\circ$ N, $104.5230^\circ$ W}).%
+\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R.
 Casey) led us to conclude that this would not be a suitable location.}

### 2019-03-28 tex/ms.tex
more conclusion

--- 2019-03-28 tex/ms.tex
@@
 In this work, we show how we can harness photometric data collected by the \TESS mission
-to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$~m
+to construct a map of Sol d, a rocky planet âwith a radius of $6.4\times 10^6$~m
 orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
@@
 One prime landing site is located at the planetary (latitude, longitude) coordinates 
-($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R.
-Casey) led us to conclude that this would not be a suitable location.}
+($33.3943^\circ$ N, $104.5230^\circ$ W).\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (Andrew R.
+Casey, personal communication) led us to conclude that this would not be a suitable location.}
 
 The work presented here also serves as a relevant case study for future 
-efforts to characterize terrestrial exoplanets. \todo{(more)}
+efforts to characterize terrestrial exoplanets. While the circumstances of \TESS's 
+observations of Sol d will not be replicated exactly for other planets, similar 
+rotationally-modulated phase curves of reflected light may be feasible in the future. 
+We show that a fast, analytic linear model can be successfully applied to such data. 
+We also underscore the importance of high cadence \emph{and} long duration for 
+these observations, and we additionally advocate for multi-wavelength coverage to 
+help disentangle the photometric signatures of continents and persistent cloud features.
 

### 2019-03-28 tex/ms.tex

--- 2019-03-28 tex/ms.tex
@@
 (\href{https://www.google.com/maps/place/Roswell,+NM/@36.2909732,-94.0798131,3.96z/data=!4m5!3m4!1s0x86e2651365aced55:0xe41b0be474cfd77e!8m2!3d33.3942655!4d-104.5230242}{$33.3943^\circ$ N, $104.5230^\circ$ W}).%
-\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (private communication, Andrew R.
-Casey) led us to conclude that this would not be a suitable location.}
+\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (Andrew R.
+Casey, personal communication) led us to conclude that this would not be a suitable location.}
 
 The work presented here also serves as a relevant case study for future 
-efforts to characterize terrestrial exoplanets. \todo{(more)}
+efforts to characterize terrestrial exoplanets. While the circumstances of \TESS's 
+observations of Sol d will not be replicated exactly for other planets, similar 
+rotationally-modulated phase curves of reflected light may be feasible in the future. 
+We show that a fast, analytic linear model can be successfully applied to such data. 
+We also underscore the importance of high cadence \emph{and} long duration for 
+these observations, and we advocate for multi-wavelength coverage to 
+help disentangle the photometric signatures of continents and persistent cloud features.
 

### 2019-03-28 tex/ms.tex
minor fixes

@@
 behaviors of background across the entire \TESS field of view. 
-To accomplish this, we interpolated all light curves in Sector 1 onto the same time
-grid, masked all cadences with nonzero \textsf{QUALITY} flags and
+To accomplish this, we applied a categorization and outlier rejection scheme to the ensemble of light curves.
+We interpolated all light curves in Sector 1 onto the same time
+grid, masked all cadences with nonzero \textsf{QUALITY} flags, and masked
 cadences during which Sol d was below the edge of the sunshade.
-During the selection step only, we also normalized them to the same min-max range.
-We then computed the median
+During this selection step only, we also normalized the light curves to the same min-max range.
+We computed the median
 flux at each cadence along with an estimate of the variance based on the

### 2019-03-28 tex/ms.tex
nitpicking

--- 2019-03-28 tex/ms.tex
@@
 (\textsf{SAP\_BKG\_ERR}) from each. 
+We then interpolated all light curves in a given sector onto the same time
+grid, masked all cadences with nonzero \textsf{QUALITY} flags, and masked
+cadences during which Sol d was below the edge of the sunshade.
+
 Not all postage stamps are equally informative, since the desired signal from 
@@
 behaviors of background across the entire \TESS field of view. 
-To accomplish this, we interpolated all light curves in Sector 1 onto the same time
-grid, masked all cadences with nonzero \textsf{QUALITY} flags and
-cadences during which Sol d was below the edge of the sunshade.
-During the selection step only, we also normalized them to the same min-max range.
+To accomplish this, we applied a categorization and outlier rejection scheme to the ensemble of light curves.
+During this selection step only, we normalized the light curves to the same min-max range.
 We then computed the median

### 2019-03-28 tex/ms.tex
fixed typo

@@
 be determined.
+\href{https://github.com/rodluger/earthshine}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 In this work, we show how we can harness photometric data collected by the \TESS mission
-to construct a map of Sol d, a rocky planet âwith a radius of $6.4\times 10^6$~m
+to construct a map of Sol d, a rocky planet with a radius of $6.4\times 10^6$~m
 orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
@@
 method makes the computation of the model both fast and precise.
-In turn, \cite{Haggard2018} derived similar analytic expressions for the
+In turn, \cite{Haggard2018} derived analytic expressions for the
 analogous case in reflected light, packaged into the 
@@
 Finally, we conclude with a summary of our major findings in \S\ref{sec:conclusions}.
+The code used to generate all the figures in this paper is open source
+and available on GitHub%
+\footnote{\url{https://github.com/rodluger/earthshine}}. Clickable icons
+\href{https://github.com/rodluger/earthshine}{\color{linkcolor}\faFileCodeO}
+next to each figure caption 
+link to the source code used to generate them.
 
@@
 
-The \TESS pipeline produces processed light curves for all short-cadence targets. 
+The \TESS pipeline produces processed light curves for all short-cadence (2 minute) targets. 
 Part of this processing is the determination of the localized background flux 
@@
 
-\section{Methods}
-\label{sec:methods}
-
-\subsection{Orbital Modeling}
-\label{sec:orbit}
-
+\pagebreak
+
+\section{Methods}%
+\label{sec:methods}%
+%
+\subsection{Orbital Modeling}%
+\label{sec:orbit}%
+%
 We downloaded%
@@
 increase the flexibility of the systematics model, we append to $\mathbf{B}$ a basis of
-fifth order orthogonal polynomials in time.
+fifth order orthogonal polynomials in time for each of the two orbits in each sector.
 The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
@@
 The total number of data points is $912,605$, so overfitting is not particularly
-concerning; nevertheless, we impose an L2 prior on the weights with
-standard deviation $\sigma_w = 0.05$ (see \S\ref{sec:model}).
+concerning; nevertheless, we impose an L2 prior on the weights to minimize this risk
+(see \S\ref{sec:model}).
 
@@
 used as a starting point for the second step (see below), the choice of prior 
-at this stage has minimal impact on our results.
+at this stage does not significantly impact on our results.
 
 In general, we find that the iterative scheme converges within about 50 
-iterations, taking about three minutes on a laptop computer. However, since it 
+iterations, taking about two minutes on a laptop computer. However, since it 
 is strongly regularized, the model significantly
@@
 computes and propagates gradient information, this step is fast, 
-finishing in under three minutes on a laptop.
+finishing in under one minute on a laptop.
 
@@
 additional temporal variations---most likely due to cloud movement---cause aperiodic
-changes to the reflectivity of the surface. We revisit this point in \S\ref{sec:discussion}.
+changes in the reflectivity of the surface. We revisit this point in \S\ref{sec:discussion}.
 
@@
 barycenter of the system, the timestamps may be wrong by up to 8 minutes,
-the light travel time from \tess to Sol. During 8 minutes, Sol d rotates
+the light travel time from \tess to Sol. Over the course of 8 minutes, Sol d rotates
 by about $2^\circ$, so there should be a blurring of our inferred map at
@@
     \begin{centering}
-    \includegraphics[width=0.5\linewidth]{figures/artist.png}
+    \includegraphics[width=0.4\linewidth]{figures/artist.png}
     \caption{\label{fig:artist}
@@
 
-\acknowledgements{Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
+\vspace{0.5in}
+
+\acknowledgements{%
+Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for 
+Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
 David W. Hogg, and Ben Pope for useful conversations. 

### 2019-04-03 tex/ms.tex
missed an acknowledgement
first pass at changes

@@
 % Title
-\title{\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: 
-       Detection of Clouds, Oceans, and Continents}
-%\title{Detection of Continents on a Habitable-Zone Terrestrial Planet with \TESS}
+\title{Observing Earth as an Exoplanet with \TESS: Photometric Mapping of Surface Features in Reflected Light}
 
@@
 \begin{abstract}
+\todo{(TO BE CHANGED:)}
 To date, a handful of exoplanets have been photometrically mapped using phase-modulated 
@@
 
-\keywords{methods: data analysis, techniques: photometric, planets and satellites: 
-          oceans, planets and satellites: surfaces, planets and satellites: 
-          terrestrial planets}
+\keywords{methods: data analysis, techniques: photometric, planets and satellites: surfaces, 
+		Earth}
 
@@
 
+\todo{(THIS PARAGRAPH TO BE CHANGED:)} 
 In this work, we show how we can harness photometric data collected by the \TESS mission
-to construct a map of Sol d, a rocky planet with a radius of $6.4\times 10^6$~m
+to construct a map of Earth, a rocky planet with a radius of $6.4\times 10^6$~m
 orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
@@
 the habitable zone for follow-up with other missions, it came as a great surprise
-that data from the spacecraft could be used not only to detect Sol d but to
+that data from the spacecraft could be used not only to detect Earth but to
 characterize it in detail. This is due primarily to the strong nature of the reflected
@@
 
-Previous attempts to map Sol d from the exoplanet community have suggested 
+Previous attempts to map Earth from the exoplanet community have suggested 
 the presence of localized surface features, but their resolving power has been 
@@
 the \starry framework to perform fast, analytical inversion of the light curve
-of Sol d and thus construct a map of the planet in reflected light.
+of Earth and thus construct a map of the planet in reflected light.
 
@@
 priors used. 
-We present results in \S\ref{sec:results} and make a comparison of these 
-findings to other state-of-the-art maps of Sol d in 
-\S\ref{sec:discussion}. 
+We present results in \S\ref{sec:results}. 
+In \S\ref{sec:discussion}, we assess the accuracy of our map and discuss the relevance 
+of this analysis to future attempts at mapping terrestrial exoplanets.
 Finally, we conclude with a summary of our major findings in \S\ref{sec:conclusions}.
@@
 grid, masked all cadences with nonzero \textsf{QUALITY} flags, and masked
-cadences during which Sol d was below the edge of the sunshade.
+cadences during which Earth was below the edge of the sunshade.
 
 Not all postage stamps are equally informative, since the desired signal from 
-Sol d is inhomogeneously spread across the \TESS detectors and manifests itself
+Earth is inhomogeneously spread across the \TESS detectors and manifests itself
 differently in different regions (see \S\ref{sec:systematics}). 
@@
 This down-selection was done with several criteria in mind: each light curve 
-should contain a significant signal from Sol d; they should be representative 
+should contain a significant signal from Earth; they should be representative 
 of the general background flux modulation seen across the \TESS cameras, rather 
@@
 in all but the last group to be dominated by 
-the signal of Sol d, while light
+the signal of Earth, while light
 curves in the last group were dominated by signals other than the
@@
 of 75 and 20 light curves, respectively. We then computed an estimate of the
-non-Sol d background flux from the cadences during which the planet was below
+non-Earth background flux from the cadences during which the planet was below
 the edge of the sunshade and removed this baseline from the flux.
@@
              Normalized background flux in each of ten postage stamps
-             for each of Sectors 1 and 2. Cadences where Sol d was
+             for each of Sectors 1 and 2. Cadences where Earth was
              below or very close to the edge of the sunshade were masked.
@@
 ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
-the relative positions of Sol, Sol d, and \TESS for every cadence
+the relative positions of Sol, Earth, and \TESS for every cadence
 in our dataset in the J2000 equatorial reference frame. In this right-handed
-coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
+coordinate frame, Earth is centered at the origin, the $y$ axis points along the 
 planet's spin axis, and the $x$ axis points toward the vernal equinox. We
@@
 
-At any given cadence, we rotate Sol d about its spin axis to the correct phase,
+At any given cadence, we rotate Earth about its spin axis to the correct phase,
 assuming a planetary rotation period of $0.9972696$ days and an obliquity
 of $23.437^\circ$. We determine the initial rotation
-phase of Sol d by computing the Sol d Rotation Angle (ERA), given by \citep{Urban2013}
+phase of Earth by computing the Earth Rotation Angle (ERA), given by \citep{Urban2013}
 %
@@
 Finally, we rotate the frame to align
-\TESS with the $+z$ axis, with the spin vector of Sol d along the $y-z$ plane.
+\TESS with the $+z$ axis, with the spin vector of Earth along the $y-z$ plane.
 We verified our rotations by comparing our results on several days to the
@@
     \caption{\label{fig:phases}
-             Synthetic images showing \TESS's view of Sol d on every date in 
+             Synthetic images showing \TESS's view of Earth on every date in 
              Sectors 1 and 2 that was included in the regression. Each image 
              is labeled with the corresponding timestamp in TJD. 
-             The dayside features shown here correspond to a hypothetical 
-             model of Sol d, not to the map inferred in this study.
+             The dayside features shown here correspond to a 
+             model of Earth, not to the map inferred in this study.
              \codelink{EarthView}
@@
 
-Figure~\ref{fig:phases} shows the view \TESS has of Sol d on each of the dates
+Figure~\ref{fig:phases} shows the view \TESS has of Earth on each of the dates
 in our dataset; these images were produced by applying the sequences of rotations
 described above. The planet is illuminated by Sol assuming it is a point source,
-and the night side is shaded black. The map of Sol d shown in this figure is 
+and the night side is shaded black. The map of Earth shown in this figure is 
 based on current models of the actual distribution of continents on the planet.
@@
 This is due to the orbit of \TESS, which changes its vantage point relative
-to Sol d over the course of its 13 day orbit.
+to Earth over the course of its 13 day orbit.
 
@@
 that are correlated but not identical across all postage stamps, since the
-illumination of the CCD by Sol d is strongly inhomogeneous. A physical
+illumination of the CCD by Earth is strongly inhomogeneous. A physical
 model of the reflections and scattering that gives rise to the
-signal of Sol d on the \TESS detector is beyond the scope of this work. Instead,
+signal of Earth on the \TESS detector is beyond the scope of this work. Instead,
 we treat this as a de-trending problem, where the signal we wish to fit is
@@
 We model the astrophysical component of the signal---the rotational modulation
-of Sol d in reflected light---using the \starry code package \citep{Luger2019}.
+of Earth in reflected light---using the \starry code package \citep{Luger2019}.
 \starry computes phase curves and occultation light curves for bodies whose
@@
 sharp rise at the beginning of each orbit in Sector 1 is due to the changing
-vantage point of \TESS as Sol d transitions from a thin crescent to full phase.
+vantage point of \TESS as Earth transitions from a thin crescent to full phase.
 
@@
 systematics model $\mathbf{p}_n = \mathbf{B}\mathbf{w}_n$ (different for each target) and
-the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we happen
-to know the exact distance $\mathbf{r}$ between \TESS and Sol d at all times
+the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we 
+know the exact distance $\mathbf{r}$ between \TESS and the Earth at all times
 (\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
 as a multiplicative term to scale the luminosity 
-of Sol d to the flux observed by \TESS. The model for the flux time series
+of Earth to the flux observed by \TESS. The model for the flux time series
 in the $n^\mathrm{th}$ postage stamp is therefore
@@
     \caption{\label{fig:map_L2}
-             Maximum likelihood map of Sol d obtained during the first
+             Maximum likelihood map of Earth obtained during the first
              stage of our optimization procedure, in which an iterative
@@
              subject to very conservative regularization. Despite the low
-             resolution of this map, the bright features appear to track
-             land masses which for specificity we will refer to as (from left to right)
-             ``South America,'' ``Africa,'' and ``Asia.''
-             The two dark features are associated with the planet's
-             two purported oceans, which we call the ``Pacific'' and the ``Atlantic.'' 
-	          Black contours correspond to supposed coastlines
-             derived from current state-of-the-art models of the surface geography 
-             of Sol d. \codelink{earthshine_S1_S2}      
+             resolution of this map, bright features appear at the 
+             expected locations of South America, Africa, and Asia, 
+             and two dark features appear at Earth's
+             two major oceans, the Pacific and the Atlantic. 
+	          Black contours correspond to known coastlines. 
+	          \codelink{earthshine_S1_S2}      
              }
@@
 wraps around the antimeridian). Overplotted on the inferred map are
-coastal outlines corresponding to our current best understanding of 
-the geography of Sol d. One can see that the three bright regions roughly
-track, from left to right, continents we shall refer to as ``South America,''
-``Africa,'' and ``Asia,'' in keeping with the literature. The dark regions
-are associated with the two major purported oceans on the planet, the
-``Pacific'' (centered at longitude $\pm180^\circ$) and ``Atlantic''
+coastal outlines of Earth's continents. One can see that the three bright regions roughly
+track, from left to right, the continents  of South America,
+Africa, and Asia. The dark regions
+appear at the locations of Earth's two major oceans, the
+Pacific (centered at longitude $\pm180^\circ$) and the Atlantic
 (centered at longitude $\-45^\circ$).
@@
 between about 0.1 and 10 days, with a significant dip at 1.00 day. This
-suggests our model is fitting the rotational variability of Sol d quite well, but
+suggests our model is fitting the rotational variability of Earth quite well, but
 additional temporal variations---most likely due to cloud movement---cause aperiodic
@@
              \emph{Top:} The maximum likelihood model for the surface albedo
-             of Sol d, weighted by the visibility across Sectors 1 and 2. The
+             of Earth, weighted by the visibility across Sectors 1 and 2. The
              dashed white lines indicate latitudes above/below which the
              visibility drops below 50\%. As in Figure~\ref{fig:map_L2}, coastlines 
-             based on current models from the literature are overplotted as black contours.
+             are overplotted as black contours.
              \emph{Bottom:} Approximate cloud coverage map based on corrected
@@
 In the top panel of Figure~\ref{fig:map} we show the final,
-maximum likelihood albedo map inferred for Sol d weighted by a visibility function.
+maximum likelihood albedo map inferred for Earth weighted by a visibility function.
 The visibility function is computed as the average of the product of the 
 cosine of the illumination angle and the cosine of the angle between the 
-observer vector and the vector normal to the surface of Sol d. This normalization
+observer vector and the vector normal to the surface of Earth. This normalization
 has the effect of downweighting regions that are either seldom illuminated (such
-as regions near the southern pole of Sol d, as the observations were taken during
+as regions near the southern pole of Earth, as the observations were taken during
 southern winter) or seldom in view (such as regions near the northern pole of the planet,
-which during Sectors 1 and 2 were mostly on the opposite side of Sol d from \TESS).
+which during Sectors 1 and 2 were mostly on the opposite side of the Earth from \TESS).
 Because there is little data from these regions, their albedo is prior-dominated
@@
 when fitting the data. On the other hand, we find that the large scale features close to
-the equator of Sol d are mostly insensitive to our choices of prior. In the Figure,
+the equator are mostly insensitive to our choices of prior. In the Figure,
 we use dashed lines to delineate the regions whose average visibility is larger
@@
 The bottom panel of Figure~\ref{fig:map} shows an approximate average
-cloud cover map of Sol d based on imagery taken by the
+cloud cover map of Earth based on imagery taken by the
 Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
@@
 While the two panels display fundamentally different quantities---an albedo
-and a cloudiness factor---we expect that the signal of Sol d in the \TESS
+and a cloudiness factor---we expect that the signal of Earth in the \TESS
 bandpass is dominated by cloud reflectivity, as water clouds have an albedo
@@
 Fortunately, there are two aspects of the problem at hand that facilitate
-this (seemingly impossible) inversion. First, the surface of Sol d is
+this (seemingly impossible) inversion. First, the surface of Earth is
 not uniformly illuminated; instead, different parts of the surface are weighted
@@
 the visible lune of the planet strictly remain in the null space. Second, 
-the changing vantage point of \TESS relative to Sol d (and our exact knowledge of it)
+the changing vantage point of \TESS relative to Earth (and our exact knowledge of it)
 breaks degeneracies that are viewpoint-dependent. In particular, the motion of
 \TESS changes the position and shape of the terminator on the projected disk
-of Sol d, enhancing the effect discussed above.
+of Earth, enhancing the effect discussed above.
 
@@
 Figure~\ref{fig:map} that degeneracies still abound. While we infer a few of the
-dominant features of the cloud map of Sol d, several of them are skewed, 
+dominant features of the cloud map of Earth, several of them are skewed, 
 shifted, or entirely out of place. This is the case, for instance, with
@@
 our adopted model. While the measurement errors on our data points are
-quite small---since the signal of Sol d is both quite strong and independently
+quite small---since the signal of Earth is both quite strong and independently
 measured at 95 different positions on the detector---our lack of understanding
@@
 We are therefore somewhat limited in our ability to infer in particular the
-latitudinal position of features. Observations of Sol d in upcoming
-sectors may contain longer segments in which Sol d is seen in crescent,
+latitudinal position of features. Observations of Earth in upcoming
+sectors may contain longer segments in which Earth is seen in crescent,
 which should help mitigate these degeneracies.
@@
 slope of the map as a free parameter rather than using the true power spectrum 
-of Sol d. Moreover, the broad features in the strongly
+of Earth. Moreover, the broad features in the strongly
 regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
@@
 systematics model is strictly multiplicative. Although we subtracted
-an estimate of the baseline non-Sol d background flux from each target
+an estimate of the baseline non-Earth background flux from each target
 (measured from the mid-sector portions of the light curve where the
@@
 that this constant baseline was the \emph{only} source of additive
-noise. We know this to be strictly untrue, as Sol d is known to
-have a companion (Sol d I), a moon about one-third the diameter of 
-Sol d, whose reflected light should cause periodic modulations
-in the background flux of \TESS pixels. Because of its small size and
+noise. We know this to be strictly untrue, as reflected light from the Moon 
+should also cause periodic modulations
+in the background flux of \TESS pixels. Because of the Moon's small size and
 very low ($\sim 0.1$) albedo, we chose to ignore its effect, but it
 is likely to contaminate our signal at certain points in the orbit
-where \TESS is closer to Sol d I than to Sol d. While this will
+where \TESS is closer to the Moon than to Earth. While this will
 likely bias the \starry model at those times, the effect is particularly
@@
 signals with varying (additive) background levels. In principle, one
-could model the reflectance variability of Sol d I in the same way as
+could model the reflectance variability of the Moon in the same way as
 we did here, but since the optics are not well understood, this 
@@
 
-We also ignored the finite angular size of Sol at Sol d (about $0.5^\circ$),
+We also ignored the finite angular size of the Sun at Earth (about $0.5^\circ$),
 treating it instead as a point source. Regions immediately nightward of the 
@@
 barycenter of the system, the timestamps may be wrong by up to 8 minutes,
-the light travel time from \tess to Sol. Over the course of 8 minutes, Sol d rotates
+the light travel time from \tess to the Sun. Over the course of 8 minutes, Earth rotates
 by about $2^\circ$, so there should be a blurring of our inferred map at
@@
 which one may \emph{a priori} expect on a rapidly rotating planet such as 
-Sol d. The bottom panel of Figure~\ref{fig:map} shows such banded structure
+Earth. The bottom panel of Figure~\ref{fig:map} shows such banded structure
 at the equator and at mid-latitudes due to the combined effects of 
@@
 Finally, and perhaps more importantly, our model assumed a \emph{static}
-map for the surface of Sol d. We also know this to be incorrect, since
+map for the surface of Earth. We also know this to be incorrect, since
 clouds form and move on timescales of hours to days. We discuss this in
@@
 the fact that rotational variability is not the sole source of the
-signal of Sol d: additionally, there is temporal variation in the 
+signal of Earth: additionally, there is temporal variation in the 
 albedo of certain parts of the map, most probably due to cloud movement.
@@
 timescales, a more detailed investigation is warranted to say anything
-meaningful about the dynamics of clouds on Sol d.
+meaningful about the dynamics of clouds on Earth.
 
@@
 (without the continent outlines),
-an inhabitant of Sol d may be hard-pressed to identify that
+an inhabitant of Earth may be hard-pressed to identify that
 as a map of their home planet. This is in part due to the biases
 in our optimization, which we discussed above, but also due to the 
-simple fact that the reflectance of Sol d is dominated---by far---by 
-time-variable clouds. While stationary cloud features on Sol d are
+simple fact that the reflectance of Earth is dominated---by far---by 
+time-variable clouds. While stationary cloud features on Earth are
 typically associated with continents (the most pronounced cloud features
@@
 spanning two months in total. Observations taken throughout an entire
-year on Sol d---during which time cloud patterns should change with the
+year on Earth---during which time cloud patterns should change with the
 seasons and the angle between the day/night terminator and the 
 axis of rotation should precess---may help to disambiguate between
-clouds, oceans, and continents. Although the signal of Sol d 
+clouds, oceans, and continents. Although the signal of Earth 
 mostly disappears from the \tess detector after Sector 2, it is
@@
 We have used \TESS photometry to
-produce a global map of Sol d, a terrestrial planet in the habitable
-zone of a G2 main-sequence star. We adapted the \starry code to 
+produce a global map of the Earth, treating it as an exoplanet with unknown
+surface features. We adapted the \starry code to 
 generate (and invert) light curves in reflected light, coupling it
@@
 
-We fit Sol d with both static and time-variable albedo maps. 
-We find tentative evidence for variability in Sol d's cloud coverage over 
+We fit Earth with both static and time-variable albedo maps. 
+We find tentative evidence for variability in Earth's cloud coverage over 
 the course of Sector 1 observations. 
 Upcoming observations with \TESS will yield further information on 
-the time variability of surface features on Sol d on a variety of timescales.
-
-\begin{figure}[t!]
-    \begin{centering}
-    \includegraphics[width=0.4\linewidth]{figures/artist.png}
-    \caption{\label{fig:artist}
-             Artist's conception of Sol d.
-             \emph{Credit: Ian Peng-Sue, age 7.}
-             }
-    \end{centering}
-\end{figure}
+the time variability of surface features on Earth on a variety of timescales.
 
 To summarize, we have robustly detected surface features from \TESS 
-light curves of Sol d. While the resolution of the map we obtain is limited, 
-it is clear that surface features including low-albedo oceanic regions and 
-high-albedo cloud banks or land masses are present on this terrestrial 
-world. An artist's impression of the planet is shown in Figure~\ref{fig:artist}. 
-While somewhat fanciful and rather far-fetched, this artistic interpretation 
-is nevertheless broadly consistent with the data.
-
-The likely prevalence of continents, oceans, and complex weather patterns 
-on Sol d make it an extremely promising site for the evolution of life. 
-We strongly advocate for future missions to further investigate this possibility. 
-In particular, Sol d may be a good choice of target for a lander mission. 
-One prime landing site is located at the planetary (latitude, longitude) coordinates 
-(\href{https://www.google.com/maps/place/Roswell,+NM/@36.2909732,-94.0798131,3.96z/data=!4m5!3m4!1s0x86e2651365aced55:0xe41b0be474cfd77e!8m2!3d33.3942655!4d-104.5230242}{$33.3943^\circ$ N, $104.5230^\circ$ W}).%
-\footnote{We considered the alternative landing site of southern Oceania, but rumors of murderous native fauna including the fearsome ``drop bear'' (Andrew R.
-Casey, personal communication) led us to conclude that this would not be a suitable location.}
-
-The work presented here also serves as a relevant case study for future 
+light curves of Earth. While the resolution of the map we obtain is limited, 
+we do unambiguously detect surface features including low-albedo oceanic regions and 
+high-albedo cloud banks or land masses.
+
+The work presented here serves as a relevant case study for future 
 efforts to characterize terrestrial exoplanets. While the circumstances of \TESS's 
-observations of Sol d will not be replicated exactly for other planets, similar 
+observations of Earth will not be replicated exactly for other planets, similar 
 rotationally-modulated phase curves of reflected light may be feasible in the future. 
@@
 
-In conclusion, we have demonstrated that \TESS is an effective addition to NASA's fleet of weather satellites.
-
 \vspace{0.5in}
@@
 \acknowledgements{%
-Our heartfelt thanks go to Ian Peng-Sue and his agent Stephanie Tonnesen for 
-Figure~\ref{fig:artist}. We also gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
-David W. Hogg, and Ben Pope for useful conversations. 
+We gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
+David W. Hogg, Ben Montet, and Ben Pope for useful conversations. 
 Crucial parts of this work were carried out at the 

### 2019-04-03 earthshine/__init__.py
streamlined the notebooks

@@ -1,2 +1,77 @@
 from .model import design_matrix, tess_earth_vector, visibility, smooth
 from .animate import animate, render
+import os
+import urllib.request
+from tqdm import tqdm
+
+# Download the TESS data
+base = 'https://archive.stsci.edu/missions/tess/models/'
+files = [
+    'TESS_EPH_PRE_LONG_2018176_01.bsp',
+    'TESS_EPH_PRE_LONG_2018183_01.bsp',
+    'TESS_EPH_PRE_LONG_2018186_01.bsp',
+    'TESS_EPH_PRE_LONG_2018190_01.bsp',
+    'TESS_EPH_PRE_LONG_2018193_01.bsp',
+    'TESS_EPH_PRE_LONG_2018197_01.bsp',
+    'TESS_EPH_PRE_LONG_2018200_01.bsp',
+    'TESS_EPH_PRE_LONG_2018204_01.bsp',
+    'TESS_EPH_PRE_LONG_2018207_01.bsp',
+    'TESS_EPH_PRE_LONG_2018211_01.bsp',
+    'TESS_EPH_PRE_LONG_2018214_01.bsp',
+    'TESS_EPH_PRE_LONG_2018218_01.bsp',
+    'TESS_EPH_PRE_LONG_2018221_01.bsp',
+    'TESS_EPH_PRE_LONG_2018225_01.bsp',
+    'TESS_EPH_PRE_LONG_2018228_01.bsp',
+    'TESS_EPH_PRE_LONG_2018232_01.bsp',
+    'TESS_EPH_PRE_LONG_2018235_01.bsp',
+    'TESS_EPH_PRE_LONG_2018239_01.bsp',
+    'TESS_EPH_PRE_LONG_2018242_01.bsp',
+    'TESS_EPH_PRE_LONG_2018246_01.bsp',
+    'TESS_EPH_PRE_LONG_2018249_01.bsp',
+    'TESS_EPH_PRE_LONG_2018253_01.bsp',
+    'TESS_EPH_PRE_LONG_2018256_01.bsp',
+    'TESS_EPH_PRE_LONG_2018260_01.bsp',
+    'TESS_EPH_PRE_LONG_2018263_01.bsp',
+    'TESS_EPH_PRE_LONG_2018268_01.bsp',
+    'TESS_EPH_PRE_LONG_2018270_01.bsp',
[…]

### 2019-04-03 earthshine/animate.py

@@ -90,7 +90,7 @@ def render(map, time, phase0=-56.5, time0=1325.5, res=75, period=0.9972696):
     source = np.dot(R, source)
 
     # Render the image
-    Z = map.render(source=source, res=res)[0]
+    Z = map.render(source=source, res=res)
     map.reset()
     map[:, :, :] = y
     return Z
@@ -233,7 +233,7 @@ def animate(map, time, phase0=-56.5, time0=1325.5, res=75, interval=75, period=0
         source = np.dot(R, source)
 
         # Render the image
-        Z[i] = map.render(t=t[i], source=source, res=res)[0]
+        Z[i] = map.render(t=t[i], source=source, res=res)
 
     # Reset the map
     map[:, :, :] = y

### 2019-04-03 earthshine/model.py

@@ -56,10 +56,17 @@ def ylm_to_alm(ylm, lmax):
 def smooth(map, sigma):
     """Smooth a map in place with a Gaussian kernel."""
     lmax = map.ydeg
-    alm = ylm_to_alm(map.y, lmax)
+    if map._temporal:
+        alm = ylm_to_alm(map[:, :, 0], lmax)
+    else:
+        alm = ylm_to_alm(map[:, :], lmax)
     hp.sphtfunc.smoothalm(alm, sigma=sigma, inplace=True, verbose=False)
     ylm = alm_to_ylm(alm, lmax)
-    map[:, :] = ylm
+    ylm /= ylm[0]
+    if map._temporal:
+        map[:, :, 0] = ylm
+    else:
+        map[:, :] = ylm
     return
 
 

### 2019-04-03 setup.py

@@ -3,7 +3,6 @@
 from __future__ import division, print_function, absolute_import
 from setuptools import setup
 
-
 # Setup!
 setup(name='earthshine',
       version="0.0.1",
@@ -19,7 +18,8 @@ setup(name='earthshine',
           'scipy',
           'matplotlib',
           'starry==1.0.0.dev0',
-          'healpy'
+          'healpy',
+          'tqdm'
       ],
       dependency_links=[
         'https://github.com/rodluger/starry/tarball/linear#egg=starry-1.0.0.dev0'

### 2019-05-01 tex/ms.tex
changes to abstract and conclusions

@@
 \begin{abstract}
-\todo{(TO BE CHANGED:)}
 To date, a handful of exoplanets have been photometrically mapped using phase-modulated 
@@
 features on hot giant planets. 
-In this work, we uncover a signal using recently released data from the Transiting 
-Exoplanet Survey Satellite (\TESS), which we show corresponds to time-variable reflection 
-from a terrestrial 
-planet with a rotation period of $0.9972696$ days. 
-Using a spherical harmonic-based reflection model developed as an extension of 
-the \starry package, we are able to reconstruct the surface features of this rocky 
-world. We recover a time-variable albedo map of the planet including persistent 
-regions which we interpret as oceans and cloud banks indicative of continental features. 
-We argue that this planet represents the most promising detection of a habitable 
-world to date, although the potential intelligence of any life on it is yet to 
-be determined.
+With future instruments, more detailed mapping of terrestrial planets may become possible, 
+but significant challenges will remain in analyzing and interpreting these data. 
+In this work, we extract a rotationally-modulated reflected light curve of the Earth 
+from the time-variable background flux in data from the Transiting Exoplanet Survey Satellite (\TESS).
+We treat these data as an unknown exoplanet and reconstruct surface features  
+using a spherical harmonic-based reflection model developed as an extension of 
+the \starry package. We recover a time-variable albedo map including persistent 
+regions indicative of Earth's major oceans and cloud banks. 
+Our results suggest that the recovery of surface features on a terrestrial exoplanet
+from reflected-light photometric monitoring will be possible, but will require
+a considerable investment of observing time to achieve the high cadence and 
+long time baseline needed.
 \href{https://github.com/rodluger/earthshine}{\color{linkcolor}\faGithub}
@@
 We detect three large scale bright regions near
-the equator of the planet, associated with persistent cloud structures
-at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
-likely track continents. Pronounced dark features are identified
+the equator of the planet at longitudes of 
+$-60^\circ$, $+30^\circ$, and $+90^\circ$, 
+which we interpret as persistent cloud structures 
+near the Andes, sub-Saharan Africa, and the South Asian monsoon. 
+Pronounced dark features are identified
 at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
-significant latitudinal extent, likely corresponding to oceans. Because of the
+significant latitudinal extent, likely corresponding to 
+the Pacific, Atlantic, and Indian Oceans. Because of the
 vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
@@
 
-We fit Earth with both static and time-variable albedo maps. 
+We fit Earth's light curve with both static and time-variable albedo maps. 
 We find tentative evidence for variability in Earth's cloud coverage over 

### 2019-05-02 tex/ms.tex
working on intro

--- 2019-04-03 tex/ms.tex
@@
 planets in the habitable zone
-\citep[e.g.,][]{Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
-for a review, see \cite{Cowan2018}.
-
-\todo{(THIS PARAGRAPH TO BE CHANGED:)} 
-In this work, we show how we can harness photometric data collected by the \TESS mission
-to construct a map of Earth, a rocky planet with a radius of $6.4\times 10^6$~m
-orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
-star \citep{Sagan1993}. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
-the habitable zone for follow-up with other missions, it came as a great surprise
-that data from the spacecraft could be used not only to detect Earth but to
-characterize it in detail. This is due primarily to the strong nature of the reflected
-light signal originating from the planet, which 
-because of complex internal optics illuminates the entirety of the \TESS detector 
-during most of Sector 1 and part of Sector 2.
-
-Previous attempts to map Earth from the exoplanet community have suggested 
-the presence of localized surface features, but their resolving power has been 
-limited by the cadence and/or duration of observations \citep{Cowan2009,Jiang2018}. 
+\citep[e.g.,][]{Ford2001,Tinetti2006a,Tinetti2006b,WilliamsGaidos2008,Palle2008,
+Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
+for a review, see \cite{Cowan2018}. In particular, several works
+have harnessed space-based observations of the Earth in proof-of-concept
+studies aimed at shedding light on the opportunities and challenges future
+exoplanet mapping missions may bring. Perhaps the most well-known of these
+is the work of \cite{Sagan1993}, who used observations from the Galileo probe
+to infer the existence of life on Earth. However, this study made use of both
+spectroscopic observations and spatially-resolved images of the planet at high
+resolution. \cite{Goode2001} and \cite{Woolf2002} used unresolved measurements of
+Earthshine reflecting off the face of the Moon to infer the planet's
+seasonally-variable albedo and its atmospheric transmission spectrum,
+respectively. \cite{Cowan2009} used unresolved images of the Earth taken
+by the EPOXI spacecraft to construct low resolution albedo maps, recovering
+approximate longitudinal distributions of oceans continents on the planet. More
+recently, \cite{Jiang2018} made use of daily images of the fully-illuminated
+disk of the Earth taken by the Deep Space Climate Observatory (DSCOVR) to recover
+the planet's rotation rate and seasonal albedo variations.
+
+In all of these studies, ...
+
+resolving power has been 
+limited by the cadence and/or duration of observations
 \TESS offers precise 2-minute cadence data spanning a wide range of illumination 
@@
 unprecedented in the history of exoplanet phase mapping.
+
+\citep{Sagan1993}.
+
 %

### 2019-05-02 tex/ms.tex
more updates

@@
 \citep[e.g.,][]{Ford2001,Tinetti2006a,Tinetti2006b,WilliamsGaidos2008,Palle2008,
-Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
+Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Farr2018,Lustig-Yaeger2018};
 for a review, see \cite{Cowan2018}. In particular, several works
@@
 seasonally-variable albedo and its atmospheric transmission spectrum,
-respectively. \cite{Cowan2009} used unresolved images of the Earth taken
+respectively. Similarly, \cite{Hasinoff2011} presented a method to infer
+the two-dimensional map of the Earth from single-pixel measurements of the
+planet's diffuse reflectance on the Moon.
+\cite{Cowan2009} used unresolved images of the Earth taken
 by the EPOXI spacecraft to construct low resolution albedo maps, recovering
-approximate longitudinal distributions of oceans continents on the planet. More
-recently, \cite{Jiang2018} made use of daily images of the fully-illuminated
+approximate longitudinal distributions of oceans continents on the planet. 
+More recently, \cite{Jiang2018} made use of daily images of the fully-illuminated
 disk of the Earth taken by the Deep Space Climate Observatory (DSCOVR) to recover
@@
 
-In all of these studies, ...
-
-resolving power has been 
-limited by the cadence and/or duration of observations
-\TESS offers precise 2-minute cadence data spanning a wide range of illumination 
-phases, enabling a level of spatial and temporal resolving power that is 
-unprecedented in the history of exoplanet phase mapping.
-
-\citep{Sagan1993}.
-
+In all of these studies, the resolution and fidelity of the inferred maps of the
+Earth have been strongly limited by the cadence and/or baseline of observations.
+Inferring high spatial resolution features necessitates observations at 
+high temporal resolution, while long baselines spanning different seasons
+on the planet are required to break the degeneracies inherent to the 
+mapping problem.
+
+In this work we use scattered light present in the background of
+detectors aboard the \TESS spacecraft to infer a map of the surface of the Earth.
+Although \TESS was designed as an all-sky photometric exoplanet survey,
+significant levels of
+scattered light from the Earth (``Earthshine'') are present across the \TESS detector
+during several of the mission's observing sectors. Despite the presence
+of a sunshade and a lens hood to limit this kind of contamination,
+Earthshine is a dominant background signal particularly during
+sectors 1 and 2, when the Earth spent a significant fraction of the
+time above the edge of the \TESS sunshade. Although the Earth is never
+directly in the field of view of the \TESS cameras, Earthshine reflects 
+off the inside of the lens hoods, illuminating each of the four cameras
+with a signal that is both spatially and temporally variable due to 
+the complex optics at play. For more information, refer to the
+\TESS Instrument Handbook\footnote{\url{https://archive.stsci.edu/missions/tess/doc/TESS_Instrument_Handbook_v0.1.pdf}}.
+
+Although the Earthshine signal in \TESS is convolved with complicated systematics,
+this dataset offers an unprecedented opportunity to tackle the mapping problem, given
+its extremely high cadence (observations recorded every 2 minutes in short cadence mode) 
+and the long observing baseline of \TESS (a 2 year primary mission, with the Earth in view
+for several months of the year).
 %
@@
 Not all postage stamps are equally informative, since the desired signal from 
-Earth is inhomogeneously spread across the \TESS detectors and manifests itself
+the Earth is inhomogeneously spread across the \TESS detectors and manifests itself
 differently in different regions (see \S\ref{sec:systematics}). 
@@
 ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
-the relative positions of Sol, Earth, and \TESS for every cadence
+the relative positions of the Sun, the Earth, and \TESS for every cadence
 in our dataset in the J2000 equatorial reference frame. In this right-handed
-coordinate frame, Earth is centered at the origin, the $y$ axis points along the 
+coordinate frame, the Earth is centered at the origin, the $y$ axis points along the 
 planet's spin axis, and the $x$ axis points toward the vernal equinox. We
@@
 
-At any given cadence, we rotate Earth about its spin axis to the correct phase,
+At any given cadence, we rotate the Earth about its spin axis to the correct phase,
 assuming a planetary rotation period of $0.9972696$ days and an obliquity
@@
     \caption{\label{fig:phases}
-             Synthetic images showing \TESS's view of Earth on every date in 
+             Synthetic images showing \TESS's view of the Earth on every date in 
              Sectors 1 and 2 that was included in the regression. Each image 
              is labeled with the corresponding timestamp in TJD. 
-             The dayside features shown here correspond to a 
+             The dayside features shown here correspond to a simple continental
              model of Earth, not to the map inferred in this study.
@@
 
-Figure~\ref{fig:phases} shows the view \TESS has of Earth on each of the dates
+Figure~\ref{fig:phases} shows the view \TESS has of the Earth on each of the dates
 in our dataset; these images were produced by applying the sequences of rotations
-described above. The planet is illuminated by Sol assuming it is a point source,
-and the night side is shaded black. The map of Earth shown in this figure is 
-based on current models of the actual distribution of continents on the planet.
-Note that although the images are computed an integer number of rotation periods
+described above. The planet is illuminated by the Sun assuming it is a point source,
+and the night side is shaded black. Note that the map of the Earth shown in this figure is
+purely illustrative and does not correspond tot he map inferred in this study.
+Note also that although the images are computed an integer number of rotation periods
 apart, the planet appears to slowly rotate over the course of the observation.
 This is due to the orbit of \TESS, which changes its vantage point relative
-to Earth over the course of its 13 day orbit.
+to the Earth over the course of its 13 day orbit.
 
@@
 that are correlated but not identical across all postage stamps, since the
-illumination of the CCD by Earth is strongly inhomogeneous. A physical
+illumination of the CCD by the Earth is strongly inhomogeneous. A physical
 model of the reflections and scattering that gives rise to the
-signal of Earth on the \TESS detector is beyond the scope of this work. Instead,
+signal of the Earth on the \TESS detector is beyond the scope of this work. Instead,
 we treat this as a de-trending problem, where the signal we wish to fit is
@@
 We model the astrophysical component of the signal---the rotational modulation
-of Earth in reflected light---using the \starry code package \citep{Luger2019}.
+of the Earth in reflected light---using the \starry code package \citep{Luger2019}.
 \starry computes phase curves and occultation light curves for bodies whose
@@
 However, in the present work, we are interested in \emph{reflected} light, so we must
-account for the illumination by the star. This illumination varies smoothly
+account for the illumination by the Sun. This illumination varies smoothly
 across the dayside of the planet, but its derivative discontinuously changes at the 
@@
 sharp rise at the beginning of each orbit in Sector 1 is due to the changing
-vantage point of \TESS as Earth transitions from a thin crescent to full phase.
+vantage point of \TESS as the Earth transitions from a thin crescent to full phase.
 
@@
 as a multiplicative term to scale the luminosity 
-of Earth to the flux observed by \TESS. The model for the flux time series
+of the Earth to the flux observed by \TESS. The model for the flux time series
 in the $n^\mathrm{th}$ postage stamp is therefore

### 2019-05-02 tex/ms.tex
woot

@@
 features on hot giant planets. 
-With future instruments, more detailed mapping of terrestrial planets may become possible, 
+Future instruments may enable more detailed mapping of terrestrial planets, including
+those in the habitable zone,
 but significant challenges will remain in analyzing and interpreting these data. 
@@
 from the time-variable background flux in data from the Transiting Exoplanet Survey Satellite (\TESS).
-We treat these data as an unknown exoplanet and reconstruct surface features  
+We treat these data as that of an unknown exoplanet and reconstruct surface features  
 using a spherical harmonic-based reflection model developed as an extension of 
 the \starry package. We recover a time-variable albedo map including persistent 
-regions indicative of Earth's major oceans and cloud banks. 
+regions indicative of the Earth's major oceans and cloud banks. 
 Our results suggest that the recovery of surface features on a terrestrial exoplanet
@@
 the \starry framework to perform fast, analytical inversion of the light curve
-of Earth and thus construct a map of the planet in reflected light.
+of the Earth and thus construct a map of the planet in reflected light.
 
@@
 in all but the last group to be dominated by 
-the signal of Earth, while light
+the signal of the Earth, while light
 curves in the last group were dominated by signals other than the
@@
              Normalized background flux in each of ten postage stamps
-             for each of Sectors 1 and 2. Cadences where Earth was
+             for each of Sectors 1 and 2. Cadences where the Earth was
              below or very close to the edge of the sunshade were masked.
@@
 \end{figure}
-
-\pagebreak
 
@@
 At any given cadence, we rotate the Earth about its spin axis to the correct phase,
-assuming a planetary rotation period of $0.9972696$ days and an obliquity
+assuming a planetary rotation period of $0.9972696$ days (the Earth's sidereal 
+rotation period) and an obliquity
 of $23.437^\circ$. We determine the initial rotation
-phase of Earth by computing the Earth Rotation Angle (ERA), given by \citep{Urban2013}
+phase of the Earth by computing the Earth Rotation Angle (ERA), given by \citep{Urban2013}
 %
@@
 where $t_U = t - 2451545.0$. At $t = t_0 = 2458325.5$, the first timestamp in our dataset,
-we find $\mathrm{ERA} = 303.4^\circ$, meaning the vernal equinox will be aligned with
+we find $\mathrm{ERA} = 303.4^\circ$, meaning the vernal equinox is aligned with
 the prime meridian $360^\circ - 303.4^\circ = 56.6^\circ = 3.77$ hours past $t_0$.
@@
 Finally, we rotate the frame to align
-\TESS with the $+z$ axis, with the spin vector of Earth along the $y-z$ plane.
+\TESS with the $+z$ axis, with the spin vector of the Earth along the $y-z$ plane.
 We verified our rotations by comparing our results on several days to the
@@
              The dayside features shown here correspond to a simple continental
-             model of Earth, not to the map inferred in this study.
+             model of the Earth, not to the map inferred in this study.
              \codelink{EarthView}
@@
     \caption{\label{fig:map_L2}
-             Maximum likelihood map of Earth obtained during the first
+             Maximum likelihood map of the Earth obtained during the first
              stage of our optimization procedure, in which an iterative
@@
              expected locations of South America, Africa, and Asia, 
-             and two dark features appear at Earth's
-             two major oceans, the Pacific and the Atlantic. 
-	          Black contours correspond to known coastlines. 
-	          \codelink{earthshine_S1_S2}      
+             and two dark features appear at locations consistent with
+             the Pacific and Atlantic oceans. Note that the colors correspond
+             to a \emph{normalized} albedo, scaled such that the dynamic
+             range of the image spans [0, 1]. \codelink{earthshine_S1_S2}      
              }
@@
 wraps around the antimeridian). Overplotted on the inferred map are
-coastal outlines of Earth's continents. One can see that the three bright regions roughly
+coastal outlines of the Earth's continents. One can see that the three bright regions roughly
 track, from left to right, the continents  of South America,
 Africa, and Asia. The dark regions
-appear at the locations of Earth's two major oceans, the
-Pacific (centered at longitude $\pm180^\circ$) and the Atlantic
-(centered at longitude $\-45^\circ$).
+appear at the locations of the
+Pacific ocean (centered at longitude $\pm180^\circ$) and the Atlantic
+ocean (centered at longitude $-45^\circ$).
 
@@
 between about 0.1 and 10 days, with a significant dip at 1.00 day. This
-suggests our model is fitting the rotational variability of Earth quite well, but
+suggests our model is fitting the rotational variability of the Earth quite well, but
 additional temporal variations---most likely due to cloud movement---cause aperiodic
@@
              \emph{Top:} The maximum likelihood model for the surface albedo
-             of Earth, weighted by the visibility across Sectors 1 and 2. The
+             of the Earth, weighted by the visibility across Sectors 1 and 2. The
              dashed white lines indicate latitudes above/below which the
@@
 cosine of the illumination angle and the cosine of the angle between the 
-observer vector and the vector normal to the surface of Earth. This normalization
+observer vector and the vector normal to the surface of the Earth. This normalization
 has the effect of downweighting regions that are either seldom illuminated (such
-as regions near the southern pole of Earth, as the observations were taken during
+as regions near the southern pole of the Earth, as the observations were taken during
 southern winter) or seldom in view (such as regions near the northern pole of the planet,
@@
 we use dashed lines to delineate the regions whose average visibility is larger
-than 0.5.
+than 0.5. Note that as before, the albedo is scaled to span the range [0, 1]. We emphasize
+that because of the unknown throughput of the optics that give rise to the Earthshine
+signal in \TESS, the absolute scaling of the albedo cannot be inferred from the
+dataset alone.
 
 The bottom panel of Figure~\ref{fig:map} shows an approximate average
-cloud cover map of Earth based on imagery taken by the
+cloud cover map of the Earth based on imagery taken by the
 Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
@@
 bands (i.e., inconsistent with a grey spectrum). We then averaged the images
-averaged over the 28 days of data analyzed in this work, smoothed it 
-with a Gaussian filter, and weighted by the \TESS visibility as in the top panel.
-
-While the two panels display fundamentally different quantities---an albedo
-and a cloudiness factor---we expect that the signal of Earth in the \TESS
+over the 28 days of data analyzed in this work, smoothed it 
+with a Gaussian filter, and weighted it by the \TESS visibility as in the top panel.
+
+While the two panels display fundamentally different quantities---a scaled albedo
+and a cloudiness factor---we expect that the signal of the Earth in the \TESS
 bandpass is dominated by cloud reflectivity, as water clouds have an albedo
@@
 Fortunately, there are two aspects of the problem at hand that facilitate
-this (seemingly impossible) inversion. First, the surface of Earth is
+this (seemingly impossible) inversion. First, the surface of the Earth is
 not uniformly illuminated; instead, different parts of the surface are weighted
@@
 \TESS changes the position and shape of the terminator on the projected disk
-of Earth, enhancing the effect discussed above.
+of the Earth, enhancing the effect discussed above.
 
@@
 Figure~\ref{fig:map} that degeneracies still abound. While we infer a few of the
-dominant features of the cloud map of Earth, several of them are skewed, 
+dominant features of the cloud map of the Earth, several of them are skewed, 
 shifted, or entirely out of place. This is the case, for instance, with
@@
 our adopted model. While the measurement errors on our data points are
-quite small---since the signal of Earth is both quite strong and independently
+quite small---since the signal of the Earth is both quite strong and independently
 measured at 95 different positions on the detector---our lack of understanding
@@
 
-Third, inspection of Figure~\ref{fig:phases} shows that most of the time, Sol
-d is close to full phase as seen by \TESS.
+Third, inspection of Figure~\ref{fig:phases} shows that most of the time, the Earth
+is close to full phase as seen by \TESS.
 With the terminator close to the limb
@@
 We are therefore somewhat limited in our ability to infer in particular the
-latitudinal position of features. Observations of Earth in upcoming
-sectors may contain longer segments in which Earth is seen in crescent,
+latitudinal position of features. Observations of the Earth in upcoming
+sectors may contain longer segments in which the planet is seen in crescent,
 which should help mitigate these degeneracies.
 
-Fourth, and most importantly, we have not performed actual inference: that is, 
+Fourth, and most importantly, we have not performed Bayesian inference: that is, 
 we simply found the maximum likelihood solution (subject to our constraints),
@@
 approach than simply maximizing the likelihood function is to marginalize
-over the nuisance parameters---such as the systematic model weights and the spectral
+over the nuisance parameters---such as the systematics model weights and the spectral
 slope. This is more costly, but certainly not intractable, and we will
@@
 slope of the map as a free parameter rather than using the true power spectrum 
-of Earth. Moreover, the broad features in the strongly
+of the Earth. Moreover, the broad features in the strongly
 regularized map (Figure~\ref{fig:map_L2})---and in particular the monsoon clouds
@@
 Similarly, we used the timestamps reported in the \tess light curve
-FITS files, which are corrected to the barycenter of the Sol system. Since
+FITS files, which are corrected to the barycenter of the Solar System. Since
 our signal originates from a source that is closer to \tess than the
@@
 latitudes. In particular, our prior implicitly disfavors banded cloud structure,
-which one may \emph{a priori} expect on a rapidly rotating planet such as 
-Earth. The bottom panel of Figure~\ref{fig:map} shows such banded structure
+which is quite common on Earth. The bottom panel of Figure~\ref{fig:map} shows such banded structure
 at the equator and at mid-latitudes due to the combined effects of 
@@
 Finally, and perhaps more importantly, our model assumed a \emph{static}
-map for the surface of Earth. We also know this to be incorrect, since
+map for the surface of the Earth. We also know this to be incorrect, since
 clouds form and move on timescales of hours to days. We discuss this in
@@
 the fact that rotational variability is not the sole source of the
-signal of Earth: additionally, there is temporal variation in the 
-albedo of certain parts of the map, most probably due to cloud movement.
-In order to test this, we used \starry to construct a time-variable
+signal of the Earth: additionally, there is temporal variation in the 
+albedo of certain parts of the map  due to cloud movement.
+In order to model this, we used \starry to construct a time-variable
 spherical harmonic map, defined by a vector of spherical harmonic coefficients
@@
 timescales, a more detailed investigation is warranted to say anything
-meaningful about the dynamics of clouds on Earth.
+meaningful about the dynamics of clouds on Earth from \TESS observations.
 
@@
 (without the continent outlines),
-an inhabitant of Earth may be hard-pressed to identify that
-as a map of their home planet. This is in part due to the biases
+one may be hard-pressed to identify that
+as a map of our home planet. This is in part due to the biases
 in our optimization, which we discussed above, but also due to the 
-simple fact that the reflectance of Earth is dominated---by far---by 
+simple fact that the reflectance of the Earth is dominated---by far---by 
 time-variable clouds. While stationary cloud features on Earth are
@@
 axis of rotation should precess---may help to disambiguate between
-clouds, oceans, and continents. Although the signal of Earth 
+clouds, oceans, and continents. Although the signal of the Earth 
 mostly disappears from the \tess detector after Sector 2, it is
@@
 generate (and invert) light curves in reflected light, coupling it
-to a variation of pixel level decorrelation to model the systematics
+to a variant of pixel level decorrelation to model the systematics
 in the \TESS detector.
@@
 
-To summarize, we have robustly detected surface features from \TESS 
-light curves of Earth. While the resolution of the map we obtain is limited, 
-we do unambiguously detect surface features including low-albedo oceanic regions and 
-high-albedo cloud banks or land masses.
+%To summarize, we have robustly detected surface features from \TESS 
+%light curves of the Earth. While the resolution of the map we obtain is limited, 
+%we do unambiguously detect surface features including low-albedo oceanic regions and 
+%high-albedo cloud banks or land masses.
 
@@
 efforts to characterize terrestrial exoplanets. While the circumstances of \TESS's 
-observations of Earth will not be replicated exactly for other planets, similar 
+observations of the Earth will not be replicated exactly for other planets, similar 
 rotationally-modulated phase curves of reflected light may be feasible in the future. 
@@
 We gratefully acknowledge Jonathan Fraine, Dan Foreman-Mackey, 
-David W. Hogg, Ben Montet, and Ben Pope for useful conversations. 
+David W. Hogg, Ben Montet, Ben Pope, and Wolfgang Kerzendorf for useful conversations. 
 Crucial parts of this work were carried out at the 

### 2019-05-02 setup.py
fix starry version

@@ -22,7 +22,7 @@ setup(name='earthshine',
           'tqdm'
       ],
       dependency_links=[
-        'https://github.com/rodluger/starry/tarball/linear#egg=starry-1.0.0.dev0'
+        'https://github.com/rodluger/starry/tarball/fd0ce1edab6a3e83cc3231411e2406bb02df6096#egg=starry-1.0.0.dev0'
       ],
       include_package_data=False,
       zip_safe=False

### 2019-05-03 tex/ms.tex
minor edits

@@
 
-However, obtaining a map of a temperate terrestrial exoplanet is still
+Obtaining a map of a temperate terrestrial exoplanet is still
 beyond the capabilities of current facilities, as both the thermal and 
@@
 is the work of \cite{Sagan1993}, who used observations from the Galileo probe
-to infer the existence of life on Earth. However, this study made use of both
+to infer the existence of life on Earth. This study made use of both
 spectroscopic observations and spatially-resolved images of the planet at high
-resolution. \cite{Goode2001} and \cite{Woolf2002} used unresolved measurements of
+resolution, neither of which will necessarily be available for an analogous exoplanet. 
+For a more exoplanet-like approach, \cite{Goode2001} and \cite{Woolf2002} used unresolved measurements of
 Earthshine reflecting off the face of the Moon to infer the planet's
@@
 Although the Earthshine signal in \TESS is convolved with complicated systematics,
-this dataset offers an unprecedented opportunity to tackle the mapping problem, given
+this dataset offers an unprecedented opportunity to tackle the mapping problem in detail, given
 its extremely high cadence (observations recorded every 2 minutes in short cadence mode) 
@@
              and two dark features appear at locations consistent with
-             the Pacific and Atlantic oceans. Note that the colors correspond
+             the Pacific and Atlantic oceans. The colors correspond
              to a \emph{normalized} albedo, scaled such that the dynamic
@@
              \emph{Top:} The maximum likelihood model for the surface albedo
-             of the Earth, weighted by the visibility across Sectors 1 and 2. The
+             of the Earth, weighted by the visibility across Sectors 1 and 2 and
+			 normalized. The
              dashed white lines indicate latitudes above/below which the
@@
 our adopted model. While the measurement errors on our data points are 
-quite small---since the signal of the Earth is both quite strong and independently
+small---since the signal of the Earth is both quite strong and independently
 measured at 95 different positions on the detector---our lack of understanding
@@
 We are therefore somewhat limited in our ability to infer in particular the
-latitudinal position of features. Observations of the Earth in upcoming
+latitudinal position of features. The Earthshine present in upcoming
 sectors may contain longer segments in which the planet is seen in crescent,
@@
 \emph{how} we performed the analysis. For instance, in an early version of 
-the project we used as regressors actual \TESS housekeeping variables---such as the angle 
+the analysis we used as regressors actual \TESS housekeeping variables---such as the angle 
 and elevation of the Earth and the Moon relative to each of the four camera 

### 2019-08-26 tex/ms.tex
updates for AJ revision

@@
 \documentclass[modern]{aastex62}
+
+% Edited text for revision
+\newcommand{\edited}[1]{\textcolor{blue}{#1}}
 
@@
 To accomplish this, we applied a categorization and outlier rejection scheme to the ensemble of light curves.
-During this selection step only, we normalized the light curves to the same min-max range.
-We then computed the median
-flux at each cadence along with an estimate of the variance based on the
-median absolute deviation (MAD) across all light curves.
-For each light curve, we calculated a score $\chi^2$ equal to the sum of the squares of the
-deviation from the median at each of the $N$ cadences, normalized by the variance.
-We removed all light curves with $\chi^2 < N$ from the pool, placing
-them in a separate group. We repeated these steps several times,
+\edited{%
+During this selection step only, we normalized each light curve $\mathbf{f}_n$ to have
+flux in the range 0--1:
+\begin{align}
+    \mathbf{f\,'}_n = \frac{\mathbf{f}_n - f_{n,0.05}}{f_{n,0.95} - f_{n,0.05}} \quad,
+\end{align}
+where $f_{n,0.05}$ and $f_{n,0.95}$ represent the 5$^\mathrm{th}$ and 95$^\mathrm{th}$ 
+percentile values of the flux in the $n^\mathrm{th}$ light curve, respectively.
+We then computed the median value of $\mathbf{f\,'}_n$ at each cadence 
+across all light curves,
+along with an estimate of the standard deviation based on the
+median absolute deviation across all light curves:
+\begin{align}
+    \boldsymbol{\mu} &= \mathrm{median}\left( \{\mathbf{f}\,'_n\} \right) \nonumber\\
+    \sigma &= 1.4826 \times \mathrm{median}\left( \big\{ \big| \mathbf{f}\,'_n - \boldsymbol{\mu} \big| \big\} \right)
+\end{align}
+For each light curve, we then calculated a score indicative of its similarity
+to the median light curve:
+\begin{align}
+    \chi^2_n = \frac{1}{K} \sum_{k=0}^K \frac{(f'_{n,k} - \mu_k)^2}{\sigma^2} \quad,
+\end{align}
+where $K$ is the number of cadences in the light curve.
+We removed all light curves with $\chi^2_n < N$ from the pool, placing
+them in a separate group. 
+}
+We repeated these steps several times,
 classifying light curves into four groups for Sector 1 and two groups for Sector 2. 
@@
 and the first 20 in the first group in Sector 2 for a total
-of 75 and 20 light curves, respectively. We then computed an estimate of the
+of 75 and 20 light curves, respectively. 
+\edited{%
+We then median-normalized all light curves (as opposed to the
+normalization used for the classification discussed above). Finally,
+we computed an estimate of the
 non-Earth background flux from the cadences during which the planet was below
 the edge of the sunshade and removed this baseline from the flux.
-Finally, we median-normalized all light curves (as opposed to the min-max
-normalization used for the classification).
+}
 Our final dataset consisted of 912,605 data points in total. 
@@
              of each orbit in Sector 2.
-             \codelink{earthshine_S1_S2}
+             \codelink{Earthshine}
              }
@@
 and the night side is shaded black. Note that the map of the Earth shown in this figure is
-purely illustrative and does not correspond tot he map inferred in this study.
+purely illustrative and does not correspond \edited{to the} map inferred in this study.
 Note also that although the images are computed an integer number of rotation periods
@@
 
-While the astrophysical signal that we wish to analyze is present in all 
+While the \edited{signal of Earth} that we wish to analyze is present in all 
 extracted light curves, its strength is modulated by time-variable systematics 
@@
 fifth order orthogonal polynomials in time for each of the two orbits in each sector.
-The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
-%
+The systematics model \edited{$\boldsymbol{\psi}$} for the $n^\mathrm{th}$ signal is thus
+%
+\edited{%
 \begin{align}
-\mathbf{p}_n = \mathbf{B} \mathbf{w}_n
+\boldsymbol{\psi}_n = \mathbf{B} \mathbf{w}_n
 \end{align}
-%
+}%
 where $\mathbf{w}_n$ are the weights of each regressor.
@@
 plane, and the sub-stellar point is on the $+y$ axis at $x = 0$
-(see Figure~\ref{fig:geometry}). In this frame, the terminator is a segment of
+(see Figure~\ref{fig:geometry}). In this frame, the terminator %
+\edited{projected onto the $x-y$ plane }%
+is a segment of
 an ellipse, with semi-major axis $a=1$ aligned with the $x$ axis and
-semi-minor axis $b$. It is straightforward to show that the sub-stellar point
+semi-minor axis $b$ %
+\edited{aligned with the $y$ axis}.
+It is straightforward to show that the sub-stellar point
 is located at $y=\sqrt{1 - b^2}$ and the illumination is given by
 %
+\edited{%
 \begin{align}
@@
     \begin{dcases}
-        \sqrt{1 - b^2}y - bz & 
+        \sqrt{1 - b^2}y + bz & 
             \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
@@
 \end{align}
-%
-where $z = \sqrt{1 - x^2 - y^2}$.
+}%
+where \edited{$z = +\sqrt{1 - x^2 - y^2}$}.
 %
@@
 of \starry
-\footnote{\url{https://github.com/rodluger/starry/tree/linear}};
-the details will be discussed in more detail in upcoming work.
+\footnote{\url{https://github.com/rodluger/starry/releases/tag/earthshine}};
+the details will be discussed \edited{further} in upcoming work.
 
@@
 Our full model for each light curve is simply the product of the 
-systematics model $\mathbf{p}_n = \mathbf{B}\mathbf{w}_n$ (different for each target) and
+systematics model 
+\edited{$\boldsymbol{\psi}_n = \mathbf{B}\mathbf{w}_n$}
+ (different for each target) and
 the \starry model $\mathbf{s} = \mathbf{A}\mathbf{y}$ (shared by all targets). Since we 

### 2019-08-26 earthshine/__init__.py

@@ -1,65 +1,61 @@
-from .model import design_matrix, tess_earth_vector, visibility, smooth
+from .model import design_matrix, tess_earth_vector, visibility, smooth, MAP
 from .animate import animate, render
 import os
 import urllib.request
 from tqdm import tqdm
 
 # Download the TESS data
-base = 'https://archive.stsci.edu/missions/tess/models/'
+base = "https://archive.stsci.edu/missions/tess/models/"
 files = [
-    'TESS_EPH_PRE_LONG_2018176_01.bsp',
-    'TESS_EPH_PRE_LONG_2018183_01.bsp',
-    'TESS_EPH_PRE_LONG_2018186_01.bsp',
-    'TESS_EPH_PRE_LONG_2018190_01.bsp',
-    'TESS_EPH_PRE_LONG_2018193_01.bsp',
-    'TESS_EPH_PRE_LONG_2018197_01.bsp',
-    'TESS_EPH_PRE_LONG_2018200_01.bsp',
-    'TESS_EPH_PRE_LONG_2018204_01.bsp',
-    'TESS_EPH_PRE_LONG_2018207_01.bsp',
-    'TESS_EPH_PRE_LONG_2018211_01.bsp',
-    'TESS_EPH_PRE_LONG_2018214_01.bsp',
-    'TESS_EPH_PRE_LONG_2018218_01.bsp',
-    'TESS_EPH_PRE_LONG_2018221_01.bsp',
-    'TESS_EPH_PRE_LONG_2018225_01.bsp',
-    'TESS_EPH_PRE_LONG_2018228_01.bsp',
-    'TESS_EPH_PRE_LONG_2018232_01.bsp',
-    'TESS_EPH_PRE_LONG_2018235_01.bsp',
-    'TESS_EPH_PRE_LONG_2018239_01.bsp',
-    'TESS_EPH_PRE_LONG_2018242_01.bsp',
-    'TESS_EPH_PRE_LONG_2018246_01.bsp',
-    'TESS_EPH_PRE_LONG_2018249_01.bsp',
-    'TESS_EPH_PRE_LONG_2018253_01.bsp',
-    'TESS_EPH_PRE_LONG_2018256_01.bsp',
-    'TESS_EPH_PRE_LONG_2018260_01.bsp',
-    'TESS_EPH_PRE_LONG_2018263_01.bsp',
-    'TESS_EPH_PRE_LONG_2018268_01.bsp',
[…]

### 2019-08-26 earthshine/animate.py

@@ -8,8 +8,11 @@ from tqdm import tqdm
 import glob
 import os
 import starry
-assert starry.__version__ == "1.0.0.dev0", \
-    "This code requires the `starry` version 1.0.0.dev0."
+from packaging import version
+
+assert version.parse(starry.__version__) >= version.parse(
+    "1.0.0.dev3"
+), "This code requires `starry` version >= 1.0.0.dev3. Install it from GitHub: https://github.com/rodluger/starry/tree/earthshine."
 
 # Constants
 REARTH = 1.0 / 6371.0
@@ -20,22 +23,45 @@ path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 __all__ = ["animate", "render"]
 
 
+def RAxisAngle(axis=[0, 1, 0], theta=0):
+    """
+    
+    """
+    axis = np.array(axis) / np.sqrt(np.sum(np.array(axis) ** 2))
+    cost = np.cos(theta * np.pi / 180.0)
+    sint = np.sin(theta * np.pi / 180.0)
+    return np.reshape(
+        [
+            cost + axis[0] * axis[0] * (1 - cost),
+            axis[0] * axis[1] * (1 - cost) - axis[2] * sint,
+            axis[0] * axis[2] * (1 - cost) + axis[1] * sint,
+            axis[1] * axis[0] * (1 - cost) + axis[2] * sint,
+            cost + axis[1] * axis[1] * (1 - cost),
+            axis[1] * axis[2] * (1 - cost) - axis[0] * sint,
+            axis[2] * axis[0] * (1 - cost) - axis[1] * sint,
+            axis[2] * axis[1] * (1 - cost) + axis[0] * sint,
+            cost + axis[2] * axis[2] * (1 - cost),
+        ],
+        [3, 3],
+    )
+
+
 def render(map, time, phase0=-56.5, time0=1325.5, res=75, period=0.9972696):
     """
 
     """
     # Load the SPICE data
-    ephemFiles = glob.glob(path + 'TESS_EPH_PRE_LONG_2018*.bsp')
-    tlsFile = path + 'tess2018338154046-41240_naif0012.tls'
-    solarSysFile = path + 'tess2018338154429-41241_de430.bsp'
-    #print(spice.tkvrsn('TOOLKIT'))
[…]

### 2019-08-26 earthshine/model.py

@@ -4,21 +4,48 @@ from tqdm import tqdm
 import numpy as np
 import os
 import healpy as hp
+from scipy.linalg import cho_factor, cho_solve
 import starry
-assert starry.__version__ == "1.0.0.dev0", \
-    "This code requires the `starry` version 1.0.0.dev0."
+from packaging import version
+
+assert version.parse(starry.__version__) >= version.parse(
+    "1.0.0.dev3"
+), "This code requires `starry` version >= 1.0.0.dev3. Install it from GitHub: https://github.com/rodluger/starry/tree/earthshine."
 
 # Constants
 REARTH = 1.0 / 6371.0
 TJD0 = 2457000
 path = os.path.dirname(os.path.dirname(os.path.abspath(__file__))) + "/data/"
 
-__all__ = ["design_matrix", "tess_vector", "visibility", "smooth"]
+__all__ = ["design_matrix", "tess_vector", "visibility", "smooth", "MAP"]
+
+
+def RAxisAngle(axis=[0, 1, 0], theta=0):
+    """
+    
+    """
+    axis = np.array(axis) / np.sqrt(np.sum(np.array(axis) ** 2))
+    cost = np.cos(theta * np.pi / 180.0)
+    sint = np.sin(theta * np.pi / 180.0)
+    return np.reshape(
+        [
+            cost + axis[0] * axis[0] * (1 - cost),
+            axis[0] * axis[1] * (1 - cost) - axis[2] * sint,
+            axis[0] * axis[2] * (1 - cost) + axis[1] * sint,
+            axis[1] * axis[0] * (1 - cost) + axis[2] * sint,
+            cost + axis[1] * axis[1] * (1 - cost),
+            axis[1] * axis[2] * (1 - cost) - axis[0] * sint,
+            axis[2] * axis[0] * (1 - cost) - axis[1] * sint,
+            axis[2] * axis[1] * (1 - cost) + axis[0] * sint,
+            cost + axis[2] * axis[2] * (1 - cost),
+        ],
+        [3, 3],
+    )
 
 
 def alm_to_ylm(alm, lmax):
     # Convert the alms to real coefficients
-    ylm = np.zeros(lmax ** 2 + 2 * lmax + 1, dtype='float')
+    ylm = np.zeros(lmax ** 2 + 2 * lmax + 1, dtype="float")
     i = 0
     for l in range(0, lmax + 1):
[…]

### 2019-08-26 setup.py

@@ -4,26 +4,28 @@ from __future__ import division, print_function, absolute_import
 from setuptools import setup
 
 # Setup!
-setup(name='earthshine',
-      version="0.0.1",
-      description="Earthshine in TESS",
-      long_description="",
-      url='http://github.com/rodluger/everest',
-      author='Rodrigo Luger',
-      author_email='rodluger@gmail.com',
-      license='MIT',
-      packages=['earthshine'],
-      install_requires=[
-          'numpy>=1.8',
-          'scipy',
-          'matplotlib',
-          'starry==1.0.0.dev0',
-          'healpy',
-          'tqdm'
-      ],
-      dependency_links=[
-        'https://github.com/rodluger/starry/tarball/fd0ce1edab6a3e83cc3231411e2406bb02df6096#egg=starry-1.0.0.dev0'
-      ],
-      include_package_data=False,
-      zip_safe=False
-      )
+setup(
+    name="earthshine",
+    version="0.0.1",
+    description="Earthshine in TESS",
+    long_description="",
+    url="http://github.com/rodluger/everest",
+    author="Rodrigo Luger",
+    author_email="rodluger@gmail.com",
+    license="MIT",
+    packages=["earthshine"],
+    install_requires=[
+        "numpy>=1.8",
+        "scipy",
+        "matplotlib",
+        "starry==1.0.0.dev0",
+        "healpy",
+        "tqdm",
+    ],
+    dependency_links=[
+        "https://github.com/rodluger/starry/tarball/earthshine#egg=starry-1.0.3.dev0"
+    ],
+    include_package_data=False,
+    zip_safe=False,
+)
+

### 2019-08-27 tex/ms.tex
finished revisions

@@
 
-We solve Equation~(\ref{eq:model}) for the weights $\mathbf{w}_n$ and $\mathbf{y}$
-by maximizing the negative log likelihood function in two separate steps. In the
-first step, we take advantage of the linearity of the problem to perform a fast,
-semi-analytical optimization to obtain a starting guess for the weights. In the
-second step, we apply additional constraints to prevent overfitting and ensure
+\edited{%
+Equation~(\ref{eq:model}) is linear in $\mathbf{w}_n$ and in $\mathbf{y}$
+individually, but not in both simultaneously. To find the true optimum for
+both vectors, we must therefore perform a nonlinear optimization. However, we find that 
+the dimensionality of the problem is so large that unless we initialize the 
+optimizer with a good initial guess, it is unable to converge on a good solution.
+Fortunately, we are able to obtain an initial guess by exploiting the
+linearity of the problem and alternating between linear optimization of $\mathbf{w}_n$
+and linear optimization of $\mathbf{y}$. Then, in a second step, we run a
+nonlinear optimizer, applying additional nonlinear constraints to prevent overfitting and ensure
 an albedo in the range $[0, 1]$ everywhere on the surface.
+}
 
@@
 uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
-side. We additionally impose a constraint on the power spectrum of the
+side. 
+\edited{%
+Note that while the lower bound of this range corresponds to a true physical
+constraint---non-negative surface albedo---the upper bound of unity is
+somewhat \emph{ad hoc}, since the true normalization of the flux is
+unknown. We find that varying this upper bound (or removing it entirely) 
+does not significantly change our results, since we only report ``normalized''
+albedos; we discuss this further below.
+}%
+
+We additionally impose a constraint on the power spectrum of the
 inferred map, requiring that it be drawn from a distribution whose mean
@@
 to suppress ringing and spurious high order features.
+\edited{%
+In practice, however, we find that this constraint is negligible compared
+to our prior on the albedo.
+}%
 Our full negative log likelihood function in this step is therefore
@@
 an east-west bias in the location of the features we identify.
+\edited{%
+Similarly, Rayleigh scattering and anisotropic scattering by clouds probably cause 
+similar biases, as could specular reflection off the oceans (glint).
+}
 
@@
              variations in the spherical harmonic coefficients. Compare
-             to Figure~\ref{fig:map}. An animated version of this figure
-             is available on 
-             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{GitHub}.
+             to Figure~\ref{fig:map}. An 3 second animated version of the 
+             top panel is available in the HTML version of this article, showing
+             the inferred cloud movement during sectors 1 and 2.
              \codelink{earthshine_S1_S2}
@@
 Additionally, time-resolved observations in multiple bands could
-also help with this problem. This was discussed in \cite{Cowan2009},
-who showed that multi-band photometry of the Earth enables one to
+also help with this problem. This was discussed in \cite{Cowan2009}%
+\edited{, \cite{Kawahara2011}, and \cite{Fujii2012}, all of which showed }%
+that multi-band photometry of the Earth enables one to
 disentangle the contributions from oceans, continents, and cloud cover.
@@
 \facility{TESS}
-\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
+\software{%
+\edited{%
+Astropy \citep{astropy1,astropy2}, Matplotlib \citep{matplotlib}, Numpy \citep{numpy}, 
+}%
+\starry \citep{Luger2019}, 
 TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}

### 2019-08-27 tex/ms.tex
typo

@@
              variations in the spherical harmonic coefficients. Compare
-             to Figure~\ref{fig:map}. An 3 second animated version of the 
+             to Figure~\ref{fig:map}. \edited{A 4 second animated version of the 
              top panel is available in the HTML version of this article, showing
-             the inferred cloud movement during sectors 1 and 2.
+             the inferred cloud movement during sectors 1 and 2.}
              \codelink{earthshine_S1_S2}
